\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{On the History of Extraordinary Abuse of Power}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Abuse of Power is Universal and Not White Ethnic}

Often, because of people's propensity to know only things of recent periods, there is a tendency in the left, both in the West and East, to associate vile abuse of power with Europeans, and this is because of history of the past five centuries as Europe colonised the world.  In this literature you have the behaviour of enslavers of Africans in the Atlantic slave trade; you have the literature such as Joseph Conrad's {\em The Heart of Darkness}.  Noam Chomsky's articles of history of "Savage US Imperialism" is part of the story.  Then you have the story of oppression of European Jews which ended with a horrific loss of life in the Second World War.  

All of these are relatively recent events.  History of abuse of power goes back much further.  In Suetenius' {\em The Twelve Caesars} you have some sense of the extraordinary abuse of power by Roman Caesars.  And before that you have others in Mesopotamia and Egypt.  There is nothing {\em ethnic} about extraordinary abuse of power.  The corruption of power and its ill effects and poisonous aftermath is part of Human History spanning millenia and including all ethnicities.

I do not want to give the impression that abuse of power is ethnicity-specific.  Indeed, my great discoveries, that between 6.5\% and 9.5\% of human moral values are affected by ethnicity has a corollary that all great immorality is also ethnicity-independent.

\end{document}