\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{These Stupid Bill Gates Types Do Not Understand the Life of Devotion To Truth}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates is a Charlatan and Obsessed by Malevolence}

Bill Gates is not a man of Truth.  He is a criminal mass murderer and thief obsessed by power and money.  He is a tacky little Demon.  

\section{Struggles of a Man Devoted to Truth}

Nature does not reveal her secrets easily.  Sometimes there are just routine work; large scale data analysis, grueling work.  

But great scientific or scholarly work is not gained easily.  For months you could be working on something with firm conviction that your ideas are right and then nothing, just nothing, you are lost and frustrated.  You might go spend time with friends.  You might even say fuck it i'll just pay and fuck a few prostitutes.  Being lost and not feeling like your great ideas have shown their true depth is normal for us. Moments of great triumph are rare, and years might go by before anyone even thinks the work has value. 

\section{Racial Ideas Do not Belong with Truth-Seekers}

There are men and women devoted to Truth in every ethnicity.  These idiotic cunts like Bill Gates who pretend they are playing a video game ordering the world and want White Rule in academia are so ludicrously small and pathetic.  How can they even remotely understand the suffering that we do for our art?  Do you think anyone with real talent would deign to say, "well I have suffered greatly for months seeking truth night and day, and today I will check my melanin levels and if it's just the right amount I am destined to succeed."  No one who has any {\em high school education} would be so unbelievably dull, ok?

\section{Bill Gates Can Burn His Race Claptrap in a Big Pyre}

What I suggest is Bill Gates take all his Racist Claptrap and tie them to himself and burn himself in a big fire.  He is an Evil Demon who ought to be burned at the stake anyway. 
\end{document}
