\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{The Order of Priority in Zulf's Identity}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Angel Above All}
I believe I am an Angel of Heaven and have been for billions of years before I was born on Earth.  I am an Angel above all.  Now I am also Human here, I was born of human woman's womb, and I had lovely human parents, and my father died in 2002 or so.  I have been human on Earth for 48 years.  

\section{Secondarily I am Human}

I am having a Human life among all the Human Beings of Earth.  I had been lovingly raised from human childhood in human cities and lived in New York and San Francisco with human employment, and so on.  So I am American.  I have all sorts of human learning, human ancestral heritage, interest in human affairs, so I am extremely familiar with human issues and contribute to human affairs to the best of my abilities.  That changes nothing of my fundamental identity deep within of just another Angel of Heaven on Earth.  It does not produce any schizophrenic difficulty for me

\section{Chalk it up to Faith}

I meet so many humans who are Christians and Muslims and Jews and Hindus.  I don't understand why my actual identity as Angel is any different from any other faith.

\section{Bill Gates is a Demon Soul to me}

Bill Gates is a Demon Soul to me, and I have 100\% conviction about this.  Chalk this up to faith as well.  I don't feel a need to explain my faith.  No one else does.


\end{document}