\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Narrative Account of Angels and Demon Souls in Human Body}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Disclaimer:Speculative}

These are things I believe to be the case and consistent with Four-Sphere Theory but I have done no experiments.  I do not accept responsibility for anyone who believes them or consequences.  Feel free to dismiss them as subjective speculations.

\section{Existence of Four-Dimensional Purely Electromagnetic Beings}

The universe has a vast fourth purely electromagnetic dimension, it is guaranteed by a parsimonious theory including reality of EM potential.  Purely 'nonphysical' elements including living beings are plentiful in the actual universe.  

\section{Birth of  a Soul}

A soul is born by entry into the fertilised human egg.  For example, my soul entered the fertilised egg of my birth in early 1973, and I was born in November 19 1973.  Regardless of the previous history of the soul, the soul that enters the fertilised egg is left to the resources and nourishment of the biological maternal human being, and all attributes and consciousness has to be regrown by the template of the genetic matter from the parents.  In other words, immediately after entry into the egg, the Soul, whatever might be its identity and history, is not able to gain access to previous consciousness and must be nourished and raised so that the brain can grow and consciousness just as all other human beings do. But the Character of the resulting human being will contain indirect evidence for the soul.

\section{All Human Beings on Earth Are Born Equal}

Equality at birth is a political theory, but it is important to understand that whether a Demon or Angel or any other soul is born as human, they are literally in the same helpless state requiring nourishment from the mother and care till their adulthood after birth.  The genetic material and nurture still constrain them. It is here that current empirical science merges with any esoteric truth.  The Character is still influenced by the soul, and this is remarkably difficult to estimate easily.

\section{Descartes was off regarding Pineal Gland as Seat of the Soul}

The Soul is delicate issue because the Soul is something that is too difficult to examine without proper Four-Sphere Electromagnetic equipment, and my S4 Electromagnetism has not yet become consensus single macroscopic force yet.  The relationship between the body and four-dimensional elements are still left to the Science of the Future.

\section{It matters not whose Soul is what}

There is absolute truth, but for most human affairs, it makes very little difference whether one's Soul is Angel or Demon or more exotic in nature, because we are all still human beings, social primates with six million years of evolutionary history as well.  The Absolute Truth, whatever it is, will be compatible with the best science.

\end{document}
