\documentclass{amsart} 
\usepackage{amsmath}
\usepackage{verse}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Life and Times of Zulfikar Moinuddin Ahmed}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{I am not a Cult of Personality}

Years ago I loved the song "I am Cult of Personality".  I like some of these songs.  I loved Audioslaves' "I am the Highway".  I am not a Renaissance Man.  I am, however, a Scientific Revolutionary, and my Four-Sphere Theory is truth.  I loved always Giordano Bruno, who is beloved as a martyr for Science.  And it may be that I am put in the same class as Giordano Bruno one day where Bill Gates takes on the role of the Church, in a twisted sort of irony, for the Church today considers him Evil. 

Now I will tell you about the dramatic tension of Self-Interest and some of the forces pushing and pulling in the United States.  

\section{Bill Gates cut up my eyes and devastated my interior}
Bill Gates has indeed been cutting up my eyes and admitted in meta that he had 'snafud' my interior which is euphemism for destructive devastation.  This implies that he had violated my American Natural Rights.  And he is not willing at all to back down because he has made the bet that despite my Princeton background and my great achievements, since I am not {\em white} he can just push forward and destroy my life completely and then he has enough money, clout and so on to diffuse the resulting negative effects. It is not an unreasonable bet from his point of view, given what he knows of realistic situations in the world in his amoral power-centric view of things.  He has a nontrivial probability of success.

\section{My reaction to accuse him of violating my Natural Rights}

Although from courtroom drama perspective accusing someone of violating one's fundamental Natural Rights does not seem particularly intelligent and worldly, this is the point of view I took immediately.  My reasoning was that in the end United States stands or falls based on whether United States Government is able to secure all Americans' Natural Rights competently.  Now this would seem fairly weak, since Bill Gates is much wealthier than I am and far more experienced in killing 'little guys' without too much trouble, and quite proficient at it.

\section{Self-Interest of the Senior folk of Justice Department}

Justice Department Senior folk have Self-Interest too.  They and US Supreme Court and US Justices might consider it fairly reasonable to ignore my case that Bill Gates is a traitor to the United States for he had recruited the Israeli asset Noia Efrat to continuously cut my eyes with horrible evil method to live on my blood energy that she calls 'floof'. Bill Gates has been empowering her to harm me in vile malevolent manner for months.  Justice Department and Feds are still reluctant to put Bill Gates to Death which I had been asking for and I know that US Justices found that he had crossed the Death Penalty lines long ago since he entered deep into my blood meta and kept going claiming White Right.  But Justice Department Senior folk are not used to defending the US Government's fundamental duty of securing my and other American Natural Rights and so they believe they are just being sophisticated and worldly by taking their time while Bill Gates has been continuously harming me more.  They are hedging for they may not consider Bill Gates harming me more damaging to the United States but they are not making a clean decision to kill him for Bill Gates having violated my Natural Rights to Death Penalty level and in effect letting him harm me more without immediate action to kill him -- which is the right answer because whatever is Bill Gates' value to the nation does not compensate for his violation of my Natural Rights.  

Justice Department Senior Staff are not used to considering pure foundations as important to their daily decision-making than what they consider pragmatic concerns.  

\section{I Will Obviously Demand \$1 trillion from US}

I will obviously demand \$1 trillion from US later for Miscarriage of Justice for their failure to kill Bill Gates as soon as I made the US Feds and US Justices and US Senate aware that Bill Gates is violating my Natural Rights and he ought to be killed for it.

Now Justice Department Senior Staff are not actually corrupt by Nature but I don't care.  I am getting hurt by their delay to kill Bill Gates so I will demand that US Government compensate me for miscarriage of Justice for delaying killing Bill Gates while Bill Gates has no incentive to stop because he has already made his decision to keep violating my Natural Rights for whatever reason his Evil Demonic Mind concocted.  

\section{Pure Rational Play}

I have no incentive either to budge because I believe in Universal Natural Rights and consider the harm done to me a great sacrifice dedicated to the well-being and future security of my Beloved Human Race. 

\section{The Future}

I cannot predict the future, but when tensions like this build up, it is hard to know what will break first.  Most people might consider me the weakest party in all of this.  That may or may not be the case.  I have no interest in compromising my deep convictions about Natural Rights at 48 because my virtues are strong and I have nothing to gain by compromise.  

\end{document}