\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{On the Nature of an Archangel of Heaven}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Disclaimer}
The content of this note and many others are matters of private faith, and can be considered matters of religious conviction from the social norms of Human Race.  They do not represent any attempt to produce coercive acceptance by anyone.  I also do not take any responsibility to harm to anyone's life that might occur as a consequence of their acceptance.  I take no responsibility or liability.  Believe or disbelieve at your own risk.

\section{I am an Archangel of Heaven Soul}
I have been an Archangel in the Universe for some billion years.  I have been on Earth last between 1180-1300 and was an English Knight during this period.  Then I was born again in November 19 1973 in Bengal, my current human life.  I am not acting on any official capacity while here, and having just a human life.  It is my vacation before hectic work schedule begins after my death.

\section{Angels' Interest in Human Race}

There are vast numbers of Angels in the Universe, much more than 7.8 billion certainly.  There are also populous advanced Angelic Civilisations around the universe.  I won't speak about details because I won't do a good job, and also because it does not really matter to Human Race in its current youthful. 

\section{Strong Support for Universal Natural Rights on Earth}

Archangels do not generally show contempt for any laws that are just and good in any Angelic World at all.  We are law-givers of Angels in a way among many other things and it is not in our Nature to produce disruptions to the development of laws and other institutions in Angelic Worlds.  I am quite proud of my inference that Human Race is Angelic from high quality measured data.  This is very important to Angels.  Angels are involved in many parts of the universe, in all sorts of conflicts and other developments, and without firm evidence that is clear that Human Race is an Angelic Race, we would not be able to decide how to engage with Human Race.  I do not have any ability to contact any large numbers of Angels at will.  I am living a fully human life, and I love human life.  It's been quite exciting.  There are all sorts of developments here, Human Race is progressing and Virtues have improved for the past thousand years, these are very good.  I don't like some of the internecine strife on Earth of course, because to us -- speaking as Angel -- it is quite obvious that Human Race is a single race.  We don't consider the sort of situation where an entire planet is constantly involved in wars among each other as a particularly advanced stage in any Angelic World.  It's true that there was relative peace after the Second World War, but there's always some war or other ever since I was born.  The Vietnam War was almost completed by then.  We don't want any wars on Earth at all, but we don't impose any sort of constraints.  

I will say that I was heavily involved in anti-war activism several decades ago in San Francisco and was a member of International Socialist Organisation then protesting the Iraq War, so as human I am rather not impressed by wars either.  Wars are signs of primitivity to us, especially wars within a Race.  We are at War with Demons all over the Universe, but if you actually get to that level, you will see that War with Demons is actually necessary for Nature.  We don't want any wars {\em within an Angelic Race} because that, to be quite frank is embarrassing.  It makes Angelic Races look bad and confused.




\end{document}