\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Not Instinct for War but Instinct for Belongingness is the Source of War}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Belongingness}
The Social needs of Human Beings for Well-Being is now empirically established by the great global survey of Tay and Diener.  I won't go into the deeper aspects of Social needs of Human Beings that are part of Human Nature.

\section{War is justified for those who do not Belong as External Threats}

We justify wars not because of our hatred for others but for the self-evident needs for the safety and well-being of our own tribes, those who satisfy our Belongingness needs.  We are then moved to war not by negative instincts but by positive instincts.

\section{Solution is Belongingness to Single Human Race}

Reason gives us inference that we can simply expand our Belongingness to the entire Human Race.  However Reason is not Human Nature, and therefore in order to accomplish end of wars, we have to do much more work to ensure that all human beings do have natural Belongingness to the Human Race.  This is not at all easy and that is why we have artists like Pink Floyd singing "Us and Them".  To habituate to trusting all human beings is not rational exactly, so this is a difficult dilemma.  History has examples like spread of Islam that did succeed in expansion of Belongingness to billions of people.  But these things are not easy to accomplish for we, Human Beings like our comfort and are emotionally attached to nostalgic identity of history.  Radical changes to point of view is too disruptive to too many people's lives.  

\section{While Belongingness Exists there will be likelihood of Wars}

Wars cannot be eliminated by simply being of benevolent intentions.  A change in consciousness and identity has to take place before threat of wars can be removed.  And that may or may not be feasible and realistic in centuries to come.  I promote Single Human Race Consciousness and that will only be appealing if it gives all people something more than what they have.  

\end{document}



\end{document}