\documentclass{amsart} 
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{What is a Stupid Cunt and Why Bill Gates is One}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{What is a Stupid Cunt?}

American English usage of the word 'cunt' is varied.  In many circumstances it is considered offensive curse word.  Literally it refers to female genital organ, the vagina.  

However, I claim that it is actually used in vernacular as a descriptive for {\em moral character}.  I justify this by reference to other body parts used as descriptive -- admittedly pejorative -- of {\em moral character}.  Consider "He is such a dick!  He didn't pay at all for the dinner and then he had sex with my girl when I was not looking."  Here "dick" which is a nickname for penis, is actually used as a descriptive of failure of moral virtues.  Similarly, "Don't even talk about that asshole.  He took \$500 from my bank account when I was sleeping and went on a joyride on my precious dough."  Note that even though the ass-hole which is a body part is not referring to any actual body part at all but as pejorative characterisation of failure of {\em moral virtues}.  

As you see from above, these and then others like "cocksucker" and various other words refer {\em always} to descriptive of moral character.  And that is not surprising, has long established tradition in the English vernacular.  

\section{My particular example of a cunt}

Unlike a son of a bitch who is treacherous in a way, whose loyalty is not dependable, a cunt is more extreme.  A cunt is someone who shows up at your house -- perhaps because you thought he was your friend -- and eats your food, drinks your wine, pisses on your carpet, fucks your wife, pushes your grandmother over the bridge, and after all this tells you about how he feels sensitive about how badly you have treated him.  That is a cunt. I want to be very clear.  A lot of people say "cunt is language of hate".  That's not true.  A cunt is what I just described. It could be in some circumstances be construed as language of hate: for example if someone were a good gentleman, sends you birthday cards, invites you to various trips to the Alps and dinners with his family, and you consider him a cunt, that's truly hateful.  That's bad.  Calling someone a cunt when they are quite civilised and not entitled to abuse your relationship and cause massive malicious and malevolent egregious behaviour with enormous entitlement and narcissism, you would be considered quite hateful.  

\section{Bill Gates is both stupid and cunt}

Bill Gates is stupid because he is irrational and despite a great deal of evidence of a single human race is convinced of white superiority.  When my IQ is 135--140 and White IQ distribution is (reasonably) N(100,15), and I am 99.6th percentile of White IQ, he still maintains that I should consider whites superior.  That is not even sensible; it is not sensible to consider any ethnicity superior generally because all traits have overlapping distributions.  Bill Gates is too stupid to understand that this straightforward argument is true.  

And he is a cunt because I did years of hard work on Medium Frequency that he is benefitting from with \$2 bn into it and he reciprocated with enormous harm done to my life instead of paying me my rightful earning.  That's enough for cunt.

\end{document}
