\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Bill Gates is Unqualified for Ruling A Small Commune in Montana let Alone 7.8 Billion}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Monarchy is Not Easy}

My father was in civil service for Bengal and worked his entire life for more than a hundred million people and he was revered by the people enough that in 2002 I was frightened at his funeral to find thousands come to give their last respect for him.  My bloodline goes back to Vedic India in 1750 BC.  I know a thing or two about Monarchy.  One needs exceptional good character to be a true king.  You need instincts for the well-being of billions of people, and natural justice in your heart, benevolence and love for people.

\section{Bill Gates is Thoroughly Unqualified for Monarchy}

Bill Gates has a deceptive evil malevolent character and is a murderous Demon seeking power for himself continuously.  These are horribly bad moral character and he does not care about the well-being of anyone but himself.  

\section{Bill Gates could not Rule a small commune in Montana}

I predict that if Bill Gates ruled a small commune in Montana, within some months, some of the men would blow his face away with machine gun fire.  This is because he is not respectful of people and do not consider their well-being as important.  Sooner or later frustrations would lead to his bloody demise.

\end{document}