\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Bill Gates Reasoning for Invading My Deep Interior and Harming Me in Irreparable Ways}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Disclaimer: I am Far more Important to America and World Than Bill Gates}

My Four-Sphere Theory is correct and is supported by Freeman Dyson as correct; he is sufficient to ensure that I have contributed far greater things to America than Bill Gates has.  Bill Gates' Microsoft has not produced anything as spectacular as Four-Sphere Theory and Final Laws of Macroscopic Nature. Furthermore, I have elucidated the Moral Universal Nature of Human Beings with Discovery of Exponential Laws, and challenged Adam Smith and John Locke showing how Social Needs are more important to Self-Interest than Money, and relating the failures of Classical Liberalism to disintegration of marriages in the world.

\section{Bill Gates Invasion of my eyes and violation of my Natural Rights}

Bill Gates says he 'took opportunity' to harm my eyes and destroy my interior and harm various parts of my meta in horrible ways for the service of white supremacy in America.  There are numerous problems with this.  First of all, America is and was always a Multi-Ethnic Classical Liberal Democratic Republic.  It was never a White Country; this is a myth of nineteenth century south for 'White Race' actually never existed.  America was a colony of multiple European ethnicities and the founders would not have succeeded by ethnic principles to have a coherent country at all without taking a Universal view of politics, and so we are not ethnic in our orientation.  Second of all, I am American.  I am not Indian visiting America.  I am an American immigrant with 33 years in this country.  Bill Gates was a traitor to America by harming me.  He harmed not a foreigner in a foreign land but an American on American Soil.  I am a Princeton Man who has had a Permanent Residency that is valid since 1997.  Bill Gates is thus deluded in multiple ways here.  First of all, that there is any 'advantage' in harming non-whites for the sake of discovery of how to enslave them or whatever it is these deluded white supremacist cunts think they are doing. Second, he violated deep American principles:  he violated Natural Rights of someone in America {\em pretending} to serve American interests.  Since he says "Natural Rights are claptrap" I deeply doubt whether he knows a goddam thing about American interests in the first place.  American Interests are security of Natural Rights at home and across the globe.  It is not destroying blood and Ancestral meta of random Americans who give you something that makes money for you, for I just did some considers with him that led to him putting in \$2 bn into Medium Frequency Strategy traded by D. E. Shaw \& Co. I wanted \$120 mn which is my cut and he intervened to tell me that I was not worth it and then proceeded to use US War meta to harm my Body meta, penetrate and destroy blood meta, Ancestral, Family, bend and rot my front tooth, and do enormous damage to my interior meta claiming 'white right'.  He does not represent American interests and his convictions are worthless.  He is a malevolent Demon without any conscience or moral compass, and is not an asset to America but a monster and deceiver who brings shame to our country.  He ought to be destroyed and killed without a second's thought to people who actually love America.  America has no interest in enslaving anyone at all and since 1945 have stood strong against violations of Natural Rights and slavery across the world.  He is the {\em most anti-American miserable useless deceiving lying malevolent low life son of a bitch in the world and not just America} and ought to have been aborted before his birth.

\end{document}
