\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Motorcycle Rear Wheel Torture Device of Bill Gates Discovered by Henry P. McKean} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Meta is Physically Real}

I expect the reader to accept that meta activity is physically real in the physics sense and has actual consequences to the body and mind.  These are not subjective issues; the current Age of Empiricism is not yet able to handle this but Four-Sphere Theory allows Science to advance to handle these.

\section{Henry McKean's Discovery}

Henry P. McKean is a great mathematician of the twentieth century and although I have never met the man personally, I have a lot of trust in him because like Elizabeth Waltien (nee Kenneally) and Jeff McNeal, he is likely Catholic and for some reason even more than my family members I am liked and assisted by Catholics of this particular region, Ireland/Scotland.  I do not have an explanation for why.

\section{What H. P. McKean found}

I was complaining about not having a couple of Ph.D.s and a tenure yet and his consider found the contraption that Bill Gates had placed in my meta after cutting into my eyes.  He had done many other evil things as well.  This contraption was a high powered motorbike with some chains attached to the running rear wheel that would cut into my flesh and cause pain.

\section{My Comments}

First of all, in the past few days I succeeded in testing Aristotle's theory, specifically his general claim that virtues lead to a happiness of a particular sort.  This theory is one of the most nontrivial claims of all of moral theory.  It is a deep claim, in particular because it does not rely on the idea that moral reckoning occurs {\em after physical death in the afterlife} which is quite powerful mythologically, and is the basis of Christian and Muslim theology and also harkens back to Ancient Egyptian theology.  My parents an family are quite taken by this sort of thinking while I, who had been Atheist since 1979, am not.  Aristotle's theory is highly nontrivial for suggesting that there is a certain type of happiness that is the result of virtuous character that is actual and in the lifetime of individuals.  

I have shown with measurements from World Values Survey that for a class of Virtues Life Satisfaction is measurably higher for Virtuous than non-Virtuous people.  Furthermore, there are interesting directions for querying whether for another class of Virtues,  $B$, whether they are indeed virtues or not.  These are issues of truth that will affect the future of billions of people, and I brought enlightenment to a question that had been confusing for more than two millenia.  

In contrast, Bill Gates has been violating my Natural Rights in the same period and working of various disgusting torture devices in my meta, showing his rather primitive mindset and values, which shows no empathy for the suffering of another human being, myself, and indeed he claims that non-white people are not susceptible to pain, which is of course erroneous as even fifth graders today around the world know that even fish feel pain.

The decision of his is literally criminal, and I suggest to the US Senators that if they do not kill Bill Gates soon then I will be extremely pleased when they are subject to firing-squad execution right in front of Capitol for their failure to secure my Natural Rights and for corruption of our nation's government by coddling and cozying up to evil criminals like Bill Gates. 

Bill Gates is obviously infinitely inferior in his moral virtues and conscience as well as his intellectual productivity compared to me.  Great geniuses like me work on problems whose solutions will improve lives of billions of people and lead to higher flourishing civilisation of my Beloved People the human race, while people like Bill Gates are too low and inferior in their understanding of civilised norms and too illiterate to have educated themselves about laws of the land and international laws or to know what constitutes civilised bounds of behaviour and what exceeds them.

\end{document}