\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{How Bill Gates' Undereducated Views on Race and Power are an Embarrassment to White America}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{American White Disapprovale of Intermarriage is At 13\%}

The American People's consensus has changed over the past century and today White American disapproval of inter-marriage is 13\%.  In fact, I have a very good statistical model that predicts that this will reduce to zero in around 90 years.  

Now intermarriage is a serious matter in terms of acceptance of multi-ethnic reality because acceptance of white daughters being married to non-white men is a significant change for White American fathers.  And yet this is precisely what has occurred through the twentieth century.
 

\section{The Above is an Indicator towards Single Human Race}

The truth is that the Human Race is a Single Race, and all non-African people of the world are descendents of a meta-tribe in East Africa 75,000 years ago.  But recent centuries had seen slavery of blacks in American South, difficulties of America in dealing with racial differences.  But they are in a sense simply matters of ignorance.  The {\em entire time} both whites and blacks were literal cousins of 75,000 years which was not clear to scientists and is now thanks to highly reputable peer-reviewed high quality scientific work published in top science journals in the past few decades.  

\section{White Supremacists like Bill Gates have at most 9\% support among American public}

Instead of analysis of recent episodes such as Charlottesville and Christchurch in New Zealand where people have been killed by White Supremacists, we can take a broader view, and consider the American history of race.  In the scheme of things, 1865 is not so long ago, and this was roughly the moment of Emancipation of Slavery.  In the period of 1776-1865, America was actually inconsistent with the Declaration of Independence, for "all men are created equal" while mandated by the Governments' foundation did not get sanction from American Southern Society. A century and half later, it is still not absolutely clear to 9\% white supremacists and to Bill Gates that "all men are created equal" is simply universally true, and there is no actual "White Race" at all.  Here people like Bill Gates hold ignorant uneducated views that are far behind the consensus view of American public, including White America generally.  

\section{Acceptance of Single Human Race is Inevitable}

Since it is {\em true} that the entire Human Race is a Single Race, it is therefore inevitable that eventually it will be accepted by everyone on Earth.  But the process to equilibrium will have all manner of frictions including stubborn and stupid convictions of people like Bill Gates who will continue to believe that "Hammurabi was white" which is absurd because Amorites in the Middle East (Iraq and Syria is the locus of Mesopotamia) had no chance to be white in 3200 BC.



\end{document}