\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Bill Gates is the Most Miserable Treacherous Ingrate This World Has Ever Produced}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates Bit the Hand That Fed 
Him}

Bill Gates only grew wealthy because United States of America secured his Natural Rights when in most other Old World Countries the Nobility would have been incensed that a commoner is gaining wealth and used their powers to seize his assets and put him in his place, perhaps extort him, and do other things that Nobles do when a punk commoner starts gaining more wealth than themselves.  They would have been right to do this in my view, too.  But America was so generous and kind to him that America secured his Natural Rights for Ages.  He lied and deceived everyone and grew big from the milk and kindness of the Nation.  

\section{The Vile Treacherous Turn of Bill Gates}

With \$130.5 billion to his name, after lying and cheating and murdering surreptitiously Bill Gates now considers "Natural Rights are claptrap".  He violated US Commercial Civilised law by denying me, an American's, fair value compensation for my good work, by blockading \$120 million from D. E. Shaw \& Co.  He is the most miserable pathetic vile treacherous snake, to turn against the sacred foundations of the very Nation that had nurtured his growth, and turn against it, and violate its sacred Natural Rights.  

\section{Bill Gates Deserves to Be Killed For His Treachery}

Bill Gates does not deserve to live.  His vile treachery will resound through history, and his menial trivial achievements will be seen for what they are, trivia.  Only his vile Character, his propensity for Treachery against the kindness of his Nation will be remembered.


\end{document}