\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Bill Gates is Absolutely Unqualified and Without Talent In Finance and has no business in judging Good Quality or Bad For Finance Work} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates Calls My World Class Work In Medium Frequency "Trivia" and Denigrates It}

My Medium Frequency Alpha Strategy is based on world class breakthrough in Finance that was recognised by Robert Merton, by Andrew Morton, by Ronald Layard-Liesching and is traded by D. E. Shaw \& Co. 

But Bill Gates whose incompetence in Finance is beyond all bounds, who is an illiterate uneducated little shit with no talent whatsoever in Finance denigrated my work.

Of the \$6 billion invested with D. E. Shaw \& Co. on my strategy, Bill Gates put in \$2 billion.  And it is spectacularly successful in profitability.

And yet, Bill Gates has continuously denigrated my work as 'trivia' and denied me my just compensation for my work which D. E. Shaw \& Co. admits is \$120 million.

So this illiterate malevolent little cunt, Bill Gates, is making money on my hard work, while denying me my money while he is living in luxury and I have a sick mom and living on disability abused by my aunt every day in Allen Texas unable to afford my own place in San Francisco.  I am American.  I don't understand how this is even possible in the United States.

\end{document}