\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Harvard Declared Bill Gates Deserves Death And Future Plans of Zulf}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Harvard Law Determines Bill Gates Deserves Death Penalty}

In the long history of the Life of Zulf, there are many worthy events, triumphs and defeats.  But the Harvard Law consideration of March 29 2021 declaring that Bill Gates' invasion of my blood meta deserves Death Penalty is a remarkable event in a remarkable life.

\section{Future Plans}

Assuming Bill Gates is put to death, how to proceed is clear.  I will take \$110 bn of Bill Gates and use it immediately as collateral to borrow \$1.6T at low rates and then refinance all college debt of America reducing the credit spread to reduce the burden on all college graduates and give them uplifting encouraging message to use their education for greater things.

\section{Politics of Gratitude and Reciprocity}

With the entire college educated population of America grateful, I should not get sidetracked by sexual favours of beautiful women and immediately proceed to Global Individual Debt.  American college educated population will form a political protection zone for me and allow me to undertake management of Global Individual Debt with all of Bill Gates' money firmly allocated to help American people so there is no doubt and take China's \$5T in a nice posh San Francisco setting to address Global Individual Debt.  

\section{Global Individual Debt is the Holy Grail for Zulf}

My Holy Grail today is Global Individual Debt.  This will allow all people everywhere to have their potential for having a better life by reducing barriers to approval and assistance for paying back debt.  All sorts of bad juju will be averted because money leads to predatory behaviour in many cases.  All of it can be reduced with Global Individual Debt from San Francisco.


\end{document}