\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Either United States Contains Bill Gates or United States Faces Extinction}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

This is a logical sequence of propositions.  

\section{America Lives or Dies based on Natural Rights}

US Declaration of Independence gives the foundational sacred core of the United States.  It is that governments are legitimate if and only if they {\em secure Natural Rights of people}.  These include but are not limited to Life, Liberty, Pursuit of Happiness.  This is what is special about America, and the sacred core of America.  We are Americans because our collective adoption of the principle that all people everywhere have Natural Rights and they are not granted by anyone; they are 'endowed by the Creator', i.e.  Nature.  United States Government's major role is to {\em uniformly over 320 million} secure Natural Rights of everyone.  That is not just one function but the only fundamental function of the American Government.  It is the {\em prime} function that is highest in priority for American Government.

\section{Bill Gates has special tricks for killing 'little guys' with meta power}

Bill Gates is big in meta, and he has habituated himself to being able to use meta power in various unorthodox ways to do things like stop people from breathing and kill them.  He has habituated to murder in this way, I claim, for the past 45 years and he has made this one tool among his others for power.  This is difficult to believe for pure empiricists, but assume for the moment that I am right and he does have such unorthodox methods. 

\section{Assuming Last Assumption Bill Gates puts America in Danger of Extinction}

Since Bill Gates is 'big' and most Americans are 'little guy', he has managed to produce methods for murder without detection in America.  He implicitly threatens the Natural Rights of all Americans using unorthodox means of power.  This immediately implies that United States Government has increased tasks to secure everyone's Natural Rights from Bill Gates because he is lawless.  He explicitly considers -- for the purpose of usurping the power to kill from the state--Natural Rights to be 'claptrap'.  In considering this, he implies that he wants to have the unilateral power to kill Americans extrajudicially.  

\section{Given the Above United States is duty-bound to kill or contain his power}

United States Government is in dereliction of duty, its primary function when it does not either kill Bill Gates despite his usurping of State monopoly of right to kill extrajudicially without detection using unorthodox meta means.  Furthermore he has for the last 45 years habituated to killing without detection or suspicion many people by confession in meta.  

\section{United States Risks Extinction if Bill Gates is allowed to continue}

Bill Gates must either be killed by the American Government in order to assure the American public security of their Natural Rights or the Government must provide credible evidence that he does not pose a threat to the Natural Rights of American people.  If, as I suspect, many murders will be found to have been committed by him for his contemptuous attitude towards killing the 'little guy' using purely meta means, he ought to be under continuous meta surveillance since he has repeatedly expressed his attitude that he is immune from US Law if and when he murders Americans using meta methods.


\end{document}