\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf Nominates Bill Gates For Academy Award for Best Supporting Actor for Five Decades}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Not Even One Claim About Bill Gates in His Documentaries is True}

Bill Gates has numerous self-promotion documentaries where he presents various themes, anecdotes, promotes his own acumen and intelligence, his reading material, his philanthropic triumphs and so on.  

All of it is complete fiction creatively imagined for public consumption and are complete fabrications.  However they are quite popular.  So I am nominating Bill Gates for an Academy Award for Best Supporting Actor.  His actual malevolent continuously power-hungry, greedy, malignant, destructive, hateful persona is completely transformed into a saintly philanthropic facade with all manner of good hearted deeds that never took place, all manner of concern for the well-being of other people that do not exist.

Bill Gates' intellect 
and education is extremely bad, and his coding is mediocre.  But his acting performance hiding his actual character is quite spell-binding and compelling.  

Sometimes his fake documentaries bring tears to my eyes.  I heartily recommend his fiction documentaries as models of deception and recommend that those who would like to live totally fake lives consume them with keen attention.

\end{document}