\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Bill Gates is a Fifth Column For America}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\epigraph{I can't stand it I know you planned it
I'm gonna set it straight, this watergate
I can't stand rocking when I'm in here
Because your crystal ball ain't so crystal clear
So while you sit back and wonder why
I got this fucking thorn in my side
Oh my God, it's a mirage
I'm tellin' y'all it's sabotage

So listen up 'cause you can't say nothin'
You'll shut me down with a push of your button?
But yo I'm out and I'm gone
I'll tell you now I keep it on and on

'Cause what you see you might not get
And we can bet so don't you get souped yet
You're scheming on a thing that's a mirage
I'm trying to tell you now it's sabotage}{Beastie Boys, "Sabotage"}

\section{I am American}
I immigrated to America in 1987, and have had Permanent Residency since 1997.  I am extremely familiar with the sacred foundations of my home country, America.  The sacred core of America is Natural Rights of Individuals and their security as the purpose of government.  

\section{Bill Gates is not American}

On the surface, Bill Gates seems like some others who are Americans.  But Bill Gated says "Natural Rights are claptrap" and is a defiler and desecrator of the sacred core of America.  He is a Fifth Column in America, an internal threat, a traitor to the very sacred foundation of the Nation.

\section{We Must Strive To Drive Bill Gates out of America}

Bill Gates is a threat to the United States of America, and will cause great harm to the American people if he is allowed to continuously deceive Americans about his intentions.  He is an Evil Malevolent Demon whose good benevolent nature is a facade, and his true intentions are to destroy America, and to degrade Natural Rights.

\end{document}
