\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{United States is not a Random Toy of Bill Gates it is a Rational Construction}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\section{United States has classification of Power}

United States is a Classical Liberal Democratic Republic.  United States has a specific judgment regarding Power.  United States considers Power to be {\em legitimate} when Power secures Natural Rights of people and {\em illegitimate} otherwise.  United States is not a chaotic construction of a den of thieves.  It is a construction of Reason.  It does not consider all Power to be legitimate.

\section{Bill Gates Abuses Natural Rights with Power}
Bill Gates had cut my eyes deep into my blood meta and destroyed using his assistant from Israel my Ancestral Meta, damaged my Body meta (violating Geneva Conventions) and done many other outrageous (and unforgivable from every moral law in history) perspective.  He is obviously a threat to the Natural Rights of all Americans.  This is his ordinary use of Power.

\section{Either/Or}
United States was constructed to secure Natural Rights of all Americans including myself.  United States is not expendible -- to 320 million Americans and not to the officials of United States, while Bill Gates is expendible.  United States has the Power and tools to execute Bill Gates and is obliged to do so in order to secure Natural Rights of Americans including myself.  If it fails to secure Natural Rights for me then he is a threat to Natural Rights of other Americans, and then United States Government, for having failed to secure Natural Rights has no legitimate purpose of existence; i.e. it ought to be dissolved.  

\section{Bill Gates ought to be expended}

Bill Gates is not necessary for United States to exist, and is a liability for the existence of United States because he uses Power to abuse and violate Natural Rights of Americans.  Therefore Bill Gates will be expended since United States will want to continue to have legitimate existence and is not barred from executing Bill Gates. 

\section{Power is a tool and has no self-generated legitimacy}

Bill Gates believes that Power makes its own legitimacy.  This sort of belief cannot be acceptable to the United States from anyone who is on American soil with actual effects on other Americans.  He is a danger to the existence of the Classical Liberal Democratic Republic of America and ought to be executed immediately.

\end{document}