\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Bill Gates Plan to Enslave the Human Race and Rule Earth}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Issue of Seriousness}

This is not a work of fiction.  This is a matter of actual serious danger threatening the entire Human Race.  This is not satire.  I repeat: this is not satire, this is not a matter of comedy; this is not fantasy.  

\section{Bill Gates Plans to Enslave Nonwhites and Produce A White Racial World Order}

Bill Gates has a lot of power in America, and he believes that he has enough power to create a secret White Racial World Order and enslave all non-white people of Earth by horrific destructive US military and other stolen illegitimate meta powers.  

\section{Bill Gates is a Deceiver and is not a Benevolent Philanthropist}

Bill Gates is thought to be a benevolent philanthropist in America.  He is in fact nothing of the sort.  All the documentaries and  public presentation of him as a benevolent philanthropist are complete fiction.  He literally totally invented things like how he was given newspapers for free from a newspaper vendor, looked for him for months, found him, and wanted to repay his generosity. That is just one example; all stories of benevolent behaviour of Bill Gates are total fiction.  In reality his is the most malevolent murderous man who had ever lived on Earth.  In fact, he is a pure actual Demon born of human womb whose Evil Plan is actual enslavement of all nonwhite people by meta and producing a dystopian White Supremacist World Order which eliminates Natural Rights for seven billion people and he and his cronies have right to kill anyone -- especially nonwhites -- at will.

\end{document}