\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Bounds of Intolerance levels in Far Right in Democratic Politics}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Parameters for Tolerance in American population}

We estimated $\lambda=0.2462$ in $I=[0,10]$ normal scale where 10 is low interest in respect and tolerance of other people.  We were surprised that we would have to put Bill Gates at $x=52$ in this scale to match rarity of his behaviour.  

In this note we consider the scope of intolerance in Democratic politics in America.  

In order to do so, we consider $\lambda=0.2624$ as invariant.  First of all, the mean intolerance is $x=4$ so majority of Americans will not ever be intolerant towards nonwhites or anyone else.  This means that any political party that wants to consider Democratic politics will necessary be considered minority.  

Our tool of exponential distribution allows us to consider some scenarios easily.  Let's consider the range $x>8$ as population that is intolerant towards nonwhites among American whites.  This actually is a reasonable value and the tail mass is $p=0.1395$.  America has around 60 percent whites so an all-white political intolerant party could control around 8.4\% of the votes.  And this is roughly impossible bound because there are no more people for this level of intolerance if $\lambda$ is invariant.  This is less than percentage blacks in America, and the white population with $x<8$ will not really be interested in this party at all.  And intolerance level 8 is not extreme, maybe just a bit xenophobic.  This is good because this tells us immediately what is feasible.  

What if we up the intolerance?  The party would shrink.  For $x=10$ we will have 5.1\% of American people.  

This is a relief for me because I don't want massive changes in law by these sorts of intolerant people since I am American and I am not white.


\end{document}