\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Elementary Theory of Why Character Is More Important Than Ethnicity} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Stop with the 'Politically Correct' Nonsense}

I am extremely annoyed at racially biased people.  I will today go through a simple exercise to illustrate issues of why Character matters more than ethnicity.

First of all, there are good people and bad people of every ethnicity.  Suppose you have a baby and you put the baby in the car and go somewhere.  You have an emergency stop and for whatever reason you have to ask someone to keep an eye on the baby for a few minutes while you run into a convenience store to buy something or other.  You look around and you have some strangers you could ask to do this favour for you.  Some of the candidates are black and some of them are white.  

You will obviously be putting your baby in grave danger if all the white candidates were baddies, criminals and crooks who are interested in harming your baby or stealing your car and the black people were goodies who are the norm.  That's the obvious hypothetical example.  

Now let us take a look at burglary statistics by race from California in 2000-2004. Number of burglaries average 2354 for whites and 688 for blacks.  California population is 36.6\% white and 5.5\% black.  In this case, it is true that the rate of burglary for blacks is around twice that of whites.  However, there are 2.1 million blacks and 14 million whites.

Let's see now.  Suppose 1\% of the whites are baddies, and 2\% of the blacks since we are looking at burglars.  Total number of white baddies is 140,000 and total number of black baddies is 42,000.  This implies that if you had a random sampling of say 10 people from the population, you want to compute the probability P( Black Baddie | There were 8W and 2B in 10).

Now
\[
P( All Blacks Goodies ) = 0.98^2 = 0.96
\]
and
\[
P( All Whites Goodies ) = 0.99^8 = 0.922
\]
Thus in California, if you saw 2 blacks and 8 whites the probability that the blacks are both goodies is higher probability that the whites are all goodies.

Fine, this is an artificial example.  The point is that you don't actually care about white or black. You care about picking goodies rather than baddies.  A black goodie will keep and eye out for your baby and not cause problems as well as a white goodie.  But if the person you pick is a baddie, then you are in trouble.  

Here I used burglary statistics, but as you can see the goodie percent difference is 0.99 versus 0.98, both quite close to 1.00.



\end{document}