\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Ethnicity Contributes to 14\% of the Variation in Child-rearing Morals of the Human Race} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle


% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Sat May 22 02:33:20 2021
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & mean & sd \\ 
  \hline
good manners & 87.533 & 7.804 \\ 
  independence & 46.360 & 12.678 \\ 
  hard work & 52.448 & 13.899 \\ 
  feeling of responsibility & 71.369 & 8.442 \\ 
  imagination & 24.169 & 11.750 \\ 
  tolerance and respect for others & 67.135 & 10.089 \\ 
  thrift saving money & 32.600 & 15.276 \\ 
  perserverence & 32.025 & 16.008 \\ 
  religious faith & 54.470 & 18.578 \\ 
  unselfishness & 30.448 & 16.802 \\ 
  obedience & 38.810 & 21.694 \\ 
   \hline
\end{tabular}
\end{table}

\section{My father's love was always strong,
My mother's glamour lives on and on,
Yet still inside I felt alone,
For reasons unknown to me}

The table shows that the variation due to ethnicity for the mean percentages who think the relevant quality is important is 13.91\% across 11 questions of World Values Survey Wave 7.

\section{The power of youth is on my mind,
Sunsets, small town, I'm out of time.
Will you still love me when I shine,
From words but not from beauty?}

We cannot say that 14\% is totally negligible, but it is not significant enough to produce all manner of multi-species separations of the Human Race.

In particular, the ethnicity-effects are responsible for variation of 13.91\% with a standard deviation of 4.3\%.  In other words, these numbers bound how much ethnicity intervenes in child-rearing morality.  This is one of the most precise estimates of effect of ethnicity on human child-rearing morals on planet Earth that has ever been examined, for it tells us 
\begin{itemize}
\item There will certainly be variation due to ethnicity but this variation will be around 14\%, the interval $( 9.7\%, 18.3\%)$ will explain 
the effect.  
\item{The uniformity of ethnicity effect and its bounded nature is a major discovery by us.  No one had suspected this before our discovery}
\end{itemize}


The rest of the variation, $(81.7\%-90.3\%)$ will have no ethnicity effect after this.  

This is not easy for us to absorb and understand because we live our lives from the subjective perspective

\section{Where have you been? Where did you go?
Those summer nights seem long ago}

I love Lana del Rey's "Old Money".  Also another song that I remember often is "Reckoner" with its haunting "because we separate like ripples on a blank shore ..."  

Blue hydrangea, cold cash, divine,
Cashmere, cologne and white sunshine.
Red racing cars, Sunset and Vine,
The kids were young and pretty.

\section{The Probability Theory}
This note showed the value of ethnic difference precisely in 11 Bernoulli random variables, which are the probilities of whether the given factor of child rearing morals are important or not important.  I have shown elsewhere that ethnicity is negligible in various values, morals, social measurements.  The situation here is easier, because we understand Bernoulli random varibles, so we can get precise variation due to ethnicity (our answer is 13.9\% or a 1-sd interval $(10\%,18\%)$ and in the future we will gain more precision. 

The right way to approach these issues is to consider all Human Race as one people and ethnicity as an {\em attribute} that is separate.  This then allows us to measure ethnicity effects without getting confused.

You are not your ethnicity, just as you are not any part of your body.  And we now have access to some deep truth, that ethnicity does have an effect and it's effect is bounded and relatively small.
 
\end{document}
