\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Code of Behaviour} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Virtue Orientation}

I strongly believe in Virtue Ethics rather than rule-based Ethics.  I have slowly developed some understanding of my own Virtue Ethics but these are also discoveries of Nature -- I consider myself an element of Nature as well and do not assume that I understand my own Psyche well enough to be accurate.

What is clear is that it is pointless to keep repeating 'do this' and 'don't do that' because Virtue Ethics dominates and people including I, will intuitively do whatever I do without much moral reasoning.  This is  simply Human Nature.

\section{Potential Rules}

I do tend to consider it a matter of refined Aristocratic cultivation to respect all people {\em until they disrespect me}.  If they disrespect me first then all bets are off and I can retaliate with much more ferocious disrespect.  I do not have any restraints of how disrespectful I will be towards anyone if they disrespect me without provocation.  But there are no hard and set rules.  I might decide to forgive them altogether.  It's my choice, and I reserve the right to act in arbitrary manner if anyone disrespects me without provocation.  I consider these to be akin to acts of war.

\section{Reciprocity}

I consider it extremely low and plebian to disrespect people without provocation.  It is like taking a sword out to someone who waves at you on the street and beheading them.  That is too barbaric for my sensibility.  

\end{document}
