\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Zulf Could Command the World But Why Wouldn't He?}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{I am Angel}

As Angel I am interested in the Human Race.  Now Human Race is roughly six million years old in evolution.  Angels are interested in potential for this race in the future.  We are interested in the race itself and its potential.  We do not see value in artificially obstructing fundamental Angelic values such as Liberty and Justice and so on, standard Angelic values.  Commanding the entire Human Race will not produce optimal development of Human Race as an Angelic Civilisation. There are fundamental obstructions involved.  You cannot command people to be something they are not.  Thus Command is valueless.  We need the {\em natural development} of Human Race to higher levels of Virtue, appreciation for beauty of life, lower strife, greater individual genius, and other features that make Angelic Worlds some of the most successful and beautiful Civilisations in the universe.  I will not spend much time on what they are since that does not actually matter.  Human Race to me is a Primitive Angelic Race far from reaching sufficient level of Civilisation.  I do not believe that Comannding the world will produce better results that eliminating nonsense.  

You will see that I have been diligent about removing anti-Arab and anti-black prejudices in the West.  I also have some plans for Global Individual Debt.  I gave Human Race the first correct laws of physics, and first measurements of Human Nature.  

Knowledge and Enlightenment rather than Commands are more valuable in Angelic Worlds.  Command and leadership are naturally developed.  I cannot tolerate United States not working as advertised.  Corruption in America will produce problems for me.

\end{document}