\documentclass{amsart} 
\usepackage{amsmath}
\usepackage{verse}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{A New Philosophy For Retail Individual Products and Services}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{A New View of Individuals}

We believe Human Nature constrains individuals to have certain values, opinions and preferences.  Individuals have these values, opinions, and preferences based on deep reasons of genetic evolutionary history of their ancestry for more than 6 million years whether they are themselves aware of this or not, and their preferences are much more {\em inflexible} than they themselves are aware.

Let us define these values as "Human Nature Values".  For these Human Nature Values, they are unlikely to change their views and will remain stubbornly inflexible quite naturally.  

\section{Responsibility for Providing Appropriate Products and Services is Burden of Industry}

It is the burden of Industry to cater to the Human Nature Values of individuals.  Products and services that are incompatible with these values will naturally be unappealing to individuals.

It is a complete waste of time and energy to attempt to convince people to purchase and pay for products and services that are incompatible with their human nature values.

\section{My company Thyself Inc. will Patent Organising Products and Services to Match Human Nature Values}

I don't want Bill Gates and other businessmen into taking my genius ideas and making money.  I will plan to patent and charge a great deal of money to Bill Gates shows and others in the industry for matching products and services to the Human Nature Values in all 7.8 billion people.  I will cleanly work out this division, and I want Bill Gates shows to continue to flounder with primitive incomprehension of the fact that they cannot sell arbitrary products and services to vast majority of people whose preferences are not respected by them.  

We believe "Market Testing" is a primitive method of determining what is acceptable by the Human Race and our method of starting from World Values and then determining what products and service ought to be offered is superior, and we'll patent this approach immediately.

\end{document}