\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Consequences of my Death by Efforts fo Bill Gates}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Harvard Response Expected}

I asked for tenure at Harvard, so if I die by efforts of Bill Gates to kill me by meta, if successful, allows Harvard to consider me a great genius who was Angelic and Saintly, a genius and a Saint, who contributed to Laws of Nature that are permanent in Physics, and laws of Quantitative Moral Nature of Man, establish that Human Race is Angelic with exponential tail that is Hobbesian.

A saintly man who suffered and died at the efforts of a malevolent man who was barbaric and racist at the wrong moment of history while he cavorts around in yachts and has \$120 bn but withholds \$120 mn owed to me instead is good material for Hagiographic extravaganza for Harvard, {\em especially when being dead, he cannot embarrass Harvard at all}.  

\section{Bill Gates will lose all gains in reputation and be considered Baddie}

Bill Gates will be considered a global villain because his PR cannot handle a public murder right in front of everyone's eyes with voluminous emails and other writings to detail my viewpoint.  He is in my meta with a great deal of unorthodox -- well that is a euphemism -- it's totally vile destructive, mixing all sorts of hard industrial and US military meta and knives and torture devices in my soft meta all starting with a violation of Geneva Conventions.  His good reputation in Earth will evaporate, so I will have unmasked Bill Gates as a Super-Villain of the James Bond type.  This will go wherever it goes.

\section{United States Will Have a Wake-Up Call from all Sorts of Wars to Shoring up Natural Rights at Home}

United States is a bit lost having expended two decades in Crusades against Muslims begun by Israel blowing up Twin Towers and blaming Muslims.  True to my expectations, there was no triumph because there was no reality to 9/11 and Muslim menace at all, so wars based on fictions do not have any satisfactory quality and there has not been any satisfactory meaning for American people from these wars.  A refocus on inner principles and securing Natural Rights at Home by United States Government is very good for us, because we will face the rise of Asia, and this example of Bill Gates shows how thin our adherence to the principles that actually matter and we wish to represent are.  Bill Gates is a vile Barbaric Ostrogoth without any clue about what Natural Rights are, thinks Hammurabi was white, and non-white people are not susceptible to pain while his PR seems to suggest he is erudite and intelligent.  America will have to clean up its own House badly.

\section{Racial Strife will be Evaded Once Bill Gates is killed}

Racial Strife in America is abnormal, as I have shown, since tolerance taught to chilren is high among white people as well as acceptance of intramarriage.  It is my fate somehow that Bill Gates happens to represent views that are alien to most white people on Earth and he is still quite wealthy and I have the opportunity to battle him or be his victim or whatever you want to call our conflict in meta, and supposing he succeeded in killing me, we have an interesting sort of dramatic situation.  I have absolutely no apoplogies whatsoever for anything I have said about him, whether I die or live.  That was a great decision by myself, and I am immensely proud of it.

\end{document}
