\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{On The Credibility and Quality of the World Values Survey Datasets I Use}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Introduction}

For all my Quantitative Human Nature work I use data from World Values Survey, generally Wave 7, but also some earlier Waves.  The data are available in R data format.  I accept the data as is and do my analysis on an Ubuntu 20 AMD machine here in Allen Texas, second floor of 915 Meadowgate Drive, Allen, TX 75002.  

I worry about questions of ethnicity and various other human traits.  I use the data from World Values Survey because I don't shy away from controversial conclusions and I don't want to be defending against people who accuse me of having biased samples.  The people behind World Values Survey are some of the most creditable Social Scientists in the world, and many of them are white.  This is an issue because Bill Gates is a white supremacist and claims that my data are not good.  These are not data collected by any secret cult of non-white people out to destroy the reputation of white people.  These are high quality data collected by professional Social Scientists for valid research purposes that they were kind enough to make available to the public.  All my analyses can be replicated with my R code by anyone.  Moreover, I do not gain any income at all for my work on these; I do them for my own pleasure and as a labour of love for my Beloved People the Human Race.

None of the racial supremacist camp can find any problems with my data; indeed, racial theorists typically do not do open research, and it is their data that is much more likely highly biased than mine. This is because I am simply a straightforward honest scientist doing honest open research and they have malevolent and dystopian political projects rather than open inquiry.  

I think it is rather funny that they, who do not share their sources, who do not publish openly and are out to prove absurd theories of racial supremacy based on weak data, should challenge open source data from World Values Survey.  They won't get very far this way. 

\section{About World Values Survey}


The World Values Survey (WVS) is an international research program devoted to the scientific and academic study of social, political, economic, religious and cultural values of people in the world. The project’s goal is to assess which impact values stability or change over time has on the social, political and economic development of countries and societies. The project grew out of the European Values Study and was started in 1981 by its Founder and first President (1981-2013) Professor Ronald Inglehart from the University of Michigan (USA) and his team, and since then has been operating in more than 120 world societies. The main research instrument of the project is a representative comparative social survey which is conducted globally every 5 years. Extensive geographical and thematic scope, free availability of survey data and project findings for broad public turned the WVS into one of the most authoritative and widely-used cross-national surveys in the social sciences. At the moment, WVS is the largest non-commercial cross-national empirical time-series investigation of human beliefs and values ever executed. 


\end{document}