\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf Will Now Test Whether the Zulf's Version of Critical Race Theory is True}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Zulf's Version of Critical Race Theory}

My version of Critical Race Theory is not deep and complex in its assumptions.  It is specific and concrete.  

We will say "Zulf's Version of Critical Race Theory is False" if for every case where there is a White Man who is doing all sorts of evil things tantamount to murder in progress against a non-white man and the US Federal Branches all immediately intervene and kill the White Man because it is obvious a murder is in progress and the US Federal Branches appropriately kill the perpetrator of the murder.  In this case, bomb the bejeezus out of Bill Gates and kill him for doing this sort of thing for months against my interests.

We will say "Zulf's Version of Critical Race Theory is False" if instead there is a lot of alternate hypotheses in the three US Federal Branches which might include "Well 2+2=4 is conventionally true, and we think that it's generally true, but there are exceptional cases when 2+2=5 and so we should wait and see whether Bill Gates changes his mind and does not continue to harm Zulf in the eyes and try to murder him as he has been doing nonstop for around a year."  This is where the white people in the three Branches, like Martin Luther King's "white moderates" will find every excuse to allow Bill Gates to murder Zulf every day pretending that today is the day that Bill Gates, who is an evil murderous malevolent cunt will turn a new leaf over at 66 when this is the sort of thing he has done throughout his life.  That is Zulf's Version of Critical Race Theory.  It is not exactly that all white people are in agreement with the White Man who is the Evil Murderer, but they will come up with ways to "Save his Soul" {\em at the expense of the non-white victim} who is confused because he can't understand how a murder in progress by a murderer who is an evil malevolent cunt and has been one for 66 years is going to suddenly without incentive turn into an actual philanthropic saint.

\section{Tribal Sympathies Are Primitive}

I am quite interested in primitivity of the entire human race of all ethnicities.  We note that today Christianity has existed for around two millenia and Islam for a millenium and half very roughly.  Both of these religions are supra-ethnic and universalist.  Both have had success.  Given their success, sympathies of tribal ethnic sort which de-humanises those of other tribes can and should be considered {\em exceedingly primitive}.  This sort of primitivity exists in all ethnicities to some extent, and are not restricted to European ethnicities.  Lack of empathy for victims of malevolence of Bill Gates will have a {\em probability distribution} among whites.  Since Bill Gates is murderous and has a record of murdering people in the past, and his victim, Zulf, is law-abiding American without much record of murder and violation of other people's natural rights, those people who are more sympathetic to Bill Gates can be considered exceedingly primitive in their moral evaluations for their moral umbrella must necessarily be restricted to an ethnic tribal balloon and not extend past 'white whites' or whatever they call themselves these days.


\end{document}
