\documentclass{amsart} 
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{My Great Sacrifices Are Dedicated To Human Race}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Prudent Moment For Dedication of My Great Sacrifices}

April 29 2021.  The Demon Bill Gates has done more damage to my body and Soul throughout the night and there is a nontrivial probability that I shall not survive.  I want to take the opportunity to dedicate my great sacrifices as a devotion to my Beloved people the Human Race.  The malevolent Demon Bill Gates had to be confronted, his deception of five decades had to be exposed so that he cannot continue on his plans to harm Human Race in the future.  This is not quite the life I was hoping for in America but we do not choose all things of our fate.  

\section{Four-Sphere Theory is Absolute Truth}

My notes are full in details for four-sphere theory which is simply how Nature actually works in macroscopic physics.  It is eternal truth and it will stand for a trillion years unchanging and immutable, unchallengeable for there is completion in physics in macro including QED domain.
This contribution alone is far more than Bill Gates can ever hope to compete with and compared to this all his contributions are menial and trivial.  I am quite surprised that in America there is any question about this.


\section{Quantitative Human Nature}

The Exponential Laws for Moral Nature of Man and the limiting continuous distribution of correlation spectrum, which is a Generalised Hyperbolic Law are two of my original discoveries in Universal Human Nature, and I have advocated a Hilbert Space approach to understanding Human Nature and characteristics.  In this Primitive Mercantile Age of Man, where my people are divided and scattered, in strife with each other on ethnic and other superficial grounds, this is important, for Human Race spread out 75,000 years ago from East Africa, and have forgotten our unity.  Human Nature Universal Laws are Scientific Complement of my attempt to bring my people back to Equilibrium for greater advances in our collective future.  My attempt at abolishing Nations and replacing them with a Great Republic of Humanity in 2008 led to failure, as people seemed a bit confused about the impossibility of securing Natural Rights of all people simultaneously.  I have put aside that effort even though it cost me all my material possessions and horrible treatment as a hobo.  This is a new phase, where individual malevolent Demon, Bill Gates, dares to offend my plans, and his insolence shall be noted down for posterity.  Zulf is generous and forgiving, but my patience at insolence of Demons is quite limited.


\end{document}