\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Mystery of Nature:  Bill Gates DNA has no non-human element at all but he is a Demon}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates is found to be a Demon by US Government}

US Government just considered and I did not see everything they saw because I have dealt with Demons for many billions of years and don't care.  But they recorded what they found.  So Bill Gates is a Demon.  His body is completely human, and here I want to make a very subtle point.

\section{DNA does not determine some aspects of Character}

Bill Gates' DNA is exactly human, as neither of his parents had {\em any clue at all} that he was a Demon.  Don't ask me how I know.  Ok, fine, I know because I know Angels and Demons.  We are born as humans in this world and elsewhere.  We choose the parents.  The parents think they planned and sussed all things out, but alas, we are Demons and Angels and we pick them and they don't pick us.  So I picked my parents before birth and Bill Gates did the same.  There is nothing odd about his DNA at all; it is 100\% human. 

\section{DNA does not contain the secrets of the Soul}

See, DNA does have all sorts of adaptations of human evolutionary past.  And Western Philosophy has gone through Rene Descartes thinking that the Soul controls the body with seal the pineal gland, and later work established that the physical brain is what really is driving consciousness.  All this is progress in one sense, but in fact the actual universe has a vast purely electromagnetic fourth macroscopic spatial dimension, and so it is important to understand that there there are many things about our Character that is not encoded anywhere in the DNA.  

\section{Why consider someone a Demon than just a Bad Character?}

One does not have to use "Demon" at all; one could just measure badness of Character.  But Demons and Angels are very special Characters and rare in Human Race, and they are exact because that's just part of Nature too.  It's not determined by DNA, and that ought to be surprising to many scientists.  I won't prove this; it's true.  

\end{document}