\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Discovery by Jeff McNeal and US Feds of a Powerful Demonic Hired By Bill Gates to Harm Me} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle


\section{Introduction}

A consider of Jeff McNeal discovered a powerful Demonic, a female, hired by Bill Gates to produce black magics and harm my chances of receiving the Nobel Prize in Physics.  The US Feds are aware of this now.

\section{Bill Gates is a Malevolent Small Cunt}

Anyone with \$130.5 billion net worth living in luxury mansions who hires a Powerful Demonic to hire me, while denying me my \$120 million from D. E. Shaw \& Co. while I am on disability and my mother is on her deathbed is so small, so far beneath contempt, so far beyond any level of civisation, so far beneath the most primitive foragers and hunter-gatherers in their civilisation, that my contempt for this man, Bill Gates, knows no bounds.  He surely ought to have been aborted before birth.  He is a scourge on Earth and a misfortune for the United States of America and ought to be obliterated with extreme prejudice by the United States government.  People like this do not deserve to live.

\section{My Scientific Genius Needs No Nobel Prizes}

There have been no Nobel Prize-winners in history with the sense for macroscopic physics and Nature and her laws that can equal mine; not Albert Einstein, not Erwin Schroedinger, not Richard Feynman, not Paul Dirac, no one in history has had the intuitive genius in the sense for laws of Nature that I have had, and that is why Four-Sphere Theory is close to Eternal Truth.

\end{document}