\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Bill Gates is Deuteronomy-Level In Civilisation} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Rock/Scissors/Paper Of Civilisation}

Bill Gate is Deuteronomy-Level in Civilisation.  He is a hard-core tribal domination man.  This level of Civilisation is lower than what China and India had 1500 BC already, which went past this level to reach higher levels.  Now United States began with a far higher Civilisation than Monarchy even, to a new conception of Man with Natural Rights and Liberty.  It was no Ethnocracy for it could not be, for European immigrants were from different nations and tribes not to mention the non-Europeans.  I am Asian-American.  I am quite aware of this.  Asian Civilisations are superior to Bill Gates' level, and if US Senate coddles this degenerate Evil Malevolent White Supremacist Tribalist, United States will quickly lose ground to the East.  Bill Gates should be bombed to obliteration.  The stakes are high, and I personally will try to execute the entire US Senate by firing squad as soon as I can accusing them of being corrupted by Racialist stains anyway, and demand \$1 trillion in compensation from US Government for failure to secure my eyes and protect me from brutal invasion by this malevolent evil degenerate White Supremacist Butcher Bill Gates.

\section{Status of My Judgments About Bill Gates}

Bill Gates is a man I have never met physically.  My ex-employer Christopher Thorpe, who I knew because he was my younger brother's roommate at Harvard, was a protege of his and worked at Microsoft in his early career.

I came across Bill Gates in the past year in ether only.  He was so malevolent and evil that I had no idea how to react to him for a while and then over time I formed my judgments and convictions regarding him.  My judgments and convictions about him are non-negotiable.  They are protected by First Amendment of the US Constitution, and I plan to make them so public that from California to Japan everyone in the world will know them.  These are not mere opinions.  I believe that Bill Gates is by far the most evil man born in the Homo Sapiens species and he represents the greatest threat to my beloved people the Human Race.

\section{I am Infinitely Superior to Bill Gates}

Imagine a list of illustrious artists and philosophers and professors of linguistic and prominent scientists are in a small bank in a line, perfectly calm and waiting quietly for their turn to conduct business with the bank teller.  Suddenly a van screeches outside and various men with guns enter the bank wearing masks and covering their faces with bandanas and so on.  They take all these people hostage and demand that the tellers give them all the money.  In this situation, I think everyone will agree that the people held hostage, even though their lives are under the control of the robbers, are actually {\em superior} to the robbers in various ways too many to list.  

In the same way, Bill Gates had found some clever evil way of cutting my eye and entering my meta and doing horrible destruction to my Life, Family, Ancestral, Romantic and other meta, and {\em then} claimed with a great deal of racial slurs that he was superior to me because of this evil unlawful act, by illegitimate use of US Industry and US Military powers.  

No one in their right might would consider Bill Gates to be superior for this.  He lied and claimed that he had 'White Right' to commit these great crimes.  Now most American white people are not evil criminals, but Bill Gates is, and he is not superior but {\em inferior} to every decent person who is not a murderous evil criminal for this.

\section{On Being An Immortal Genius}

For several millienia, Human Race, my Beloved People had been confused about issues of ethnicity and race.  I have produced {\em definitive authoritative} and just quite spectacularly clear and straightforward and irrefutable results on how ethnicity effects on human moral values is at most 6.5-9.5\% with the straightforward corollary that {\em all} theories of racial superiority, all of which {\em require} moral superiority, are folly for there is no moral superiority {\em possible} for any ethnicity over any other.  Obviously I will consider all people who do not accept my authoritative definitive results with clear measurements to be rather foolish, ignorant, backward, superstitious, and altogether far too uncouth, unsophisticated, boorish, rustic, and provincial to contemplate.

\end{document}