\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Diary of June 8 2021} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

I woke up after some hours of sleep and pored through E. T. Copson's book on Complex Variables.  On my mind now is that World Values Survey needs to be more carefully understood.  

I thought about whether my experience today is comparable to the experience of a Jewish man in the 1930s Germany.   Bill Gates had done more harm to my eyes than any German Nazi had done to any Jewish man according to Christine Lagarde.  I am a greater scientific genius than Isaac Newton, than Erwin Schroedinger, than Albert Einstein, than Paul Dirac, for as the late Freeman Dyson had said regarding Four-Sphere Theory, "He's right, so he's greater".  

As I write this Bill Gates, who has been cutting up my eyes and harming them is in my meta repeatedly saying, "I'm big" and such.  He is a total waste of my time, and he needs to be relentlessly bombed till he is physically obliterated.  Such a man as Bill Gates ought to be aborted before they are born.  United States of America has not killed him at all, and I do hope that historians of the future, when they do a dramatic reconstruction of "Life and Times of the Great Zulfikar Moinuddin Ahmed" will pay attention to the level of Civilisation in the United States of America in 2021, where the US Senate, the entire bureaucracy of the United States of America, is simply unable to give peace to her greatest scientific genius who is accosted for months by this criminal White Supremacist Malevolent man Bill Gates.  I cannot imagine any civilised nation in history that allowed its malevolent criminals vast powers to harm their greatest scientific minds and did not realise that these criminals ought to be killed so that civilised people can live in peace.  

\section{Appropriateness of Comparison With Jewish Experience Under Nazi Germany}

Bill Gate repeats racial slurs like "Whites Are Superior" nonstop day and night in my meta for a year now, and regardless of whether the rest of America has a different experience, I am an American and I strongly resent this mistreatment by the United States Government where a Racial Supremacist who steals US Military meta is not wiped out and I, the greatest of scientific geniuses, am kept from tenure at Harvard, Yale, Princeton, Stanford or Yale, and have to suffer through through the miserable rambling and use of illegitimate power of this miscreant Bill Gates, who repeats "Natural Rights are claptrap" and still does not have all his assets confiscated and his body put to death, who still has not faced relentless bombing until he is obliterated.  These are what I expect from the United States of America for a Racial Supremacist who has violated my Natural Rights and cut up my eyes.  But the US Government has yet to respond at all.

\section{I Live Once, so My Experience Matters more than general experience of all Americans}

I certainly do not care all that much if the experience of other Americans is different than mine.  In this Eternally Recurring universe, I have to pay attention to my experience.  And at the moment, I am astounded that this criminal illiterate malevolent man, Bill Gates, is not destroyed by the United States Government and is allowed to conduct his evil criminal violence against my Natural Rights nonstop.

\end{document}