\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Exercise of Decomposition of Faith and Science}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Science is the Empirical-measure based inferences in coherent contradiction-free theories}

Four-Sphere Theory is science.  My work on Quantitative Moral Values of Human Nature is science. 

\section{Example of my faith}

I am an Angel of Heaven and have been for billions of years before my birth on Earth, November 19 1973, acquiring a 3000 year Aristocratic line DNA and poverty too.  War of Good and Evil has raged in the universe that is Eternally Recurring for billions of years and involves millions of civilizations and millions of star clusters and galaxies.  Earth is a far from Civilisation, and is a Primitive Mercantile World, an Angelic Race still too primitive to be unified live here, still filled with tribal strife.  I have been here 1180-1300 once before and was an English Knight.

\section{My faith is no more strange than Christianity or Islam}

My faith is not very different from Christianity or Islam.  For example I am fully a believer in my past in one life in an Angelic World quite a bit more advanced from Earth, I along with all inhabitants of the planet died when Demons exploded the star of the system.  I won't try to prove it.  I take it on faith.

\section{Faith: Bill Gates is not Human but Demon}

I will prove to the world that Bill Gates, although he looks like a human superficially is a literal honest to goodness Demon.  I will prove it by characterising Human Race quantitatively in moral qualities and showing that Bill Gates is exceptional in malevolence, destructive agression, and other evil qualities, deceptive, horrific and abominable, makes Jack the Ripper look like Big Bird, and Dante's Inferno requires entire classes of basement floors to put him.  He's an Evil Demon.
\end{document}
