\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Are You Such A Dreamer To Set The World To Rights I'll Stay Home Forever Where 2 And 2 Always Makes A 5} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{The Trouble With White People Taking Pride in Work of Schroedinger and Darwin and Newton}

Erwin Schroedinger, Charles Darwin, and Isaac Newton were great geniuses.  But White People who have no interest in studying their works or dealing with the issues they dealt with with devotion claiming their own {\em pride} based on ethnic association are {\em quite absurdly demented}.  Ethnicity will not give you any of their genius.  What will get you some of their genius is {\em love for the subjects they engaged in}.  I am so sick and tired of people who have zero talent and zero interest in Science but who are full of pride for {\em other people's work}.  

I remember not even five years ago talking to some American White Supremacists on Facebook who kept posting pictures of gorillas etc. about me, and I was not offended, because I don't have any chips on my shoulder about my appearance.  The right lovely ladies are fine with it.  But then I asked them about what they thought about Hermann Broch and Robert Musil, and their answers were so blank I could literally hear the winds across the oceans in their empty heads.  This will not do.  You see, I have more in common with Percy Bysshe Shelley than most of the English Ethnics in America.  That's because I love the poetry and I {\em spend my precious time} on Shelley's poetry while I could 

\end{document}