\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Model of Uncountably Infinite Human Beings}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Motivation}

We would like Social Science to be based on some smooth densities on $\mathbf{R}$.  Now the actual human race is a finite set and we show below we cannot produce smooth densities.  We want to consider embedding of human race $H_0$ into a larger smooth manifold.  We are not interested in doing this frivolously but for scientific models of the Human Race.

This is not so strange.  We could consider for example $H_0 \rightarrow H \rightarrow \mathbf{R}$ where $i: H_0 \rightarrow H$ is an inclusion or embedding and the smooth density is from distribution of $v:H\rightarrow
\mathbf{R}$ so that law of $v$ has a smooth density.

\section{Embedding}

There are 7.8 billion humans on Earth.  Let $H_0$ be a finite set representing them with $|H_0| = 7.8 \times 10^{9}$.  We are not satisfied with this in our view of the world.  We will consider embedding $H_0$ in a Euclidean space $H_0 \subset H$.  This extension is valuable for us.  This is crucial for us.  

We want to take continuous densities seriously on human race measurements.  If we leave finite $H_0$ then if we consider the measurement $v: H_0 \rightarrow \mathbf{R}$ then we cannot have a smooth density for the distribution of $v$.  This is easy to see because the $v(H_0)$ is finite, and therefore we can find an interval in the complement of $v(H_0)$ and the distribution of $v$ cannot have positive mass on it.  

We will extend human race to be represented by $H$ which is a continuous parameter space, say $H \subset \mathbf{R}^G$.  This will allow us to consider functions with distributions that have a smooth density on $\mathbf{R}$.

\section{Steps Toward a Scientific Framework}

We believe Social Science will great progress with an embedding of $H_0 \rightarrow H$ and doing analysis for $H$ and restricting to $H_0$.

\section{Example}

Personality models would embed $H_0 \rightarrow \mathbf{R}^5$

\section{Embedding By Infinite features}

One sort of idea is to embed $H_0$ in an infinite dimensional Hilbert space $H$ as follows.  We suppose that all measurable features of a human being is a countable sequence $\varphi_j$ and $1\le j < \infty$.  Then we take some standard complete Hilbert space and choose an orthonormal basis $e_j$.  Then map $h\in H_0$ to $( e_j \varphi_j(h))$.  Then we want to put a special probability measure $P_H$ on $H$ such that for any measurement $v$ of $H$, we have $v_*(P_H) \in GHD(\lambda,\mu,\sigma, \gamma, \bar{\alpha})$ for some parameters.  

In other words, every measurement pushes pushes $P_H$ to a generalised hyperbolic distribution.

Let us pretend this setup is possible and self-consistent.  Considering the measurements $\phi_j$ themselves we are seeking a GHD on infinite dimensions.

\section{Some Conditions}

We put the conditions that given any two humans $h_1, h_2 \in H_0$ who are distinct, there exist $\phi_a$ such that $\phi_a(h_1) \not = \phi_a(h_2)$.  In other words, these $\phi_j$ separate all pairs of humans.

Second we ask that \[
| \phi_k(h) | \le Ck^{-2}
\]
These conditions ensure that 
\[
\| \phi(h) \|_2 <\infty
\]
where
\[
\phi(h) = \sum_j \phi_j(h)e_j
\]
So we have {\em separability of humans} by our series of metrics and we have square-integrability so that $H$ is isomorphic to an $\ell^2$.

Then we want to put a Generalised Hyperbolic Distribution on $H$ with various projection properties.



[{ \end{document}