\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Notions of Entitlement}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle


\section{Types of Entitlement}

I have been thinking about notions of entitlement for a while, maybe a bit more than a decade.  I was first-born in a relatively poor but extremely illustrious bloodline of Nobility of 3000 years in Bengal, and am American by immigration as boy in 1987, and I was valedictorian in John Adams High School in New York and graduated Princeton magn in 1995.  Thus -- and I think you can see that these would lead to a certain natural level of entitlement -- I was not unfamiliar with the turf of entitlement but it was not based on reflection.  I think that the first time inchoate feelings of entitlement gave rise to any sort of entitlement with real force began late, around 2002-4 when during the Iraq war I had to confront my feelings of Conscience as the war deaths mounted in Iraq and I felt that I had to do something about it.  So even though I had some sense of entitlement as  prince in more than a literal sense internally, the force of entitlement was not in this direction but came from pangs of Conscience and that is the subtle issue of legitimacy of entitlement.  Legitimacy of entitlement from noble lineage, of the 'this is who I am' is, I can tell you with confidence of a lived life, is meagre.  True force of entitlement is deep like ocean currents and is due to having flown far with your Conscience.  A decade or two ago, I could only raise my Entitlement level to a peak on issues of moral nature that affected the entire Human Race on a very limited set of issues.  For example,  maybe against genocides, against nuclear weapons, against those things that affected the well-being of a great mass of people.  And this was in concrete terms a transformative moment, as I realised deeper force arise that accepts the entire human race as your own.  This entitlement allows you on those limited topics to "you miserable fucks why do I have to do everything around here" on the world scale. And this is the key point of entitlement, that one cannot have this level of entitlement as a matter of mere opinion as a democratic ballot.  One has to embrace vaster peoples as one's own not as a posture but genuinely, and I habituated eventually to thinking about the entire Human Race as my people.  One cannot have entitlement at the scale of the entire world as a rhetorical flourish; one has to be in that stream and it is a matter of intuition what issues lead to use of this entitlement in public and others for which one would not touch it.  It is not a choice that is made at the moment of writing; this is what people simply do not very often understand; writing expresses the feelings of the soul, always, and when it is simply technical rhetoric it is not valuable at all, like doodles on the napkin after a good lunch with fish and white wine on a San Francisco afternoon, it is not serious.  But entitlement of a world scale is not something that is a special tool in a toolbox; it is natural and it has deep currents in one's soul that expresses itself once in a while.  It is totally inappropriate to invoke this entitlement except when the need arises naturally.

\section{Use of Entitlement}

WHO GAVE BILL GATES GOVT POWER AT ALL?
Inbox

zulfikar.ahmed@gmail.com 2:50 PM (1 hour ago) April 26 2021


Dear World,

These miserable useless worthless people ought to be put out of their misery one and all.  Who the fuck gave Bill Gates any US Government Power?  You stupid fucking moronic idiots without a bird-brain: SEEK AND DESTROY BILL GATES IMMEDIATELY YOU COCKSUCKING MISERABLE SHITS!  Who the fuck gave Bill Gates government power?  Are you fucking insane?  He's a malevolent murderous evil fuck you morons!  Take away his Government Power, seek and destroy him physically.  Why does Zulf have to do everything around here?

Thank you,
ZULFIKAR MOINUDDIN AHMED

\section{Support from Chicago}

By 4:29 pm Apr 25 2021 Chicago tells me in meta their full support of seek and destroy for Bill Gates.  I am wondering about how in an Eternal Recurrence, that I should be faced with a true butcher like Bill Gates who is much more oriented towards very gory cutting of flesh and eyes and damaging exoskeleton and slicing up muscles and cutting nerves than any movie butcher from Nazis.  Seek and Destroy for Bill Gates is mandated, and is almost universal in its moral force.  That Bill Gates must be considered a target of seek and destroy by every legitimate judiciary and government in the world is now quite clear.  
\end{document}