\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}\title{No Choice But To Ensure that Bill Gates Is Erased From Life and Existence}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates Harmed Me Deeply}

I don't know this man, Bill Gates from a can of tomato soup.  And yet, he harmed me more than my greatest enemy.  And of course when one is harmed in one's short life, one has to ask whether it makes any sense.  I am a Princeton graduate with enormous contributions for my people the Human Race.  This low life worthless cunt harmed me.  Of course I will ensure his extinction and erase his stain from existence.  Nothing else is even remotely possible.  I have never actually encountered a more horrid, ugly, malignant, evil, malevolent, rotten, worthless, scum bag in my entire life.  He must die and all his entire life's work must be purged from this Earth.  He represents a grave threat to my beloved people, the Human Race.  And he harmed things that were worth far more than he can even comprehend with his illiterate glib, stupid, dull, idiotic, inferior mind.  These sorts of people ought to have been aborted before they are born to poison the Earth with their evil, their abomination, their horror, and I am quite surprised that the American people and American government permit these wretches, these parasitic things to continue to cause trouble for the good people of Earth.  Now I am not the sort of person who moans and sighs and considers himself to have a tragic life when confronted with evil of this proportion.  No Nazi and no one else has been nearly as evil.  He deserves to be annihilated and fate puts me, Zulfikar Moinuddin Ahmed, in this rather delicate position of responsibility.  Who will do this?  Who is responsible enough to understand that annihilation of Bill Gates is the Salvation of the Human Race, that the hapless Human Race had never faced a more grim danger of dystopia than this malevolent and disgusting, this evil, this scourge upon us all.  Well time will clear this up.  I am not a violent man, but this murderous cunt Bill Gates cannot be allowed to live.  United States Government is incompetent.  I had asked the US Government repeatedly to bomb him back to Kingdom Come and they simply cannot do anything right.  These are not responsibilities I was prepared for.  I don't understand why no one else does anything right around here?  Why do I have to do everything.  You can't wipe out an evil murderous malevolent son of a bitch?  Are you joking?

\section{I Do Not Recognize Bill Gates As A Legitimate Businessman}

I only knew the man from his false deceptive self-promotion documentaries and interviews.  I knew he had some money, and I offered a good investment in my Medium Frequency Strategy with D. E. Shaw \& Co.  He put in \$2 billion and instead of paying me compensation used US War meta to damage my Body, rotted my teeth, and did all manner of Evil deeds, and disrupted my professional compensation in Finance from D. E. Shaw \& Co.  He is lawless, is incompetent in Finance, unprofessional, has the manners of a Barbarian from the jungle and does not respect professional work.  He denigrated my work while his entire ouvre of work from 1955-2021 is not even worth my pinky finger.  He is insolent, illiterate, has ugly racial convictions that are irrational, is totally barbaric, illegally uses US Military meta, and has Evil Plans for White Supremacist Secret control.  He harmed my Personal meta violating my Natural Rights.  I am extremely unimpressed that these did not lead to a Death Sentence by the United States Government which is thoroughly incompetent and might need to be dissolved completely for this outrageous incompetence at securing my Natural Rights.  



\end{document}


