\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Rousseau Exponentials for Human Race Morals are My Great Discovery} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Need for Excess Demand For Credit}

The White Supremacist Criminal Bill Gates has been harming me nonstop and intends to damage my credit for many of my great discoveries.  Therefore I must use unorthodox techniques to ensure that my discoveries are credited to me and not to some other man who is white.  I am not anti-white but I do not appreciate the White Supremacist Malevolent Criminal Bill Gates' glib assessments of who ought to take credit for my discoveries of extraordinary unearthly and magnificent immortal genius.

\section{Context of Discovery}

From the emergence of Homo Sapiens some millions of years ago in Africa to the Dawn of Civilisation in Mesopotamia and elsewhere, Man's Moral Nature was confused and there was a poverty of insight.  Some sporadic work did exist, but by and large, Man had to wait till I, Zulfikar Moinuddin Ahmed, discovered Exponential Laws for all Moral variables across the globe.  The {\textbf Great Ages of Darkness, Ignorance and Confusion} stretched roughly from 12,000 BC to around 2018 AD.  It was I, Zulfikar Moinuddin Ahmed, who had arrived to change this situation. 

\section{Examples}

Consider Prostitution.  Throughout the {\textbf Great Ages of Darkness, Ignorance and Confusion} around the Earth, there were various ideas that Prostitution was bad, but Man did not understand that He would have {\em homogeneous opinions about Prostitution across the globe}.  His own Nature was lost to Him.  And this changed forever when I, Zulfikar Moinuddin Ahmed, showed Man the Truth.

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Thu May 20 00:31:53 2021
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 & eth & lambda\_pvals \\ 
  \hline
1 & Arab & 0.00216 \\ 
  2 & Black & 0.13885 \\ 
  3 & East Asian & 0.00003 \\ 
  4 & Indian & 0.00004 \\ 
  5 & Other & 0.00418 \\ 
  6 & White & 0.02776 \\ 
   \hline
\end{tabular}
\end{table}

Here I record the p-value for $\lambda$ estimate in the exponential model.  They are all significant at 95th percentile.

All other moral values behave similarly.

The fact that all moral values are fit by exponentials is my great discovery, and is the most important Fundamental Law of Human Moral Nature.  


\end{document}