\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Fate In the Actual Universe} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Eternal Recurrence is True}

All things that will occur on Earth, and all things that have occurred in the past of the universe, have occurred infinitely often in the past, and will occur infinitely often in the vast future.   In particular all events of the future of my life are recorded in the stars.  

This is true, but the governing force of Fate is only my Four-Sphere Electromagnetic law, and this is what makes things quite intriguing.

I am seeking now two Ph.D.s and tenure at a top tier school: Princeton, Harvard, Yale, Stanford, Berkeley.  I do not know if the various illustrious people I am asking will even respond let alone give me two Ph.D.s (For Four-Sphere Theory, Finance, Quantitative Human Nature, Moral Models etc.) and a tenure.

It is interesting to try to understand what inferences I could draw regarding the future events of my life.  The answer is simply I do not know.  And this is one of the fundamental difficulties about understanding.

Although I know with certainty that the future events of my life are recorded in the stars or encoded in the cosmos in other ways, I cannot know what they are.

What inferences can I make?  Well I definitely deserve a couple of Ph.D.s and a tenure at a top university because I have proven myself as a great scientific mind.  Then there is the question of optimism versus pessimism.  I would rather be optimistic generally, but I cannot know with certainty so I do not worry too much more about it.



\end{document}