\documentclass{amsart} 
\usepackage{amsmath}
\usepackage{verse}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{The Final Laws of Good and Evil in Human Nature}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

The final laws of Good and Evil for Human Nature is that every value that has a scale between Good and Evil has an Exponential distribution, weighted on the Good End.  

Human Nature is Exponential on the Good end with an Exponential Law.

\section{Evidence}
See previous notes for exponential fits for Justification for Violence, Suicide, etc. as well as the number of lies per day.

\section{Significance}
Empirical Virtue Ethics is correct, and it does not really matter what the reasoning is.  In actuality, the values of the entire human race has uniformity in the exponential law with small noise level with $R^2=0.7-09$ range for exponential distributions.  The origins of evil is that the exponential distribution had some people with values that are far from Good.  So the tail end of this distribution is solves the problem of origin of Evil.  

\section{Zulf's Law of Good and Evil is the Final Law for Good and Evil}

The fits are good, and the answer is clear and universal and based on extremely high quality data.  No sage or philosopher from Ancient, Enlightenment or Modern times from East or West has ever produced a clearer answer to this problem.  This answer is right and simple, so it is the final answer.

\end{document}