\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Much of Twentieth Century American Politics Depended on Unclear Understanding of American Government's Fundamental Purpose}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{What is the Fundamental Purpose of American Government}

The fundamental purpose of American Government is not a secret.  It is written directly in the first few paragraphs of the Declaration of Independence of United States.

The fundamental purpose of American government follows from the American Founder's elucidation of Fundamental Purpose of all governments.  

\begin{itemize}
\item All men are created equal with Natural Rights that are inalienable endowed by "the Creator" (i.e. Nature)
\item The securing of Natural Rights of all Americans is the Fundamental Purpose of American Government
\end{itemize}

\section{Inferences}

American Government is not an ordinary Democracy.  It is fundamentally defined as an organisation whose fundamental task is securing of Natural Rights.  Democracy and Republic structure are {\em secondary} for American Government.

The American Government exists primarily to secure Natural Rights -- among them Life, Liberty, and Pursuit of Happiness, of Americans.  

We are Americans to the extent we embrace the Universal Character of Natural Rights being inalienable for all people everywhere, and our government exists to secure these rights for, now, 320 million Americans.

\section{Explanation of Racial Strife and Corruption of American Government}

Throughout nineteenth and twentieth centuries, there has been continuous confusion in Washington and in public opinion about the fundamental purpose of American Government. 

\section{Not a Matter of Devious Interpretations}

The interpretation I offer of the purpose of American Government is clear and straightforward, and supported by decisions including our leadership in UN Universal Human Rights Declaration of 1948. In particular all manner of {\em devious interpretation} of 'all men' being restricted by ethnicity and other characteristics are completely and utterly wrong.  'All men' are all male human beings on Earth, and indeed we include all women as well.

\section{Conclusion}

No deviation is possible or tenable for the Fundamental Purpose of American Government.  The primary duty of American Government is to secure Natural Rights of all Americans, rich or poor, black or white, sick or healthy, and nothing less and nothing more.

All other functions of American government are secondary to this fundamental purpose for American Government.  American Government can be considered totally corrupt if any other priority supercedes the securing of Natural Rights of all Americans.  

We are in fact bound by many treaties and agreements to in addition secure Natural Rights of all people everywhere on Earth.

\section{Sacred Soul of America is Universal Natural Rights}

The Sacred Soul of America is our conviction that all men (and women) are endowed by the Creator certain inalienable Natural Rights including Life, Liberty and Pursuit of Happiness. 

\end{document}
