\documentclass{amsart} 
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Plan for the Future of Human Well-Being}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}

\begin{document}
\maketitle

\section{1000-node clusters with Mesos for processing Human Services}

A 1000-node Linux cluster can service algorithmic and computing needs for 7.8 billion people.  The backend is MongoDB and frontend Meteor.

This is the key point, that the technology that is appropriate to serve 7.8 billion humans simultaneously can be packaged, and a 1000-node Linux cluster running Mesos can do it.  

\section{Preparing for Future Needs of Human Race}

In the future, the clear needs that will persist are Social/Respect and Autonomy/Mastery.  These psychological needs do require effort.  We believe that strong Social Science and research breakthroughs in reducing combinatorial complexity to polynomial complexity in handling the variety of human personalities and uniqueness details will allow us to establish a canonical architecture to serve 7.8 billion people's needs simultaneously.  

\section{Uniqueness is the key to the Future}

As population grows, Man finds it more difficult to distinguish himself from the mass of people without assistance, and social life of Man becomes so complicated as to require significant assistance from technology.  It is not primarily the engineering that is important, but deeper quantitative understanding of Human Psychology and Personality Psychology.  This direction will produce the giant successes of tomorrow because managing a meaningful life becomes overwhelming work for Man without extraordinary and nontrivial assistance from technology applications of quant Social Science.

\section{Personalised Religions}
Religions all arose in sparser population and slower times.  They combined social with personal spiritual needs.  They begin to lose their effectiveness as the population explodes and individuals need to have spiritual instructions tailored to their personality.

\section{Summary}
The era of deeper understanding of human well-being and its precise management has just begun.  The future challenges here are tremendous.  Algorithmic assistance that is adapted to the exact individual has mathematical difficulties that will require nontrivial effort as the set of measurements per person grows.  Partly this problem is resolved by a solid uniform Human Nature model for all people.  

\end{document}



\end{document}