\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Bill Gates Had Expelled me out of Gaga Car and put horrible Razor Blades to Hurt my Eyes}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Gaga Car}

Gaga is my word for my paternal grandmother and her Car was my meta inheritance.  Bill Gates had expelled me from it destructively and set up Razor blades to cut my eye if I came near it in meta.

Now let us rewind what had gone on between myself and Bill Gates.  I actually don't know Bill Gates personally.  I had worked on Finance in Allen Texas, living on disability and I had success with Medium Frequency.  I sent it out to many people, and people did not respond but D. E. Shaw \& Co. liked it and started trading it.  Bill Gates did some considers for technology with me, and I arranged \$4 bn of his money in my strategy.  He did not want to pay at all, and I told him to go to hell and gave \$4 bn to India.  Then he put in \$2 bn into my Strategy and began harming my eyes and trying to murder me without paying my cut of \$120 mn.  I was angry because the fuck prances around in Xanadu Mansions and yatchts and lives of my great work; he repeatedly denigrated my work calling it 'trivia' without paying.  

He did many other horrible things too, including what is mentioned above.  

The total package of malevolence done to me was so high, that I knew he was a literal Evil Demon and not a Human Being at all.  I do not mean this as a pejorative.  I mean that he does have Human DNA but he is not a Human Soul at all.  He is a non-human Demon Soul and that is why his malevolence level is not a bad personality trait but an {\em impossible one}.  He is much more malevolent than any white man alive, so I dismiss his 'white man' routine.  White humans are not particularly more or less malevolent than any non-white man.  He also has deceived the entire Human Race for more than four decades with pretense at benevolence.  His is by far the most malevolent cunt who had ever existed in the evolutionary history of Homo Sapiens.  And that is because he is not Human at all but Demon. 

\section{Do You Think Any Human is Capable of Repaying Money Making With This Malevolence?}

It is not possible for a Human Being to react to someone American doing something that makes them money with this extreme level of malevolence.  All Governments of Earth ought to Seek and Destroy him.

\end{document}