\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{What Produced My Animosity Towards Bill Gates} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Prehistory}

My exact times will be off without careful examination of my email dates and such.  I will give a rough sketch.  About a year ago, I had already worked for some years on Medium Frequency Alpha Strategies, and also Personality Psychology.  I had discovered thousands of Personality Types in data extending Briggs-Myers types but using Big Five.  I was excited about this discovery because I was interested in the problem of Soul Mates.  Also Uniqueness of products and services.  

I was looking for \$80 million to expand my registered company.  I never dealt with Bill Gates directly and did some meta considers with him from here in Allen Texas. 

I was doing considers with him for creating good relationships because I had no idea he was an evil malevolent criminal cunt.  I believed the PR.  

Well I arranged for him to make quite a bit of money as it turned out D. E. Shaw \& Co. were trading my strategy and it looked good 10-12\% with 1-2\% volatility.  I thought I'll get a lump sum of \$80 million and relocate to San Francisco.  Well it turned out that Bill Gates was a total cunt and just wanted to make money on my work and instead of paying cut up my eyes and murder me.  

D. E. Shaw \& Co. is trading my strategy and now they owe me \$120 million because India put in \$4 bn and Bill Gates \$2 bn.  

Bill Gates cut into my eyes and started all sorts of horrible destruction claiming 'White Right'.  He used US War meta to total my body meta, and he used US Industrial meta to harm my exoskeleton and harmed my interior, blood meta, Romantic, Family, Ancestral and was just evil beyond belief.  I emailed a lot of people but US Government did not intervene at all to secure my Natural Rights.  

And this continues.  Bill Gates believes that he can just harm anyone without repercussions because he's white and this is a White Supremacist country.

Anyway, I am threatening the US Senate that I will firing squad all 100 Senators if they do not kill Bill Gates, preferably by relentless bombing of Bill Gates till he is totally destroyed physically.

\end{document}
\end{document}