\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{May 27 2021:  Zulf Proposes Drawing the Boundaries of Political Conflict} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Ethnicity is Irrelevant}

My latest result is that Ethnicity effects for midpoint breakup for morals is around 6.5\%.  I am not particularly keen on arbitrary and irrational break-up of political conflict based on Ethnicity.

What I am thinking is a much more parsimonious and valuable breakup along a different lines.  I like the breakup of Good People of the world, and I want to name this group "Goodies" versus Bad People of the world, or "Baddies".

We can draw the lines of political conflict along "Goodies" versus "Baddies" and Bill Gates can be the Leader of the world's Baddies.  Let's do a quick and dirty estimate of the total number of Baddies in the world.  If you are a Baddie then just join Bill Gates' side.  I'm a Goodie.  I will take all the Goodies of the world.  

\section{Easy Test Of Goodie Versus Baddie}

Do you believe that you ought to have the right to harm people anywhere in the world at will?  Do you believe that you were fated to be the rulers of the world and others ought to be your slaves?  Do you believe that you ought to be able to take other people's things because you're big?

If you answer yes to these, just join Bill Gates' side.  I want people who believe in Goodness, Justice, Natural Rights and their protection for all people, etc. to join with me in the Goodies Camp.  I don't care about your ethnicity.  You can start with elementary exercises such as "Death to Bill Gates!!!" and so on.

\section{A Speech For Goodies}

My Beloved People the Human Race,

You are an Angelic Race.  Within your hearts are the Noble, Good, and Just sentiments.  You have clean Conscience, and Great Hearts.  You believe in security of Natural Rights of all People everywhere.  Your life on Earth is filled with purpose and meaning, and you will lead this world into the future.  You believe in tolerance and respect for others, and you are proud of the Goodness of your Hearts.  You recognise that it is not superficial things like Money and Possessions that make people who they are but their inner Character.  You are vast and fill this world, and you make Civilisation possible without strife.  Be proud of your nature, and be benevolent and kind to your brothers and sisters.

Thanks,
ZULFIKAR MOINUDDIN AHMED



\end{document}