\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Thoughts on What Makes You A Great Monarch or a Great Republic Leader} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Occasion}

I am just a much higher caliber Monarch or a Republic Leader than Bill Gates.  He has been cutting up my eyes and destroying my Ancestral Meta and doing other damage, and so I have the occasion to ponder what makes me such a better caliber Monarch or Republic Leader than Bill Gates.

\section{Heart and Conscience Not Power}

Power is just an instrument.  It's like a screwdriver, or gasoline.  Bill Gates happens to be totally Barbaric and always starving for power; it's pathetic how he is just uncouth in his rushing around for power like a starved dog.  Disgusting.  I have 3000 years of Aristocracy and I generally tend to avoid seeking any power.  But since I am thinking about the topic right now anyway, let me pontificate a bit.

Great Monarchs and Great Republic Leaders are not actually focused on Power.  They are great because they have Great Hearts and they have Great Conscience.  They have fine tuned Virtues, and they are much better than non-Aristocrats and quickly and accurately gauging right and wrong.  They have instinctive sense for the {\em well-being of their people} and they devote their lives to improving this well-being.  This is what makes them Great.  It's only shabby charlatans and plebians who strive for power and then believe that they are worthy {\em because} they have attained some power.  It's just disgusting to behold, and even Theodoric's awful execution of Semmechus is more graceful.  Bill Gates is the furthest creature that I can even imagine than a true King.  He was literally psychopathic.  No self-centered glib charlatan without empathy has even a remote chance of being a Great Monarch.  Bill Gates is psychopathic; he literally has no capability for any moral conscience.  This is like a man who lost his legs seeking to be the marathon running champion.
 
Bill Gates does not have any capacity whatsoever to be a Monarch of even a small group of kindergardeners, let alone of nations and the planet.  He should be executed for insolence for harming me.  I could be a Global Monarch; but I have no interest in it.  He has not even a remote chance.  It's an absurdity beyond imagination.  

\section{Quick History of Aristocracy and Relation To Mythology}

My Ancestry goes back to the Vedic period of India.  If you look at the Indian examples, you see that the great figures were Rama and then you have the gods.  Aristocracy developed with notions of Divinity.  In other parts of the world similar phenomena occurred.  Human beings needed a particular sort of talent, which is the source of Aristocracy.  In Europe, after the French Revolution, there was a collapse of understanding of Aristocracy.  Today we have 'Game of Thrones' in HBO special.  What is not understood is that Aristocracy is a talent, like Mathematical Genius or Musical Genius.  Some people have refined sense of well-being of vast numbers of people, and they manage to produce political environments where people flourish.  That is not a joke.  All the modern political theorising has not found the secrets to this situation.  So Aristocracy grew as particularly talented people impressed the people, and then it becomes hereditary and this is based on theory because progeny of great kings and queens do not necessarily perform as well.  There is some hereditary component to the {\em talent} of Aristocracy but the actual results are often dismal.  This is because power is dangerous and corrupting.  And so this is the story.  American Power is carefully non-Aristocratic, but once again, perfection in political systems simply does not exist.  

Bill Gates may have skills in Game of Thrones for bloodthirsty aggressive acquisitive power-seeking, but he has {\em absolutely no Aristocratic talent whatsoever}.  Most of the hobos in New York I have met would be better at well-being of others compared to Bill Gates.  He is a totally selfish malevolent psychopathic cunt.  Let me repeat this.  Bill Gates is a selfish malevolent psychopathic cunt.  He will not have an iota of Aristocratic talent in a thousand rebirths.
 

\end{document}