\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Zulf's Strategy For Proving that Bill Gates lies outside Human Range in his Violence}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

When we fit an exponential model for agreement with "Violence against other people are justified" we get such a beautiful fit for American data with $p<0.0002$ that we can take it as the true distribution.  We find $\lambda_{America} = 0.4537$.


\section{At What Point does Bill Gates exceed Human Bounds?}

This is a general question and we can approach the question rationally.

First, since we are dealing with the exponential distribution, the true range is $[0,\infty)$ and not $[0,10]$.  

Bill Gates falls somewhere $x_{BG} \in [0,\infty)$.  Let us try to understand at what point some $x>0$ goes {\em beyond Human Bounds}. 

For this recall that there are $N=200 \times 10^6$ white people in America.  

We see first that 
\[
e^{-\lambda_{America} 10} = 0.0107.
\]

These are people who answered "violence against others is always justified".  Now 1.07\% of American whites compose a good number of people.  So the general idea that violence against other people is always justified, while not palatable for quite a number (roughly 95\% have $x<5$) of white Americans is palatable for some 1.07\%.

Now Bill Gates, I know this personally, believes that he ought to have the right and power to kill any nonwhite in America {\em at will}.  This implies that he is in the $x\ge 10$ group of 1.07\% white Americans.  But it is much more severe.  His $x_{BG}$ ought to be much higher than $x=10$. 

The question is whether it is high enough to exceed human bounds.

\section{Criterion for Exceeding Human Bounds}

A simple criterion for exceeding human bounds is when
\[
e^{-\lambda_{America} x_e} N < 1.0
\]
In other words, when the fraction of the population that is higher than $x_e$ is such that there are no whole number of people left in America then $x_e$ is beyond human bounds.

The cutoff value can be estimated as
\[
x_e = 42.15
\]
This is the cutoff point such that
\[
N e^{-\lambda_{America}x_e} < 1.0
\]
with $N=200,000,000$.  

\section{Exact Criterion for Bill Gates exceeding Human Bounds}

Bill Gates can be said to have {\em exceeded human bounds} if we are able to establish that $x_{BG} > 42.15$.  Since at this point, he is more rare in his agreement of violence against others that exceeds the rarity of 1 in 200 million.

\section{Bill Gates is a Demon If $x_{BG}>42.15$}

The moment his propensity towards violence satisfies $x_{BG} > 42.15$ we can safely conclude he is not a Human Soul but a Demon regardless of his Human DNA!

\end{document}