\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf Speculates About Universal Message Reception in Human Race} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Universal Human Moral Nature Exists}

Ethnicity effects on Human Moral Values is between 6.5\% to 9.5\% I have established already on strong data from World Values Survey.  We can conclude that Universal Human Moral Nature exists.  This is a great conclusion and a fundamental advance for the human race and will forever change the future trajectory of the human race.

That is a solid milestone in our knowledge about Human Nature.  Now I am interested in building on this solid foundation to further understanding.  Now I am interested in understanding whether there is a Universal Human Message Judgment that is possible to quantify, i.e. I am seeking a {\em parsimonious scientific theory} that will tell us the conditions under which a given message $M$ will be accepted and taken seriously by almost all people on Earth.  

A priori, this is an impossibly difficult problem but I am optimistic that
\begin{itemize}
\item{There is an objective solution to the problem}
\item{Certain messages will have a high likelihood of being accepted by the entire human race}
\end{itemize}

These are extremely nontrivial problems in general but we want to consider the problem since it is interesting to us.

\section{Main Speculative Hypothesis}

The acceptability of a given message to almost all human beings on Earth is primarily dependent on the judgment of virtuous moral character of the sender, as judged by the receiver.  I want to keep my speculative hypothesis focused and simple.  

\section{Marketing Theories Are Inadequate}

I really don't like Marketing theories of communication.  Their version will be 'what message $M$ will lead people to buy my product'.  I don't like the problem because I don't really care.  Furthermore, I don't understand how this problem can be solved without solving the more general problem I have outlined, i.e., what messages are acceptable {\em at all} at the human race scale.

\section{The Problem Needs to Mature}

This is a great and highly nontrivial problem, and so I will let the problem mature.


 


\end{document}