\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Natural Rights of Man is More Successful than Christianity and Islam}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Success of Natural Rights of Man}

There are around 2 billion Christians and 1.5 billion Muslims in 7.8 billion; about 45 percent of human race.  The estimated popularity of Natural Rights of Man, by agreement of "human rights are important to protect" is 78 percent of the world.  

"Eight in ten people surveyed stress the importance of having laws that protect human rights in their country and more than half say they make their life better."\cite{HR}

\section{Natural Rights of Man did not Exist as a concept before John Locke and Thomas Jefferson}

In the entire history of the world, including the history of Europe, with all the vast amounts of thought, no one had ever conceived of anything so strange as "Natural Rights" of human beings attached to them from birth before John Locke, although he was not as clear about universality as Thomas Jefferson.  No one, before these people had even conceived of such an odd idea.  It simply did not exist.  It did not exist in Plato and Aristotle; it did not exist in Confucius, not Ancient Mesopotamia, Egypt, in India, Greece, China.  {\em Before Locke and Jefferson} it did not exist in anyone's dreams. They thought up the whole thing.  It was so marvelous, so spectacular, so true in the end, so beautiful, good and right, that the hearts of all of humanity were touched and now 78 percent of human beings consider it their own conviction, matter of their own ideas of what is right and what is wrong.  Such a spectacular religious coup this planet has never witnessed.  It is one of the most marvelous successes in all of human history.  Absolutely gorgeous, the mind of some geniuses, confused as they might have been were able to polish a heavenly thought, and that thought took the world by storm.  The convictions about Natural Rights runs very deep.  Even I was envious once of their success.  But I am wise and give admiration without reservation where it is due.  Congratulations on your immortality John Locke and Thomas Jefferson, for you deserve it.



\begin{thebibliography}{CCC}
\bibitem{HR}{\url{https://www.ipsos.com/en/human-rights-2018}}
\end{thebibliography}
\end{document}
