\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf Promotes Human Race Pride and Reports the Obnoxious National Pride Life Satisfaction Premium} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{The Obnoxiously Positive Effect of National Pride in Life Satisfaction}

I do love America, don't get me wrong.  I love America, my adopted home.  At the same time, I also have a vast view for my Beloved People the Human Race and promote something greater than National Pride.  But since I am an honest man, I will give the actual results of National Pride.

We let $S$ denote life satisfaction and $H$ happiness, and $P$ national pride and $NP$ no national pride.

\begin{align*}
P(S|P) &= 0.34\\
P(S|NP) &= 0.20\\
P(H|P) &= 0.734\\
P(H|NP) &= 0.8832
\end{align*}

National Pride does decrease happiness, which I will not talk about too much but it has the obnoxious capability of increasing life satisfaction.  This is true, but I don't like this.  I believe that Human Race Pride will have an even higher effect on Life Satisfaction.  These little nations are too small, too primitive for me to tolerate.  They are far too small for me, and I don't like this increase in life satisfaction due to National Pride one bit.

\section{Notes on my Development of Human Race Pride}

When I was young, I did not care about nationalism.  Bangladesh, East Bengal was not even a country some years before my birth.  And there was a great deal of ra ra of nationalist type that did not appeal to me.  At thirteen I was already an immigrant to America, living in New York, and I was too internal to consider National Pride so important.  We were in a neighborhood with some unruly kids, and I did not like Fourth of July celebrations which seemed to me to be occasions where I could be accosted by boys from the neighborhood for being Indian immigrants.  This was near the Aqueduct racetrack in Queens.

Over the years, my totally un-nationalistic attitude changed, I grew closer to the foundations of America, and years of reading Emerson had left its mark too.  And finally I had my spiritual revelations and realised my short life on Earth shall have deeper meaning, and I embraced Human Race as my people.  And it was just absolutely glorious, for this belonging, to the Human Race, had depth, and my We could embrace Mesopotamia, Egypt, Greece, China, India, and all of Civilisation, a greater we than can even occur in the Superbowl.  And this makes sense to me, that all Old World and all New World would merge within me as my history.  After that epiphany, Nationalism is not even an option for me.  I have seen the light.

\end{document}
