\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Human Race Functionals and Human Nature}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{The Great Discovery}

Early in late March and early April 2021, I discovered a remarkable set of regularities for the entire human race.  The principle is that Ole Barndorff-Nielsen's Generalized Hyperbolic Distributions (GHD) have the ability to describe distributions of quite non-trivial distributions percentages of people across the world that have answered similarly in World Values Survey.  

This is an extremely surprising discovery, because there is no reason to believe that these measurements have any simple mathematical parametric form at all.  And yet, they are quite often extremely well-fit by these five-parameter univariate probability distributions called GHD.

\section{Single Human Nature}

Human Nature has been previously thought about without quantitative tools of the sophistication of GHD.  I will not go into the technical issues of GHD except to say that they are infinitely divisible distributions, but they are not Gaussian.  They have five parameters $(\mu,\sigma, \lambda,\bar{\alpha},\gamma)$.  Now the complexity of Human Race is tremendous obviously with 7.8 billion people geographically spread around the globe with enormous variety in culture, language, ethnicity, nationality, and other demographics.

We introduce the human race mathematically as $\mathcal{H}$ with $|\mathcal{H}| \sim 10^{10}$ and we consider the percentage agreement to World Values survey as maps from $\mathcal{H}$ to $\mathbf{R}$.  We are fitting the probability density of these distributions.  It is already a serendipitous discovery that they can be fit by any smooth density at all, let alone by a 5-parameter analytical GHD.  This is an empirical discovery of great serendipity and fortune because some of the fits are truly remarkably tight.

The existence of many functionals $F:\mathcal{H}\rightarrow\mathbf{R}$ with the property that the probability distribution is GHD on $\mathbf{R}$ is one of the deepest sources of our study of Human Nature.  

\section{Global Political Context}

The existence or not of Human Nature has been, both in the political arena and in social sciences and humanities a matter of extreme controversy now for several centuries in West and East.  We can establish some features of Human Nature quantitatively from our discoveries that many functionals have GHD whose smooth simple structure would be quit impossible to justify if there were not a strong nontrivial Human Nature.

These are difficult questions that go against many accepted intuitions of the current age.  The discovery of a Single Human Race is as solid as any part of science but has yet to produce a reduction of racial strife in parts of the world.

\section{A Vision For The Future}

Human Nature at some point has to form the foundation of Social Science.  The Human Race is not infinitely malleable and one hope is that a relatively small set of variables will give us an accurate fundamental model for human beings that is accurate in modeling all individuals.  The total variation of Human Race we believe is tractable in the future although quite an open challenge.

\section{Example of Large Scale Problems}

It was I who had observed that failure of Classical Liberalism of Adam Smith and John Locke is responsible for large scale marriage failures and fatherlessness and loneliness in America.  This is due to a failure of a correct Human Nature model held by Adam Smith and John Locke who had correctly grasped need for Autonomy and Money but not Social/Respect needs.




\end{document}