\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{The Weaker Attack on Bill Gates: Make Him Seem a Hypocrite and Fool}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\section{Introduction}

"It's not that people have a well of goodness that moral exhortations can tap.  It's that information can be framed in a way that makes exploiters look like hypocrites and fools.  One of our baser instincts--claiming authority on a pretext of beneficence and competence--can be cunningly turned on the others."

(Stephen Pinker, {\em How the Mind Works} 2007, p. 518)

That Bill Gates is a hypocrite and fool is not in doubt.  These are far too lukewarm to describe his character.  He is a malevolent deceiver completely consumed with avarice in a way that is much more intense than any normal human being can imagine.  And that he is a fool is also too mild.  He has {\em convictions} about things for which simple inference and education will quickly lead to contrary answers.  Steven Pinker, fortunately, is talking about much more general phenomena, the method to lead to addressing far more benevolent and reasonable people than Bill Gates.  

I want to return to one of my own ideas about {\em public speech}.  It is that in public speech, the only content that is actually transmitted is are in values contained within and not the details.  I have been thinking about this quite a bit in the past months.  We use language to communicate but I am quite lazy and don't remember details of what I had read.  Sometimes I do, but this only happens when something truly interests me and then I am much more alert to details.  Daniel Kahneman's theory of level 1 and 2 thought processes apply.  Usually I read quickly and don't worry too much about remembering details.  When something that I had thought about before many times seeking some subtle exact answers, I am alert and use careful reading.  I don't like expending that much energy on much reading.  Whether it is a good habit or a bad habit I don't know, but I do know that I am comfortable with doing things this way because I hate wasting energy on things that are probably not going to be all that important.  I have literally close to a thousand books and I hate spending time reading things that will take my time away from doing something more important.  That is my excuse for lazy and disorganized reading.  I am intuitive about what is important.  A few topics have been with me through life, and I pay attention when my glorious convictions are touched.  I am remarkably accepting when they are not.  Now I don't believe that my ways are unique here, but I don't know for a fact.  I have this deep feeling that as time passes I am meant to be more selective and I am less anxious about conscientiousness as I used to be as a young man with good studious habits.  Partly it is the effect of living with a disrespectful cantankerous shrew -- at least some of the time who does not respect my efforts at all since I can't get D. E. Shaw to pay me my \$120 million over Bill Gates' blockade, so I have to adapt to adversity every day.  And partly it is because I feel anxious to make pioneering progress on something and do not see it in something I am reading.  I mean I am reading, but with a clear sense that I am not going to try to remember.  And that is when I am most aware that it is the values that are absorbed or interpreted most easily.  And my values are, even though as not articulate systematically quite sophisticated and tempered in lived experience with a lot of adversity and variety and growth.  So I can feel whether there is substance there.

Now with Bill Gates, I happen to know extremely well that almost all his public statements, interviews,  documentaries are strongly deliberately deceptive.  This is quite the wonder because I had no idea.  He is obsessed with controlling all things and everything and is continuously lying, continuously lying, and calls any fact or principle he does not like PR, and anything he did not do "trivia".  I have never encountered a more abominable, criminal, malevolent worthless personality in my life.




\end{document}