\documentclass{amsart} 
\usepackage{amsmath}
\usepackage{verse}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Histories of Zulf}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

I am a blend of many strains of history.

\begin{itemize}
\item Angel of Heaven for billions of years
\item Bengali-Persian Noble line for around 3000 years
\item Western American Man with Western Values and Western Cultivation
\item Professional in Finance, Science, and Technology in America
\item American Universal Idealist
\item Scientific Revolutionary who overthrew Schroedinger and Einstein and Gravity
\end{itemize}

Most people would find it easier to understand the later histories, and not Angel of Heaven for some billions of years.  But identity is always a strange and subtle mixture of elements.  As Angel I chose to be born to my parents.  From them I inherited 3000 years of Aristocratic history in Vedic Civilisation.  Early history had Hindu Noble blood, and probably converted to Islam 11th-14th century.  

Bill Gates and Noia Efrat destroyed my Ancestral meta with destructive criminal intent, and the mastermind was Bill Gates.  I am Angel even without Asian Noble meta infrastructure.  That is fine as well, and I will ask China or others to repair my Asian Noble infrastructure in the future after Bill Gates is put to death.  

\end{document}
