\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Estimate Self Celebrity Level Past Michael Jackson}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{My Actual Celebrity Level is Past Michael Jackson}

Bill Gates has used some artificial power tricks to suppress my renown, but in my own internal computations, I have surpassed the celebrity level of Michael Jackson already.  I am owed \$120 million from D. E. Shaw right now that Bill Gates is blockading and so on.  So I do not actually worry too much about what people think and pursue my life with the implicit faith that I am past Michael Jackson in global renown already.

\section{Human Race Message May 15 2021}
My Beloved People the Human Race,

You might have heard of the magnificent genius of the German philosopher Friedrich Nietzsche.  His great genius is without question, and I am a student of many of his works.  I will tell you today about one of his greatest errors.  Nietzsche believed that human beings are far more malleable than we are in actuality.  He believed that values are created and invented rather than discovered.  And having decided to believe this, he set about considering creation and invention of values of his own.  This exercise is wonderful if you are an intellectually gifted individual, as he was.  But he was misguided in many ways about the genealogy of morals.  You see I am the great genius who discovered that the actual values of Human Race across the globe have deep invariance.  It is impossible to have this regularity across ethnicities if Nietzsche were actually correct.  Human Moral Values are far more likely to have developed from six million years of natural evolution, rather than being the effect of following the commands of some individuals and aristocrats like a herd of reindeers following their invented values for control.  This flaw of Nietzsche's is a deep error of understanding Human Nature. He thought that things only changed for masses of people because Aristocrats conspired these changes.  This was a great flaw of his thinking.  Neither Aristocrats nor Commoners or anyone else has the actual power to go against the tides of Nature, of Human Nature, for the power of the Natural force is Existential, and it would be like the hubris of people to Dam the currents under Pacific Ocean.  The prevailing values are not inventions of any religion, of any Prophet or Holy Man but the outcome of Natural Evolution, maybe touched and articulated by Aristocrats here and there.  "Herd" is partly just the social nature of the Human Race.  Be creative and independent in formulating your values, but also understand that Human Nature is strong and powerful within you as well.  Do not accept denigration from those who call you 'sheep' and 'herd animal' for what is pleasing to your heart.

Thank you,
ZULFIKAR MOINUDDIN AHMED

\end{document}