\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Justice Department Higher Ups are Cronies for Bill Gates who allow him to violate American Natural Rights}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

I have been dealing with Bill Gates for six months now.  A more horrific cunt this planet has never seen, and he is totally murderous, criminal, and ought to be put to death. 

Justice Department Higher Ups, whose primary duty is to secure my Natural Rights, have instead collaborated with Bill Gates, including agreeing to hold off a Seek and Destroy on the horrific criminal Bill Gates who has violated my American Natural Rights horribly.  

There is very little question that Justice Department Higher Ups are extremely corrupt and would rather collaborate with murderous criminals and pretend to be 'pragmatic' than do their primary duty, which is secure Natural Rights of Americans like myself.  

They ought to be sacked immediately because they do not represent the interests of the American people, and they do not stand on the principles that have allowed this Nation to thrive.  They don't belong in Justice Department at all; rather they should go into shady business with all the criminals on the planet. 

We cannot allow Justice Department of the United States of America be corrupted by people who are more interested in people with power than securing Natural Rights of Americans.  The latter is not a secondary matter but the heart and soul of the American Classical Liberal Democratic Republic. 

In the future, people in authority in Justice Department ought to be sacked immediately rather than us having to deal with a corrupt Justice Department.  United States does not have many redundant institutions and cannot afford to have key Federal Institutions to be manned by people whose interests are not those of United States of America.


\section{Direct Message to Justice Department Higher Ups}

You stupid cunts!  You pick any American from Michigan, Wichita, Dakotas, Carolinas, New York, California, anywhere at random, and you tell them that when Bill Gates violates their Natural Rights you will be "pragmatic" and let him do it and consider him a National Treasure instead of your job of securing their Natural Rights and watch what happens.   They will burn down your houses and kill off your bloodline you stupid incompetent shits because in America no one pays taxes so that Justice Department is crony to Bill Gates and "pragmatic" about not doing their primary job.  You want to fuck with Zulf?  Huh?  I'll get millions of people going to burn down each and every one of your houses and killing all your children?  You want to fuck with Zulf?  You want to be pragmatic?  I'll show you pragmatic you little pathetic low corrupt little shits.  You want a future, better secure my Natural Rights.  They will burn down all your houses.  You want to suck dick to people with money, do in another country stupid cunts!

\end{document}
