\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{How Much Money is a Lot of Money?}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{\$23 trillion is not a lot of money}

When you ask people how much is a lot of money?  They give you personal answers.  I saw a survey recently on some web magazine.  It asked people whether they feel wealthy or not, and what is the level at which they feel wealthy.  I don't remember the exact numbers, but something like \$1-2 million in the bank seems to make people feel that they are wealthy.

For me, the perspective is quite different.  For me, \$23 trillion is not a lot of money.  This will rub some people as quite strange and outlandish.  So let me explain this.  I don't actually worry too much about my personal wealth.  Maybe I should have; I am right now living with my aunt on disability, so I am clearly not successful.  Well actually I am phenomenally successful, just not in money.  I am owed \$120 million from D. E. Shaw that Bill Gates is blockading with all sorts of racial plans to deny nonwhite people money they have earned.  Well, c'est la vie, I will end up dealing with the little shit the way he ought to be dealt, which is totally wiping out and all his memory from Earth.  But going back to the issue of why I think \$23 trillion is not a lot of money you have to have perspective. 

Around \$23 trillion is the per annum GDP of America.  If this were a lot of money, America would be perfect, but it's not.  There are a ton of problems in America, such as 61\% loneliness.  

\section{Finance Scale}

Finance has various perspectives. My perspective is that Finance is part of human civilisation and therefore exists to serve the human race, my Beloved People.  People have skewed perspective when they read Ayn Rand, whose ideas are very bad, and consider glorification of various industrial magnates and so on.  For me these are small players too.  The right perspective is {\em global} and the {\em global economy} and the whole thing exists to {\em serve my people the Human Race}. 

\section{Zulf's Definition of Right Amount of Money}

The Amount of Money needed to produce a harmonious healthy peaceful world with happy people living productive lives across the globe is the {\em Right Amount of Money}.  It's a lot more than \$100 trillion.  Who takes a little puny amount of money and feels big in front of grocery store owners is not exactly going to be the sort of thing Zulf will be interested in.
 

\end{document}