\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{ZULF'S MESSAGE TO MY BELOVED PEOPLE THE HUMAN RACE MAY 14 2021}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Body of Message}

My Beloved People the Human Race,

I have learned some things that I wish to share with you.  First of all, there is plenty to do after you are dead.  But you should pay attention to your life here and now as well.  Always be honest with yourself and with all people.  Dishonesty is a certain lack of regard and respect for your own life, and you should always avoid disrespecting your own life because life is precious.  It is also miraculous and more beautiful than your mind will be able to comprehend.  You are an Angelic Race, so never be ashamed of your goodness.  Never envy anyone else if you can avoid it.  You will find your uniqueness shine bright.  You are not forgotten by the Angels or by the beings across the universe, so do not feel that you are alone.  You will find many who will understand you and be sure to reciprocate.  It is dishonourable to take for granted love and efforts of others for your interests.  Trust people as much as possible but do respond when the trust was undeserved.  Be optimistic about the future.   Do not live for others; live for yourself but never be malevolent in self-interest.  It is when you are respectful of your self that you will contribute the most for others and not at your expense.  Be good.  The future will be bright.

Thank you,
ZULFIKAR MOINUDDIN AHMED

\section{Minor Exegesis}

\subsection{Audience}
My message of May 14 2021 is addressed to all 7.8 billion human beings, regardless of ethnicity, nationality, language, sex, education level, and other demographic characteristics.  It is a personal message from myself to my people, the Human Race, at an individual level.

\subsection{Reach}

I used a group email for the message.  It is meant for eventual reach of everyone.  This is why it is dated explicitly.  It might reach some people quickly.  It might reach others in months, and yet others in centuries.  Reach is not a concern for me.  The message is time-invariant.  So long as the message reaches an individual of the species {\em homo sapien} it will have validity.

\subsection{My Extraordinary Talent In General Principles}

I am a rather retiring man in person who likes to socialise once in a while but am quite busy with my own thoughts and do not spend a lot of time in small social gatherings of less than 100 people.  Thus it might seem a bit strange that I am writing messages to the entire human race.  I am more talented at understanding simple clear ideas for billions of human beings where much of their complex details are integrated out and only some key features are prominent.  I am extremely confident that those who appreciate and listen to my message will experience much better lives in the long run.



\end{document}