\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Money is today opposite of Love but the Solution is Excess}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\section{Subtle Problem of Money}
Money has been difficult for me to understand, and I am not ignorant about the different viewpoints.  I am actually talented in professional Finance, and know perfectly well some of the great qualities of money.  At the same time, I understand perfectly well the Evil of Money.  Nietzsche was unimpressed after much thought of the Ascetic ideals in India.  This is not trivial because Rama and Buddha had abandoned their material possessions for their enlightenment, their spiritual journey, their meaningful adventures.  Nietzsche had settled on Wolfgang Von Goethe as an exemplar of his ubermensch -- which had nothing to do with marauding cruel barbaric blonde beast -- but had to do with spiritual refinement.  Goethe was not poor, and yet he had a refined poetic soul and a fine sense of the worldly.  And it was his worldly and un-ascetic aspect that Nietzsche attempted to highlight.  Nietzsche's spirituality was centered around an affirmation of life.  

All the above are preliminaries, and I have gone through my own abandonment of material possessions, and my own slow understanding.  I will present my understanding in scholarly terms, with scientific rigour in the end one day.

\section{My Solution to Money}
You can turn towards Money wholeheartedly.  You can turn away from Money in disgust.  Both have virtue in them.  You can be reconciled to Money as well and put your efforts elsewhere, and that is what Robert Emmon's positive psychology finds for well-being, that people are happier when they make money and achievements secondary to other things.

My solution is not personal; it is global.  It is that Money has been for certainly in the past five centuries but even for the past several millenia been a matter of scarcity and division.  This does not have to be the future at all.  It is difficult for us to see this clearly, but Global Central Banking with targeting of Global Unhappiness levels along with Global Inflation and Global Unemployment would increase the Money available to individuals without cost in Inflation.  Another project of mine is Global Individual Debt with \$5 trillion borrowed by China.

These projects arose from my resolution of issue of Money, which is that the problem is {\em artificial scarcity}.  There is no reason to consider Money to be anything other than like water.  Our ancestors had difficulty getting clean water and today it is tap water because of advances in technology.  In the same way, Money could be quite ubiquitous and not a significant part of one's headaches and sufferings with advances in Finance technology and knowledge.  When Money is not a significant worry in people's lives at all it will be like a Utility for everyone on Earth.  It will still demand some attention but nothing wild and excessive where countries go to war with each other for money; can you imagine countries going to war with each other today for tap water?  In the future, Money will be simply part of life.  That day has not come yet and will not come without effort.  We are not stuck in this situation where our relation with money is static -- and we sing about how we are slaves to money and then we die.  Money is only difficult because it is {\em primitive}.

\section{The Present: inverse relation between Money and Romantic Love}
Having shown some exit from the issues of money for the future, it is quite interesting that rape rates in the world can be predicted by log-GDP (per capita).  Then when we combine this with identification of rapes as a measure of negative Romantic Love Competence, we have the relationship of Money is Evil in the current world order.


\end{document}



\end{document}