\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Moral Value Distribution in Entire Human Race}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Summary}

In the past month I have discovered a number of salient facts about measured moral values for the entire human race and proposed a scientific model to explain all moral values across the entire human race.

We propose that moral value distribution in human race can be explained as a sum of two terms.  Before we explain the details, we want to return to the well-established results from Sewall Wright's {\em Index of Fixation} $F_{ST} = 0.07$ in a study from 2012 for human genetic variation.  The fact that emerges from genetic variation studies is that if we divide the human race by continental inhabitants, we find that around 3-7\% of the variation is due to between-group differences and around 93-97\% genetic differences are due to within-group differences.  I am not immune to human affairs and have been a strong advocate of acceptance by the masses of people of a {\em Single Human Race} based on this fact that Science had uncovered so long ago; the inference of course is that there are no 'biological races' in homo sapiens contrary to what was originally hypothesized by Carolus Linnaeus.

Now we describe the decomposition.  There exists a universal model that covers all human race moral values that explains around 91\% of the variation of human moral values that is ethnicity and nationality and culture-independent.  The remaining 9\% of the variation can be attributed to other factors such as ethnicity.  We have direct estimates due to ethnicity that attribute 2-8\% variation to this factor.  

Our major significant scientific discovery is that a Markov Chain model for ordered morals can explain around 91\% of all human moral values across the globe.

\section{Markov Moral Model}

See previous notes for the details.  The scientific hypothesis is that there exists an ordering of morals for every human being such that given measure -- in terms of preference in 1-10 scale for right or wrong for an issue --leads to explanation of all other moral values by a Markov Chain with a fixed 55-parameter Markov transition matrix $P_{moral}$ which we have been fitting to data.  

\section{Discrete Time Markov Chain Model is Fundamental to Human Race Morals}

We can draw various inferences from the success of the Markov Moral Model.  The first is that the stochastic regularity of the Markov transition Matrix cannot be avoided.  Even if there are variables found to predict moral values of individuals exactly in the future, when the population is taken into account, stochasticity {\em with regularity} cannot be avoided.  In other words, the variables that specify moral values of the individuals will then carry the regular stochasticity of the Markov Process.  

For those unfamiliar with it, Markov chains are stochastic or random and one cannot avoid the randomness; however, there is a strong regularity in Markov Processes which is stationarity or time-independence which makes these possible to study mathematically.  Their study is highly developed in probability theory.  Our adaptation for these models for sequences of morals was due to observing stability in pairwise joint frequencies for arbitrary pairs of moral values and not arbitrary.  We do not have an explanation for what underlies the regularity of joint distributions and leave this for the future.

\section{Markov Moral Model is a Great Vindication of Markov Process Theory}

I consider Human Moral Nature to be one of the most important scientific problems in our entire human Civilisation, and one that had not been adequately addressed at the total population scale ever before.  Markov Process theory has been successful in other settings but it is a fundamental surprise that these beautiful mathematical models have direct applications to Human Moral Nature at all.  This is a great vindication for the entire mathematical subject of Markov Process Theory.

\section{Personal Note}

There is no question in my mind that my Markov Moral Model for Human Race will be the beginning of a new Dawn of Civilisation on Earth.  Without clear scientific models, my beloved people, the Human Race has been afflicted with strife and conflict across the globe for many millenia.  My Markov Moral Model will bring Peace and Civilisation to the hapless Race of Man, by bringing Enlightenment and Self-Understanding.  This is of course the Duty of Genius, and I am delighted to take this role.  For millenia, Human Race has suffered with Darkness and Ignorance, distrust and misunderstanding.  Tyrants with Strife, Deceit, and Fear divided my Beloved People, and this is a great moment for transformation to a Civilised period of the History of Human Race.  
\end{document} 