\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Lecture to Harvard, Yale, Princeton, Berkeley and Stanford on Responsible Behaviour} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Virtuous Behaviour is to Respond}

I have been asking Harvard, Yale, Princeton, Stanford and Berkeley for some months now if they want to give me a couple of Ph.D.s and a full professorship based on my revolutionary work and they simply do not even have the courtesy to send a response with "no" or "yes".  This is the epitome of irresponsible behaviour.  It is not Virtuous, Just and Good.  It gives the impression of rather lacking in decisiveness and moral courage.  I don't understand why the top universities in America cannot see my tremendous genius work and give me a quick response about whether they can actually give me a couple of Ph.D.s and a full professorship or not.  It's just absurd.  I mean I am an adult and can handle a "no" without resentment but total silence is just irresponsible and lacking in moral courage.  What has happened to our best universities?  Why is there no moral responsibility anywhere to be found?  Why don't you just become more decisive?  This "I don't want liability" approach by simply not responding which D. E. Shaw also took is just not even civilised.  How are you going to influence and lead the world if you can't even have moral courage to take a stand?

\section{It's Your Fault If I Become Center of Truth Like Descartes or Socrates And You Are Deemed Less Relevant}

Some centuries ago, Rene Descartes began working on Empiricism and collapsed a huge industry of Humanism.  Earlier, Socrates formed Academy in Athens and formed the lofty point of advancements.  Four-Sphere Theory is advance over Einstein, Schroedinger and Lemaitre; and Quantitative Human Nature is the first time there is any quant scientific model for Human Morals.  If you dismiss me altogether, I will carry forward the Renaissance of the entire goddam Age from some hovel in San Fracisco and the world will diminish your position as intellectual center of great importance.  If this happens, I will not take blame for it, for I have given you all years of chances and you refuse to show respect for Zulf.  

Fate will decide what happens.  Nothing is without consequence, remember that.  You let Zulf suffer with disability income in Allen Texas and you get cushy salaries and tenure perks, the world will avenge this insolence.
\end{document}