\documentclass{amsart} 
\usepackage{amsmath}
\usepackage{verse}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Bill Gates is the Exceptional Malevolent Evil Man Who Proves the Rule}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Do Moral Values Matter?}

I was never excited about moral values, and for a very good reason.  It so happens that I am exceptionally good truthful person.  And when you are an exceptionally good truthful person, and you are happy with who you are, then moral values do not matter because your morals are expressed in your actions.  I am 48 now, and I never worried about it.  The man who convinced me that this was an error of mine, not to worry about moral values is Bill Gates.  He is the superstar of all Seven Deadly Sins in a symphony.  I have never actually come across a more horrendously disgusting abominable evil man as Bill Gates.  And now I am truly curious about moral values, the extent to which they exist, the point at which they fail, the good and evil within human beings. 

\section{Social Context of Good and Evil}

There is no Good and Evil for a completely solitary man.  Paul Simon's "I am a rock and I am an island" is a particular sort of hope, that we can live mostly in isolation.  This could be problematic too in some cases, but it is extremely damaging to the natural human psyche.  We are social animals, and good and evil are issues in social contexts.  Moral values and action are always fundamentally social issues, based on dealings with other people.  Bill Gates is disrespectful and contemptuous of other people which is bad, because I am far greater than him as an immortal genius.  I am generally a retiring solitary man these days but I am interested in doing some big things for my people the Human Race, and consider this to be important for my life.  But Bill Gates is so extremely horrendous as a man that I have to take a slightly indirect path, which is get rid of him completely while focusing on some positive things for the world.




\end{document}