\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Recommendation to Terminate Employment Of All Justice Department Higher Ups Collaborating With Bill Gates' Murder Plan}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{What I Learned}

April 29 2021.  I learned after a short consider by Silvio Berlusconi that Bill Gates had promised Justice Department Higher Ups that he could, using his horrific meta tactics, ensure my death.  Justice Department Higher Ups considered the 'pragmatic solution' that Bill Gates would succeed in my murder, and they made plans appropriate and had put a "hold off" of Justice Department action against Bill Gates.

\section{Deep Corruption Implied}

Complicity of Justice Department Higher Ups in collaboration with a murderer for a murder plan is deeply offensive to the foundations of United States of America and these corrupt US Justice Department officials ought to be sacked immediately.  The purpose of government according to the Declaration is to secure Natural Rights of all people.  Now I, Zulf, have never committed any crime in America, and the US Government is {\em obligated to secure} my Natural Rights.  Any agreement made between Justice Dept higher ups and Bill Gates that include my murder by Bill Gates -- and we understand that Bill Gates uses meta means and not physical means for murder -- shows both that Justice Dept Higher ups {\em knew all along} that Bill Gates was indeed a murderer and that {\em they approved of violation of my fundamental Natural Rights}.  It is the job of all US Federal Employees to understand that securing Natural Rights of Americans is the first priority of American government.

\section{Recommendations}

Bill Gates must be neutralised for he poses a grave threat to Natural Rights and health and life of the American people for he is simply a murderer.  He ought to be totally neutralised by military force.  Justice Department Higher Ups are corrupt and acting against the prime directive of the US Government and its purpose, which is securing Natural Rights.  They are incompetent to hold office in US Justice Department and in fact {\em in any part of US Government}.  They ought to be sacked immediately.

\end{document}


\end{document}