\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Some Comments on Charles Murray's {\em Human Diversity} Race Part}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Main Issues}

First of all I like this book, although I am thinking about the issues of Race as well, and I will roughly sketch out some major differences with Professor Murray.

\begin{itemize}
\item{Professor Murray emphasizes racial {\em differences} without insufficient attention to the much more powerful genetic commonality}

\item{Genetic differentiation for 75,000 years produces some measurable differences in 3-7\% range no more}
\end{itemize}

Charles Murray is focused on genetic difference of so-called races.  His arguments are technically valid, that SNPs stop varying more easily  as a group splinters off.  I love the fact that he says "snips".  I'm just going to call SNPs {\em snips} because they are important in biology and no one wants to read SNPs SNPs SNPs because that's just unreadable.  I'll call SNPs snips from now on. 

Here is my point of view. You look at four or five million years of co-evolution, say 75,000 years ago in Africa.  There's a meta tribe in East Africa that are Ancestors to all non-Africans.  I'll keep sticking to non-Africans because I think that the same arguments will work for Africans in the end.  So now you are in 75,000 years ago in East Africa.  You see such and such groups of people.  You genome sequence all of them in a snip snap because you're that good.  You snip snap the whole tribe and you have all their alleles.  You find that some amount, say 25 millions snips have multiple alleles.  

Here is the key point.  They haven't left yet for their great journey into Agriculture and all tribal massacres and kingdom formation, and captivity of all sorts of religious minority, and all the other conquest conquest things and peace and harmony things.  They are just hunting and gathering and hunting and gathering.  

See this is the thing.  All 100\% of their genetics is one tribe here.  So Murray's point that some people broke off and became genetically distinct is not the big issue for human race.  Fine, some of their snips changed and stopped varying etc. but that's residual, no more than 3-7\% of the genetic totality and that is what is measured by fixity index.  In other words, Murray's story does not have a proper preface, that the whole shebang for four-million years was a single race, and then the question is whether if you perturb this for 75,000 years, and discover 3-7\% variation from the totality, are we really talking about a different 'race' or are we talking about various cousins whose noses look quite different because noses always look different for cousins.  Fine, my nose is quite good, and I'm proud of my nose, but even my brother's nose seems that he's can't do a good looking down with the nose and so on.  

So that's the major issue.  Does 3-7\% genetic difference really matter enough to call these 'racial differences'.  I take the position that it's not enough, {\em compared to 4 million of co-evolution}.  Another way to see this is that genetic diversity decreased, because snips stopped having varying alleles.  That's fine.  But how is that a different genetic race in 75,000 years?  Time is important.  Let's do the simple computation, 
\[
75/4000 \sim 0.019
\]
So he's saying that we evolved for 4 million years and did not produce multiple races but in less than 2\% more time, we're genuinely new races now.  That does not compute for me.

 
\end{document}