\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{I am American National Treasure Bill Gates is a Charlatan Criminal Con Man Malevolent Demon White Supremacist Traitor}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates is no American National Treasure}

Bill Gates is not even American in his outlook, nor does he care about any American laws because he does not know what they are and does not understand them.  He considers Natural Rights to be 'claptrap' and cuts up non-white people's eyes with the dream of slavery for blacks and conquest of all non-white people for a new colonialism.  He is no National Treasure.  He has not done an honest day's work in his life.  All his documentaries are totally fake self-aggrandising propaganda.  He is a pathological liar with no compunction.  When you make him some money, the ingrate will retaliate with destruction of your Ancestral meta, your Family meta, dip industrial meta in your blood, cut deep into your eyes to your deep interior to seek material to enslave you.  If this is American National Treasure I do not know what is American Putrid Refuse.  Bill Gates cannot become American National Treasure in a million years.  He is a con man, a total charlatan.  If you ask him to show his code he deflects and refuses because he does not have any good work. He was an enslaver and his only talent is to obsessively and continuously lie to the public with a benevolent mask and plot to be a Global Autocrat following Egyptian Pharaohs enslaving the Human Race.  We do not need this sort of National Treasure as Bill Gates in America.  He should be put to death for harming my Natural Rights by putting industrial meta to mangle my flesh.  He says this is his white right.  Do we want to celebrate this sort of National Treasure in America.

\section{I Am Far Greater American National Treasure Than Bill Gates}

I have resolved three centuries of theoretical physics cleanly with Four-Sphere Theory for macroscopic physics; I have overthrown gravity, big bang, expansion, given the final law of Electromagnetism which is S4 Electromagnetism and Freeman Dyson agrees that it is right. 

I have provided Quantitative Human Nature models that showed clearly and quantitatively that the structure of Human Morality is based on exponential laws and is uniform across the globe, across nations and ethnicities, across religions.  

I have made deep advances in Finance, with my Medium Frequency Strategy and Closed Form Long Memory Stochastic Volatility Models being the most accurate match to market in the world, and the strategy is successful in multiple markets with D. E. Shaw \& Co. trading it.  I gave the opportunity to Bill Gates to put money into it.  What did the stupid cunt do?  He retaliated with harm to my eyes and grave destruction.  We don't need these types of Demons alive at all, let alone being celebrated as "National Treasure".  He is a con man, a charlatan, an enslaver, a Demon whose malevolence knows no bound, a man without moral compass with a saintly mask and claims about 'philanthropy' while he plots the harm to my Beloved people the Human Race.  It is a matter of National Shame that such horrific ugly malevolent criminals are considered National Treasure in America today.


\end{document}