\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{On the Fundamental Importance of Natural Rights to Me Personally} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Natural Rights of Man}

Before John Locke worked out parts of the Classical Liberal philosophy that formed the basis of the United States, there was no concept of Natural Rights that are inalienable for every human being born on Earth, endowed by the Creator.  This is not rhetoric.  I have spent years of my life considering this, that this idea, that there are Natural Rights that are inalienable and granted by the Creator, i.e. Nature, and not by other human beings, that others may secure or violate but do not grant and cannot take away, is one of the most significant advances of the entire Human Civilisation in our history.  This is such a nontrivial and successful idea, that I have tremendous faith that security of Natural Rights will be the foundation of a far better future of Human Civilisation than exists today.  For me, who had been Atheist since 1979, there was a certain religious adaptation to it.  One can remove Creator from the process and see how potent this idea is, that there are Natural Rights that are inviolable, and legitimate governments secure them and gain their legitimacy {\em by securing them}.  I am a religious fanatic, a zealot, if you will on Natural Rights, for I cannot see anything else that can produce a reasonable outcome for the entire Human Race either, in the Kantian manner.  I have a complex religion, but Natural Rights of all my Belove People the Human Race is not separate from my religion.

\section{I Am An Enlightened Successor of James Madison}

Like my illustrious predecessor James Madison, I am a Princetonian, and although I did not go professionally into American government service, I am quite a bit more clear about Natural Rights than James Madison was.  They were pioneers, Madison, Jefferson, Washington, etc.  But they were far more confused about ethnicity issues than I am.  I am far more clear that Natural Rights of all people of all ethnicities is sacred.  For me it is obviously a great deed to abolish the entire American Government in order to strengthen security of Natural Rights in America.  It would be a great honour for me, and a matter of great heroism for which my progeny would consider me truly magnificent and great.  So I will obviously be interested in the opportunity to abolish the US Government if it failed to secure my and other Americans' Natural Rights.

\section{I Am Not Radical}

When the US Government Agencies do not secure my Natural Rights and I do not break the Laws of the Republic but give privilege and Liberty and freedom to a vile malevolent criminal who does not respect any law like Bill Gates, then it is United States Government that is being radical and not I.  I stand on the firm grounds of US Declaration of Independence, while the US Government is off the rails.  Abolishing US Government may be our only hope for legitimate politics at Home and Abroad.


\end{document}