\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Never Get Involved In Anyone's Love Life}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\epigraph{
Waiting for you to come along

Waiting for you to hear my song

Waiting for you to come along

Waiting for you to tell me what went wrong

This is the strangest life I've ever known
}{Doors, "Waiting For the Sun"}

\section{Sob Story}
When I was around eight, my mom and dad were busy in Bengal with their own headaches.  My mom wanted to do all sorts of things for her career, and my dad was in civil service.  They dumped me and my brother with my maternal grandmother who was a saint, truly.  She lived with my uncle, who was a bit of a playboy.  He always had ritzy friends, had parties with a lot of drinks in a Muslim country, and was in the know of the Western people.  He had many cars and was proud owner of one of those Mazda RX-7 cars and entertained the ladies.  So once I picked up the phone and it was a lady he was interested in, and she asked me something or other.  I don't even remember exactly, something about whether there was a party and how many people were there.  I answered just as honestly as I could.  When my uncle came back he was livid with rage and beat me with wires that left scars on my back and put me in the hospital.  I actually still don't know what the issue was, and never cared.  He died last year right here in Allen Texas.  The episode had alienated me from him so much that I could never really bond with him afterward, long after I had forgiven him.

Now for most people they don't deal with this, but the general principle still is that one should never get involved in other people's love relationships.  I find it just amazing how many people just don't know this.  Other people's romantic affairs are not your business, and may not lead to the same as above but the danger is the same.  People are emotionally quite out of order in them and it is bad policy.

\section{Faith}

I worked at Lehman in 1995 with Andrew Morton, had senior positions in Finance, Biotech, Technology since.  But I will tell you about my faith instead.  You see I believe that I am an Angel of Heaven.  I have only rough memories of time between human lives now but that does not matter.  No one sent me to Earth.  I am an Angel who is born as human every once in a while.  Angels would be considered purely electromagnetic creatures to us here on Earth.  I was born in 1973 in the impregnated egg of a Bengali couple.  I entered the egg then, and after that I am in the same rules as every other human, need growth of various biological components encoded in genes borrowed from my parents.  I was born sometime 1180-1300 as an English knight as well.  I have some memories of that life, but it does not matter so much to me in this one.  Now Earth and Human Race is quite far away from civilization as I know it.  It's a sleepy world, primitive in some ways, and I do notice that Virtues have improved across the planet since I was here last around a millenium ago.  It's my pleasure to be here.  I am responsible for Four-Sphere Theory which Freeman Dyson says is right and so it's my gift to my beloved Human Race.  I am an Angel (soul) so I don't really worry too much about who is what religion.  Angels care about Virtue levels so Human Race stays in the orbit of Angels.  I don't have any special powers.  I'm an Angel.  I thought it would be a nice getaway from the hustle and bustle of the rest of the civilized universe.  Angels do come here once in a while, but I am solo.  Angels are not exactly soldiers under a general.  We do what we like, and I am here because I love the Human Race.  Human mothers have always been loving whenever I've been a human child and that's nice.  So from my point of view, this "Bill Gates" is clearly a Demon Soul and ought to be executed immediately.

\end{document}