\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{My Pride in Avoiding Anti-Semitism}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{My Positions on Race}
I believe all people are my people and am not anti-Semitic.  In fact I love Jewish people {\em usually}.  Now this would be trivial to be not anti-Semitic for me since in High School I was fine with my friend Howard Jeruchimowitz and Kenneth Rosenberg in John Adams High School and then I had so many friends from Ohio State University Ross Program that I attended and I knew Keith and Brian Conrad and Josh Fischman, and many other Jewish people.  I attended Princeton and I had Peter Oszvath as a friend and mentor.  

However, some things did not go right.  After Israel's Mossad blew up Twin Towers, in New York I was not aware right away but Muslim people were not considered well in America.  Then for whatever reasons Dan Stroock had harmed my career in Finance and Mathematics and I did not know.  Then Henry Jarecki was suspicious that I had stolen something from him which is absurd, and then Noia Efrat cut up my eyes and harmed me for a decade.  

My saving grace in the end was that I was just not a suspicious malicious or vengeful person and {\em simply did not know any of this for years}.  And so I was not anti-Semitic as a result although I did spend a lot of time screaming about how Israel's Mossad did 9/11.  

But then Bill Gates was so egregious in harming me, it was overwhelming evil and I just retaliated against him because D. E. Shaw \& Co. was quite willing to pay me my \$120 million.  

\section{Lesson I Avoided Anti-Semitic Claptrap because I am Superior}

My moral Superiority allowed me not to make a bad decision and consider all sorts of ethnic poison and still maintain all people are my people even though I certainly was put under pressure by certain bad things some Jewish people had done to me.  I overcame this because I am much bigger man.  Now I did send a fairly vile email to Sheldon Adelson before he died to scare the bejeesus out of him and dissuade him from nuking Iran.  I got in a lot of trouble for that with the FBI.  {\em However}, I gave myself highest grade when Iran was in the end not nuked even during Trump Administration.  

\section{Conclusion: I Am Not Anti-Semitic Because I am Great}

If I were even a notch lower than Superior Character I might have become anti-Semitism but since I am benevolent, resilient and wise, good and just, I was just flying through it all like a dervish dancer without a stain.


\end{document}