\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{On the Power of Bill Gates and Power of Fate}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle


\section{Power is manipulation of 4D Electromagnetic Substance}

Bill Gates' power relies on the manipulation of 4D Electromagnetic substance.  I hypothesize that this substance is made of magnetic monopoles.  Using this substance, he has mastered various abilities to engage with human minds, etc.  This is broad.  I won't try to prove it.

\section{This 4D matter pervades all of Universe}

In my understanding of the universe, substance similar to what Bill Gates uses to have power pervades the entire universe.  Specifically this 4D matter between galaxies is literally like a vast ocean in space and behaves just like open ocean, and it moves by Natural forces, and is much more powerful than any control Bill Gates can acquire.  His control of this substance is literally like a boy playing with sandcastles on the shore of an ocean.  True power is in the tides of the ocean, and can totally wipe out his power and empire and all things that he controls.

\section{I will not produce a theory of this soon}

Without a great deal of observational {\em measurements} it is not possible to produce a good science, regardless of our capabilities for creative imagination.  In George Lucas' movies Star Wars you have the "Force" that governs the universe with good and bad elements.  This is not so bad.  My terminology is Ocean of Fate for this "Force" and its rough.  The entire universe is governed broadly by the forces in this Ocean, and we simply do not understand it yet.  My S4 Electromagnetic law governs the whole of existence but of course there is more as we know from currents under the oceans on Earth.  I will not be interested in speculating about what exists, and this will have to be mysterious for Human Race.

Empirical three-dimensional science is simply wrong; all the deepest mysteries of Nature are in the fourth purely electromagnetic spatial dimension.

\end{document}
