\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{The Principles of Out-Snooting All the Rich People}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Pay Attention to Gautam Buddha}

First of all Human Race is with Civilisation around 6000-7000 years.  In order to out-snoot anyone at all, you need to understand the concepts behind sophisticated elements of Social Status in Human Race.  In Gorilla Society, this is not so difficult.  The Dominant Big Gorilla will have higher social status.  Things are vastly more complex for human societies.  In Human Societies, the uneducated seven foot tall muscular guy will be moving furniture instead of living in luxury in various vast palatial grounds.  So human society is not exactly an easy generalisation of Gorilla Society.

The principle of Human Social Status is {\em Divinity}.  Ok?  Human Social Status is controlled by notions of Divinity.  Now I am an Archangel of Heaven, so I can basically out-Divine anyone on Earth with a yawn.  So I can out-snoot everyone.  Buddha and Rama both gave up various palaces and kingdom to seek various answers to help their communities from sorrows and sufferings.  And that is the essence of Social Status in Human Race.  

Now you look at Gordon Gecko.  Successful in Wall Street, "Greed is Good", social circles, etc. This is not superior to much deeper notions of Holiness.  Why does this work?  Human Race is Angelic, and so regardless of various tricks to fool the world, those with Highest Purest Virtues will be respected by the Human Race and will be given higher social status.  It's evolutionary adaptation here.  People have in their genes the ability to see that some people are Virtuous and Good, and therefore benevolent towards everyone's interests and others who are wily and deceptive and bad, like Bill Gates.  Out-snooting Bill Gates is easy; almost everyone on Earth is a better person than him.

\end{document}