\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Basic Statistics of Peace-Loving People by Ethnicities}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Why We Need This}

I am extremely irritated that people have all sorts of looney bin ideas about other people and prejudices and such.  In order for this planet to work right, every school child should have a clear idea of some basic data.  For example, every child on Earth should learn these facts.

\section{Around 95\% of Every Ethnicity feel Violence Against Others is Wrong}

Let me get the exact statistics, from Q191 of World Values Survey.

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Thu May  6 21:17:14 2021
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 & eth & good \\ 
  \hline
1 & Arab & 98.25 \\ 
  2 & Black & 94.10 \\ 
  3 & East Asian & 95.27 \\ 
  4 & Indian & 97.38 \\ 
  5 & Other & 92.39 \\ 
  6 & White & 94.15 \\ 
   \hline
\end{tabular}
\end{table}

This is crucial for everyone to know, that roughly 95\% of people in the world are opposed to violence against other {\em regardless of ethnicity}.  This is a strong fact, and it is regular.  People around the world are mostly non-violent, peace-loving people.

\section{Simple Exercises}

Suppose you pick a random person of some ethnicity around the world, say from a poor country in Africa?  What is the probability that he thinks violence against other people is justified?  

The answer is definitely less than 5\% chance.  

Suppose you pick someone white from Montana far from the cities. What is the probability that he thinks that person thinks violence against other people is justified.  

The answer is definitely less than 5\%.

Whatever you imagine the world to be, if after doing this exercise for a while you think you know what a person who thinks violence against other people is justified, then try again.  

I will show you the statistics of people of different ethnicities who think that violence against other people is {\em always justified}.  You will notice that they occur in {\em all ethnicities}.  There are no ethnic violence genes out there.  There are issues of tail properties of all populations.  

You can call what I am doing trivia.  It ought to be trivia but unfortunately we live in a world where this basic information is not taught to every child, because this is a {\em Primitive Mercantile Age of Man}.  We're going to fix it right away.  I am so irritated by idiots who do not know these things and pretend to be educated.

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Thu May  6 21:25:13 2021
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 & eth & bad \\ 
  \hline
1 & Arab & 0.17 \\ 
  2 & Black & 3.21 \\ 
  3 & East Asian & 0.83 \\ 
  4 & Indian & 0.51 \\ 
  5 & Other & 1.66 \\ 
  6 & White & 3.02 \\ 
   \hline
\end{tabular}
\end{table}

Here sampling produced a range from Arabs at $0.17\%$ to blacks at $3.21\%$.  These are the percentages of people who believe violence against other people is always justified.  Now they are all wrong, but as you see, they are of all ethnicities, and they are all smaller than $3.5\%$.

These are the rough good and bad morals versus violence in the {\em entire planet Earth} ok?  You need to know this in order to have rational sense on Earth.

You could make a huge amount of noise about differences of these numbers by ethnicity but they are irrelevant.  The probability that anyone of {\em any ethnicity} will be in the bad camp is roughly less than 3.5\%.  No rational person ought to then have all manner of ethnic fear that the random person from anywhere is going to be a violent murderer.  They won't; the chance is quite small.

\end{document}