\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}\title{My Place in History of Racism}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Fate Determined My Place}

I had no idea that Bill Gates was a White Supremacist.  I thought he was an ordinary successful technology businessman.  I offered him to make some money because I worked on some amazing Finance, some of the best in the world with Medium Frequency Strategy, and D. E.Shaw \& Co. started trading it.  I {\em seriously expected} to take my cut of \$120 million and move on.  But it turned out that Bill Gates was White Supremacist and he decided that my work was 'trivia' and decided that I'm {\em not worth} \$120 million.  Then he cut up my eyes and destroyed all manner of important inner personal meta following more White Supremacist butcher techniques that even the worst Nazi War Criminals never employed against Jews before the war (according to Christine Lagarde).  Now I have had many white lovers in the past, so I am not your ordinary garden-variety anti-white nutcase.  But so Fate brought me to this conflict, and Fate challenged my Honour and demanded that I react with whatever I got.  And so I am fine with it.  I will struggle and I will win against Bill Gates the White Supremacist Evil Cunt and I will eradicate Racism on Earth.  Why not?  When Fate calls you to your greatness, who are you to deny Fate?

The struggle against racism is distinguished with two centuries of struggle, and mostly it was black people who faced this.  But I am not racial in my views, and I know most white people are not enthusiastic about White Supremacy.  You can say, "That's too sad, Zulf; I am sorry for your troubles."  But my life is precious and my place in History of Human Race is Immortal, so sad or not sad, I will struggle on and I will win and Bill Gates will be wiped out from all of history in the end.  

\section{I Eradicated Race}

My results from the Quantitative Human Race Model showed that Whites are {\em morally indistinguishable} from others of the Human Race.  And since Bill Gates has harmed me egregiously I am not sensitive about white people who are offended by {\em anything I do}.  I don't worry about offending people who are White or Black or Yellow or Brown.  I don't give a damn.

I'm Zulf ok?  I'm Zulf and I don't give a flying fuck.  Ok?
\end{document}