\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Christopher Boehm on Pleistocene Society}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle


Christopher Boehm's {\em Moral Animal: The Evolution of Virtue, Altruism, and Shame} addresses moral values say 75,000BP in East Africa.  He considers "Late Pleistocene Appropriate" some contemporary forager societies with hunter-gathering.  In pages 79--82 he begins to consider some of the features.  The nomadic groups are 20--30, large game is shared communally, but families have separate hearths.  The hunters are political equals.  Social control mechanisms are similar for theft and bullying.

We can expect then that egalitarianism existed with social sharing of food and separation of families in 75,000.  And this is all part of human nature, the sharing of game, egalitarian politics, and some moral taboos, and family separation. It is here that we can already find some common evolutionary depth in social organisation.  We are extremely pleased with the work of Christopher Boehm in this book because it is very difficult to have some confidence in the life of Pleistocene Social Structure.

\section{The Coup of John Locke and Thomas Jefferson}

That it is self-evident that all men (everywhere in the world) are created equal was a coup that is quite spectacular to behold.  Boehm's recent research makes clear that hunter-gatherer nomadic bands of families of 20--30 have egalitarian political status among the hunters and big game is shared by the whole tribe.  The egalitarian component was spectacularly successful in the American experience.  The recent understanding of Early Pleistocene Society makes clear as well the sharing of large game.  On the other hand, Individualism was in fact not natural in Pleistocene. This was a grave error of Jean-Jacques Rousseau who Romanticised the primitive state of Man as solitary.  We have always been social even 75,000 years ago, and we have always had families with separate hearths is the inference.  This is extremely illuminating because the cooperative nature of human being as well as Romantic Love between couples were quite clearly established in hunter-gather nomadic societies of 75,000BP in East Africa.

Now I do not believe at all that this was different for two million years prior to Exit from Africa 75,000 BP.  And by and large by this point Human Nature had formed and it formed in such a way as to ensure that egalitarian political organisation among hunters and family structure and collective sharing of large game were simply deeply evolved parts of our genetic matter and psychology.  This is a partial explanation of the universality I had discovered in exponential distribution in moral opinions.  More than 75,000 years ago, for several million years, this egalitarian structure had evolved, and this structure {\em with pair-bonded families} has the deepest example.  Here survival pressures ensured in the end the propagation of the genetic matter and isolation and ostracism implied certain death.  Survival pressures thus kept this egalitarian structures intact.  

\section{Settled Agriculture is 12,000BP from Fertile Crescent}

Settled Agriculture came much later, in 12,000 BP in the Fertile Crescent and some other independent beginnings.  Social morality by then had been strongly developed naturally.  There are issues of bullying and theft and methods of social control are similar in the contemporary "Late Pleistocene Appropriate" forager societies.  

\section{Cannibalism and other Exotic States were Highly Abnormal in Pleistocene History}

Bill Gates has recently declared me "quarry".  Now quarry implies hunting for food.  In other words, Bill Gates implies his taste for cannibalism, and since I am quite merciless, I would remind people of Hannibal Lechter played by Anthony Hopkins in {\em Silence of the Lambs} who ate human brains.  As we see above, the norm of Pleistocene man was large game shared by the group and cannibalism is not a major factor around 75,000 BP in East Africa among our ancestors.  In particular I claim quite confidently that Cannibalism was not Human Nature, and the cases found of Cannibalism in the past are exceptional rather than the norm of 99.9\% of the population.

\section{}




\end{document}
