\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf Waxes Poetic About Reminiscences of Princeton} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Princeton Made Me Feel Normal}

I don't know what reputation Princeton has to the external world but for me it was a magical place.  I did not even realise how magical it was for me till well after I had to deal with people who are not lofty and high falutin by nature.  There are better words for this but this will do.

Looking back all the people I came upon at Princeton were just much loftier and high falutin compared to almost everyone I met afterward.  Princeton is like Rivendell from the Lord of the Rings.  It's so special and magical that you can't actually believe that it is real at all, and then years go by and suddenly you feel extremely fortunate because anywhere else you would have been destroyed and Princeton made you feel that you were normal, and it was okay to be lofty and high falutin and think that vastly intellectually esoteric obsessions were not wrong and absurd and silly but perfectly right.

No other university in the entire world can come close to this ability of Princeton to make one's totally esoteric passionate concerns seem quite serious and important in the world.

After dealing with Bill Gates for a while, whos is simply incapable of rising above the most disgustingly low and plebian obsessions, tribal and primitive and vastly low in his ordering of priorities, totally uncouth and lacking in civilised cultivation, you come to realise the enormous fortune that accompanied your brief student period at Princeton.  

In the rest of the world, money is more important, and power; in the rest of the world, exploitation is suave and high falutin lofty concerns are impractical.  This was not so at Princeton.  At Princeton, people genuinely cared about the most high falutin and impractical and idealistic and extremely far from practical reality without feeling abnormal at all.  

I am profoundly grateful for my Princeton experience.  

\section{Great People}

I had lunch with John Nash a few times.  I met Elias Stein and Charlie Fefferman and Terry Tao.  I was mentored by Peter Oszvath.  There were many great professors there, and great students too.  One does not realise the wonderful people who actually had substance within them as I had come across at Princeton.  It's truly a marvelous experience, and I don't think I would have any of the progress that I have made completely independently without the fundamental experience of feeling {\em normal} for your intellectual obsessions that Princeton provided.

\section{Bill Gates is Less Civilised than any Hunter-Gatherer or Cave Dweller in History}

Harvard cannot be blamed for the horrific lack of Civilisation of Bill Gates.  Princeton to me was the epitome of Civilised West, and people treated each other with extraordinary respect.  The lack of disrespect shown by Bill Gates makes him totally without any trace of Civilisation; Tarzan the Lord of the Jungle was infinitely more Civilised than Bill Gates.  Now he happened to have dropped out of Harvard, so Harvard cannot be blamed for this scourge on Human Civilisation, this man of such low Civilisational state that even the most barbaric cults of history would shun him for being too incapable of absorbing civilised norms.

The contrast between all the people I knew from Princeton, who were not just greatly gifted but respectful and encouraging, always benevolent and Bill Gates who would destroy all that is good and civilised in the world, whose attitudes are purely horrific and barbaric, who would be chased out of any savage society from any jungles of the past for inability to absorb civilised norms is profound.  I have never encountered a more dreadfully savage barbaric man than Bill Gates.

\section{Zulf's Clans}

I am a Princetonian with great accolades from my undergraduate years.  I am a Princeton Insider regardless of how long I have not been wining and dining with my Princeton classmates and friends.

I am in the Finance Clan. I worked for Andy Morton in 1995 and he respects my abilities and so do Ron Liesching and Robert Merton.  So I am a Finance Insider as well.

I worked directly for Robert Reich in technology and he thinks I am finicky but good.  My code is public.  So I am in the Technology Clan.

I am doing absolutely great genius Science.  My ex-colleagues Perry de Valpine and Hans Bitter and I have mended our differences and regardless physicists know who I am.

I am in the American Clan, and a vocal supporter of fundamental sacredness of Natural Rights.

So tell me, Bill Gates, what Clans do you actually represent besides "White Supremacy"?  You have been a liar and charlatan all your life regarding your life and works in your self-promotion propaganda material.  Who knows you exactly?  Do they know that you were strongly a psychopath from childhood?

\end{document}
