\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{All White Racist Ideas Need to Be Cleansed from American Government with Extreme Prejudice Right Away}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{My Condition}

I am literally out of the blue hit by racist malevolence that is just unimaginable by Bill Gates including use of US War meta against my body meta violating Geneva Convention, mixing of US Military corrosive meta with my blood meta which causes continuous physical pain, rotting of my teeth, huge amount torture in cutting up my eyes including use of Medieval torture devices in meta and African slave meta, and nonstop other issues from Bill Gates who has been continuously trying to murder and kill me with vast destruction of my Ancestral Indian meta, industrial meta damaging my exoskeleton and this is nonending.

\section{Bill Gates' Conviction:  Nothing will happen to him}

Bill Gates continues because he literally has the conviction that he has white right to 'conquest' right on American soil to Americans like me, and that regardless he is immune to any repercussions because he is white.  To consider this 'outrageous' is not even respectful to the scale of things. 

This happens because he is partly {\em right}.  United States Government and Society has given him this idea; he does not have this idea out of thin air that his being white will give him immunity from any consequences.  This cannot be tolerated, must not be tolerated and the United States of America must take severe action to punish and fire every single motherfucker who supports these things by Bill Gates.  I am so incensed I think they should all be burned at the stake immediately.  They are the rot of this nation, and their passage out to death will cleanse this nation of pure evil.  Racism is not a matter of political correctness; it is a matter of producing these vile horrific monsters who have glib confidence that no matter how vile and abominable and outrageous is their malevolence, there will be support for them in the end from government of the United States.  This cannot be tolerated, must not be tolerated, and the international community ought to be involved in thorough cleansing of American Government to weed out every single racial man and woman in the country and unceremoniously toss them into the ocean.  White Americans are good people, and tolerance and respect are part and parcel of our civilised existence of all ethnicities.  We cannot tolerate any more the creation of these sorts of monsters from their firm faith that their horrific crimes will be overlooked because they are white.  That is an insult to the foundations of this Nation, and injurious to the rest of the white people who are struggling with nonwhites to build a future for the country that is worthwhile for our children.

\end{document}
