\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Thoughts on What Is Ridiculous about Racial Supremacy} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Conventional Ideas of Closeness}

Not long ago, I constructed a beautiful model of dynamics of trust as one moves away from family, to friends and neighbors, to strangers, to people of other countries.  There is a precise quantitative relationship there.  There is an objective human nature element in these, and so in some sense, you can see how racial supremacy ideas can lead to some positive results.  You could have positive reinforcement and pride.  Nationalism has this quality.  

\section{Objective Clarity Regarding Ethinc Effects on Morals Did Not Exist Before My Discoveries}

In the past four thousand years of civilisation, the relative independence of moral values from ethnicity -- i.e. 6.5\%-9.5\% -- was simply not known at all.  It is almost impossible to guess and speculate on these things without measurement.  I personally was remarkably fortunate in holding inclusive views about people mostly from life experiences, friends and lovers from ethnicities different from my own in America, etc.  But for most people, belief was random based on no real knowledge and anecdotes and political propaganda.  So I understand quite clearly just how important my discoveries are for the future of the entire human race.  Racial supremacy theories are today tied to far right in America and Europe mainly, but these have developed, grown, and collapsed routinely across the globe.  It is my great fortune to put an end to this state of affairs.  My results show that ethnicity does not have a great influence on universal human race moral values, and therefore both superior and inferior moral characters are distributed roughly the same way across all ethnicities.  This has been a difficult journey for the human race.  Racial strife in America is high and Bill Gates is putting huge amounts of money and resources into various White Supremacist World Orders.  

\section{Optimal Productive Environments Are Respectful}

Genuine mutual respect marks the productive collaboration that produces the best results in multi-ethnic environments.  This is well-known in coastal cities in America as well as in London.  But provincial biases are ever-present.

\section{Individual Level Reasoning}

I think I am the Chosen One, and all other people are special in their own way but not as Chosen as myself.  This does not lead me to treating people with disrespect.  

I will show you what my reaction is when I am treated with disrespect.  Here is an email I wrote to Media at Gates Foundation today.

SO YOU DECIDED TO MISTREAT EVERYONE NONWHITE FROM 1970S YOU STUPID ILLITERATE CUNT BILL GATES?
Inbox

zulfikar.ahmed@gmail.com <zulfikar.ahmed@gmail.com>
7:29 AM (36 minutes ago) June 4 2021


BILL GATES,

You stupid illiterate pea-brained lowlife cunt you decided to mistreat everyone nonwhite from the 1970s eh?  I'll show you mistreatment you pathetic little shit.  I'll have all your assets confiscated and your ugly little face barred from the United States of America permanently you little worthless cunt.  You want to cut into my eyes inferior little intellectually challenged lying little shit huh?  

Thanks,
ZULFIKAR MOINUDDIN AHMED

I have no apologies whatsoever for any part of the letter.  This is a normal reaction to being treated with disrespect.  The sheer normality of my reaction ought to be a good enough reason not to treat anyone with disrespect, especially using racial supremacist views.




\end{document}