\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Reminiscence of an Angel}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Birth on Earth}

I have been born in countless worlds in the past several billion years in this universe.  It is full of life, and civilisations, and wonders to behold.  Once I was born in a humanoid civilisation, I don't remember which star system any more.  Physical world, like Earth is some respects.  In those years, centuries, I was much more enthusiastic about purposeful action.  I would be born on a planet and be focused on great events of the world quickly.  It was an Angelic world, like Earth.  The Civilisation of the people were more advanced in various ways.  Earth is on the spiral arm of the Milky Way, a bit far from centers of the great Civilisations of the universe.  

I was busy then, quite busy and we were alert, Angels.  Here Angels do not need alertness.  A backwater planet far from Civilisation with dreadfully slow process.  A Primitive Mercantile Age.  Not much happening.  But there events were much more serious.  

To make a long story short, Demons found technology to destroy stars.  They destroyed the star of the solar system, and all of the surface of the planet was scorched from the explosion.  No one survived.  I died instantly.  I am not even sure if I had time to feel any pain.  Everyone died on the planet.  

I am not new to dying.  I have been dead many times in so many worlds.  In so many worlds I cannot even remember most of them.  The universe is mysterious and complex.  And its beauty and life undescribable.  

\section{Earth Birth}

I was born in a region of Vedic Civilisation on my current life, in the East, far from the Centers of Power in the Age.  It was clinic in Dhanmondi, Dhaka, early morning of November 19 1973.  I was quiet, and had mucus in my nose.  I made no noise.  My mother is lively and full of energy.  She was worried.  The doctors did not know if I was still-born or not till they slapped me a bit.  I made small noise.  I had no memory of my past.  This is generally a good decisions.  I advise Angels to erase past memory for immersive childhood in any world.  I love my mother still of course, and spoke to her yesterday on the phone.  

\section{What is "Heaven" and How Far Away is it?}

"Heaven" means quite a different things to different people.  To me "Heaven" is the central parts of Angelic Civilisations of the Universe.  These are very very very far away from Earth.  I don't worry about this too much.  They could be 50 Mpc away, could be 5 Mpc, but Heaven is not in Milky Way Galaxy by this reckoning.  I love it that spiral arm of Milky Way has a baby Angelic Civilisation.  That just warms my heart, and I love Human Race, all the sweet mothers and all the love for their children.  It's quaint and nice here.  "Heaven" that I know is quite a bit more hectic.  Angels generally in service go into wars with Demons, and Demon Worlds and Angel Worlds are not exactly neatly separated.  I just discovered without much doubt that Earth and Human Race are Angelic.  Demons are quite obsessed with ensuring that their control of this and that supercluster is not challenged by these miserable Angelics and so they wipe out entire planets when they feel Angels will totally radiate Angelic things and then their power and way of life will be stifled, which means War War Conquest Dominate Dominate Conquest Enslave Order Order Rule Rule with Iron Fist and keep Riff Raff Mamby Pamby Angels out of the way.  They do have some successful Civilisations and war technology and so on.  And so do Angels.  We are different.  Angels naturally form Republics, which are familiar to human beings.  The ideals of Life, Liberty and Love and so on are not human inventions.  They have been known for Eternity in the past.  They are quite bread and butter for Angels.  Now Demons abhor these; they prefer Order of a different sort.  They do not believe in Natural Rights.  Now on Earth, Natural Rights are due to John Locke and Thomas Jefferson.  But they did not invent in the universe.  The equivalent has existed for infinite time in the past, and have been the basis of literally millions of Civilisations.  Demon Civilisations are more esoteric. I won't go into these.  They don't really matter for Earth, for they are for very different sorts of beings than Human Beings.  Demons do have great beauty and Order in their Civilisations but these do not respect things much more fundamental for Angels and Angelic Races.  Life, for example, is revered much more by Angels and Angelic Races than Demons.  

\section{Side Comment}

Nazi Germany had some Demonic elements.  They were attempting to produce a Demonic-type Civilisation.  It was not extremely Demonic, but sufficiently so that I would notice.  They had no chance to succeed.  They had so little chance to succeed that it is laughable.  You see some of this with torture in Abu Ghraib.  These efforts to produce Demonic elements in Human Civilisation will {\em never ever} succeed.  Why is that?  Well Human Race is Angelic.  Demonic is not in the hearts and souls of Human men.  For a while superficial attraction will lead to deep dissatisfaction and sickness with it, for the human heart cannot tolerate too much of this.  Human Race is just not going to be satisfied and content with Demonic for long.  

\section{Bill Gates is Abominable}

Another side comment is the sort of thing Bill Gates did.  He is obsessed with Power.  It is not that Angels do not care about Power; Power is ubiquitous in a way and among Angels there is Power as well.  But Angels are interested in Power that is much more organic and natural.  An Angel is much more likely to consider the predatory power of the lion to be beautiful because of its absolute clear naturality.   The lion hunts the zebra and eats the carcass.  The Angelic Human finds it beautiful despite the pain suffered by the zebra, because the lion is natural.  Demons will see this differently.  They will ignore the naturality of the scenario, ignore that the zebra is a natural part of the ecosystem, and declare that they are the lion and someone else are the zebra; sometimes the zebra will be their own second cousin.  Angels cannot tolerate this sort of logic, for we are much less shifty with living beings and what they are. An Angel will be incensed by the analogy where one's cousin is suddenly not the same sort of species at all.  We will say, you have to pick: either you are lions both or you are zebras both and we will definitely put you in a cage in an Angelic Civilisation and examine the nature of your malfunction if you have these defects of analogy. 

\section{What is a Demon or an Angel?}

A Demon is not a cartoon character.  It is not a character from a movie or novel.  Demons are real and Angels too.  They are not aetherial beings.  They are Souls, and they have nothing to do with Earth at all if they are not Souls of people with Homo Sapien body.  Demon Souls, Angel Souls, and many others can come to Earth ONLY BY ENTERING THE FERTILISED EGG OF THE MOTHER IN HER WOMB.  So on Earth, Demons are human beings.  On Earth, Angels are human beings.  Now you can say, "whatever characteristic you exhibit about any human being, whatever behaviour you exhibit of a human being, I can easily remove Demon/Angel and recover the behaviour".  That is WRONG.  You cannot.  You cannot actually explain Demon or Angel Character by any DNA-centric hooky-dooky.  You can feel glib as a modern man and think that it's just a matter of time before you will understand how DNA contained the behaviour, but you will be lying to yourself.  There is more to Human Character than things encoded in the DNA, and Demon and Angel are some of the things.  Now you can say, "Ah Zulf is just playing with semantics.  He is just characterising some behaviours, imagined or observed and calling it Demon rather than much more precise and scientific Psychopathic BlahBlah DubbaDubba Jargon Jargon".  No.  When I say that man -- in my case Bill Gates is a Demon I don't mean he is a species of Psychopaths with such and such disease.  I mean he is a Demon.  He's an Evil Demon with all manner of pretensions to be a Philanthropic Successful Billionaire etc.  He's just a Deceptive Evil Demon.  That is not an interpretation; it is who was before his birth and what he will remain long after his Death.  Demons are Demons.  They don't have a change of heart and become something else.  He was a demon for billions of years before his birth as Bill Gates, whether he himself knows his history or not, and will be a Demon for billions of years after his death.  The DNA does not actually care about this.  On Earth DNA will reproduce Angelics.

\section{Demon or Angel is Parsimonious for some people}

In the case of Bill Gates, his benevolent presentation for decades was a conscious choice to deceive people.  It turns out that he considers all of the public presentation "PR", i.e., deliberate deception.  In reality he considers Natural Rights "claptrap" even though 80 percent of human beings believe in them, and he considers me 'quarry' even though I am American of Bengali origin and is using his power to harm my physical body with using Industrial meta and military meta and other hard meta in my eyes claiming "White Right" and damages my physical brain with tremendous amount of Evil meta, and clogs up my mind even though my work is good enough for a tenure at Harvard. This level of malevolence while public posture of benevolence for example is the sort of thing that "Demon" explains infinitely better than attempting to employ other explanations.  His wealth and success for example does not explain it.  Other wealthy people are not as malevolent.

\end{document}