\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Response to Bill Gates' "White Control is What Makes the World Go Round"}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{I Am Not Offended}

I just heard Bill Gates tell me in meta "White Control is What Makes the World Go Round".  I am not offended.  If that is what he believes, I am glad he is sharing his view with me.

\section{It's Not Actually True}

My response to Bill Gates is that his view, while it might seem quite clear and obvious to him, happens not to be true.

You see, Bill Gates was born in 1955, and he is what, 66 years old.  Now if you look at for example the history of lynching of black people in America, you see it dying around 1942.  Then America entered the Second World War which Russia did most of the dying and actual fighting on the ground in Europe but we love to take credit for the victory.  I remember Gore Vidal's beautiful essay "American Empire" about how for a short period after Hiroshima and Nagasaki ended American Empire was Globally Supreme.  And so it is not surprising that just after the great victory of all hemispheres and before the Cold War really took off, America was the Global Power without peer, and that's the point when young Bill Gates was born, just as we had a third of the world's gold and total control of all the Oceans and Continent, briefly, then we rushed to contain Russia and protect our money.  I say "we" here even though I only arrived as an immigrant in 1987.  I happen to know these things extremely well because I spent a great deal of my life studying them.  I am also Finance, so I know Bretton Woods 1944 and the establishment of the postwar global financial order, the United States came out of Franklin Roosevelt's State Department.  And America is still 60 percent white, so most executives in American Corporations are White.  Bill Gates' opinions are from a nostalgic idea from someone who is not actually extremely serious scholar of these things.  He has a feeling and a conviction, that White Control is what is making thing work because he spent much of his life {\em during the Cold War} where no one mattered and things were about ideological conflict that we would win because London and New York were the money centers and not Moscow.  I was born in 1973.  In 1973, America was losing the Vietnam War already, and I was too young to follow the news, and I was influenced by Michael Jackson and English Literature well before my arrival to New York.  Now I was also steeped in Indian History, and so I have intimate knowledge of English colonialism in India as well.  And right now global growth is carried by Asia, not Europe and America.  So I understand what he is saying, in a sense, from his life, but that's not {\em my} life.  All the countries in East were decolonised after 1945, and I could be offended by his glib view, for the last thing I want is to be an American and compromise the struggles of my grandparents against British Rule and accept such nonsense.  But I am not Indian.  I am Asian-American, and "White Control" is not what has run the world for the entirety of rise of Asian GDP.  Nor is "White Control" acceptable in Corporate America; 40 percent of CEOs are minorities in technology.  Bill Gates' subjective views I would consider reasonable if he were my friend.  He is not. He is one of the most harmful people to my life that I have ever come across.  So I will apologise and tell him that he ought to write about his opinions; these are not mine and I will never accept what is clearly false.  My entire life was post-colonial, and China and India and many other countries have done much better after de-colonisation.  We do not need Bill Gates, who is literally an idiot who thinks Hammurabi was white, to control us.  And that is a good thing.

\end{document}



