\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Rights I Claim Against Bill Gates}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Rights I Claim Against Bill Gates}

I am an Eastern Noble with a 3000 year bloodline.  I am not from a wealthy family but adequate in some ways.  My grandparents were wealthier than my parents.  Now I moved to America and made America my home from 1987, more than three decades ago, while I was barely a teen.  I am a good man and have never seriously broken any law at all.  I accepted America along with its fundamental sacred core, the Universal Natural Rights at an early age and believe in them.  I grew up in New York and ended up being happiest in San Francisco where I wish to reside.

I expect people in America to abide by ordinary American norms, which includes respect and tolerance for other people and professional courtesy and following norms of various industries.  Bill Gates is an outlier in his behaviour and I do not care about his success and wealth.

\section{Bill Gates did things that provoked new Rights for me}

Ordinarily, I do not claim rights to harm anyone at all.  Now in the East, as an Eastern Noble, there are rights to retaliation for Nobles that are accepted, but I am in America as an American now, so I have to think through things.

Bill Gates destroyed my interior claiming 'White Rights' that neither I nor the United State Government accepts.  He had no such right.  But by harming me in such an egregious way, he has given {\em me} certain rights.

\section{My Claimed Rights}

I claim the right to destroy Bill Gates completely by any method that does not violate United States Law.  I claim the right to expose Bill Gates as a total hoax in his public presentation to any and all people of the world.  I claim the right to expose Bill Gates as a pure Evil Demon Soul in human body who has been deceiving all people by pathological lies, a thief, robber, murderer by meta of many people in the past four decades.  I claim the right to evicerate, destroy and annihilate Bill Gates, have the United States confiscate all his property and shut down all his businesses, review all claims that he has about all achievements, execute him for violation of my Natural Rights, downgrade all his achievements, and extinguish his legacy completely.  

These are rights that I did not claim against anyone else but do against Bill Gates because he is a vile dangerous criminal who is a threat to my Beloved People the Human Race.  He cannot be allowed to live on Earth at all, and all his legacy ought to be cleansed of all falsehoods, lies, and other things he has used to amass a fortune by illegitimate means.  He must be killed and shamed and dishonoured and his legacy must be extinguished.

\section{These Rights are Right of Retaliation}

I am not impressed by ethnic hocus that he spews.  All his White Supremacist claptrap I will eviscerate as well.


\end{document}