\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Zulf Honours Scandinavians for Tapping into Trust in Human Nature}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\section{Acknowledgement to Sine Jensen}
Sine Jensen was my lover from 1999-2002 and I was quite astounded at her level of trust, and I was not a student of psychology in those years, and I was happy with her, and was heartbroken when she went back to Denmark.  But over the years I was curious about why she seemed so more trusting than any other woman I had been interested in.  The answer is now clear that trusting improves happiness for all human beings.  Now of all the peoples of the world, credit should be given to Scandinavian peoples for actually discovering something about Human Nature that others did not as clearly.

\section{Ranking of Trust and Happiness}

Let us look at the highest levels of trust, measured by percentage of population that think all people can be trusted and happiness.

% latex table generated in R 3.6.3 by xtable 1.8-4 package
% Fri Apr  9 00:02:37 2021
\begin{table}[ht]
\centering
\begin{tabular}{rlrr}
  \hline
 & Country & trustMost & Happy \\ 
  \hline
1 & Denmark &  74 & 90.10 \\ 
  2 & Norway &  72 & 94.10 \\ 
  3 & Finland &  68 & 88.90 \\ 
  4 & China &  64 & 88.90 \\ 
  5 & Sweden &  63 & 93.80 \\ 
  6 & Iceland &  62 & 95.20 \\ 
  7 & Netherlands &  59 & 91.60 \\ 
  8 & Switzerland &  57 & 93.00 \\ 
   \hline
\end{tabular}
\end{table}

\section{Recommendation to all countries}

It does not require extra wealth or technology to trust more people.  I recommend all nations, especially Developing nations foster trust of all people for improvement of happiness.  Scandinavians are not happy because they are of any particular ethnicity or because they are rich.  They are happy because their cultures had understood implicitly that well-being improves with trust and cultivated this.  Happiness can improve around the world with improved ability to trust all people.

\end{document}
