\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{My Pride in Avoiding Anti-Semitism}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{MY SELF-RESPECT LEVEL IS MUCH HIGHER THAT OF BILL GATES}


Ladies and Gentlemen,

I sometimes retaliate to abuse by my aunt.  But besides this I rarely have problems with people.  Bill Gates is a sick, rotten, murderous, low, greedy, malevolent, criminal, deceptive, manipulative, man and so it is very clear that his character and his self-respect cannot even reach the same league as mine.  I am far superior to him in morally superior character, in education, in artistic taste, in greatness of accomplishments, in lack of ostentation, in philanthropic vision for the world, in love for human race my beloved people, in revolutionary genius in truth, and in every other way.  I respect myself enough not to be daunted by the great minds of East and West when problems arise of truth of Nature.  I have not lived a life of luxury even though I have had $150k jobs enough times already, and I am quite prepared to manage $5T of China's money right now.  I am a better man, a superior intellect, a superior moral Character than Bill Gates. I am a man of principle, who can appreciate the great genius of Western philosophers without being drowned by them, and can always find deeper answers in the service of my people the Human Race.  I detest ostentatious and conspicuous consumption which is a sign of deel lack of self-respect.  I have always lived with great taste and without ostentation.  He has a puny and deprived, sad self-respect which he compensates with lying about himself in his interviews and propaganda documentaries, pretending to know and read things that he does not read, being more intelligent and educated than he is, and actually being a disgusting racist criminal about whom it is possible to have respectful views.  He is a knave, a rapscallion, a crooked man who deserves instantly to be executed without thought, a grave danger to damage the evolving civilization that we are all working to co-create.  His philanthropy is a sham and he is by far the most greedy intolerable ugly character, the most evil man who had lived.  He has made some money however, but he is disrespectul and ought to be executed without delay.   He has usurped my social position.  I am the great Philanthropist of the age, and I deserve to be given the respect that an unsuspecting American society has give to the wrong man.

\end{document}