\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Zulf's Attitudes Towards Totally Wiping Out All Race-Oriented People From Earth}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Strongly Advocate Wiping Bill Gates From Earth}

I strongly advocate wiping out Bill Gates from Earth because he harmed me and violated my Natural Rights.  Here I have 100\% conviction that Human Race is better off if Bill Gates is even killed by massive nuclear detonation.  It would be right, just, and good, and those who do it are on the right because no one deserves to be wiped out more than Bill Gates.  I have no doubts or moral qualms about this.  The future of Human Race and America is just better if this were to occur.

\section{More Difficulties in Generalisation}

In the case of wiping out Bill Gates who is White Supremacist, I have no hesitations, doubt, no qualms about right and wrong.  It's just good, right, just, and so on to wipe him out from the face of the planet.  It's no loss at all for us.  Now suppose we attempt to use {\em induction} and ask:  "Is it therefore good, right, and just to wipe out {\em all} race-oriented people on Earth?"  Here matters are a bit more difficult.  Should race-orientation strip people of their Natural Rights?  I would say that from the point of view of justice, we ought to keep them around with the hope that they could be educated in the future.

\section{Hypothetical Conjecture}

Now I don't actually think that the future of Human Race would be particularly bad if all race-oriented people on Earth were actually just wiped out from the face of the Earth without a trace.  At the moment, I am reluctant to be involved in any actual project to do this, and consider this an interesting issue to consider.  This is because there are race-oriented people of all ethnicities on Earth, and they cause strife for the Human Race, and it is a worthwhile thing to ask if the world would be a better for everyone from all ethnicities if we just wiped all race-oriented people altogether or whether it is worth the effort to keep them around and deal with all the problems that they create for the rest of Human Race.


\end{document}