\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Classical Liberal Guarantee of Right of Single Man to Respond to Any Woman Who Shows Sexual Interest}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

I am single right now, so I am extremely aware of the Classical Liberal freedoms and restrictions.  You see given any two people on Earth, Classical Liberalism is concerned with both of their Natural Rights.  I do not have the right to invade their sexual organ without consent; that is a violation of their sacred Natural Rights, ok?  This exaggeration is necessary so idiots can understand.  Women have their right to avoid invasion of their body by male sexual ardour.  That is rape.  That was known as a crime even in Pleistocene Era and in Mesopotamian Empire and before.  On the other hand, I do have a right to engage with any Woman without criminal violations and determine interest and if the woman is willing to have sexual encounter with me, Classical Liberalism guarantees my right to pursue this.  In Classical Liberalism, all issues boil down to those things are permitted that do not violate Natural Rights of the women or of myself.  

No woman has any right to get jealous and upset that I was lusting after someone else and kill me in vengeance.  Classical Liberalism would secure my Natural Rights against her jealousy and her vengeance.

\section{This is One of the Deepest Issues in Science}

You see Human Beings are Natural phenomena.  What people actually do is part of Natural events in the universe.  However, {\em understanding these} and {\em regulating them} is a matter of Science.  

Classical Liberalism is a theory, partly scientific.  That theory underlies United States Law and, say, the morality of Jefferson Bible.  Now what human men and women do are Natural Phenomena.  When theory matches Natural Phenomena, we have a harmony between events and our mental understanding.  When there is an incoherence between Natural Phenomena and our theories about them, we can expect there to be a million problems.  These problems might not show themselves in the short term.  But in the long term we will have serious failures of human societies and Civilisations.

These are not trivial matters.  "Trivia" can be identified with the sort of thing Bill Gates has done all his life.  These are serious issues of Science, of our clear theories of how the world is and how the world is actually.

\end{document}
