\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Irrelevance of Money in My Status Rivalry with Bill Gates}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{My Finance Background}
I have a great Finance background and understand the laws of capital markets much better than Bill Gates, who uses phrases like "looking at volume curves " and "it's a zero-sum thing" to describe securities trading, which is tantamount to extreme disrespect for the difficult aspects of financial markets and dealing with uncertainty.  I worked at Lehman Fixed Income Derivative Research in Andrew Morton's Group of Heath-Jarrow-Morton model fame, and Kaushik Amin for my first job out of Princeton.  And I also have some work of high genius in the past decade in Finance.

\section{What I can do to be Richer Than Bill Gates in Five Years}

I can ask China to borrow \$5T from capital markets and let me be the fund manager for a Global Individual Debt play to reduce Credit Spread for all individual debt in the world.  The fee alone for management will make me richer than Bill Gates in a decade.

\section{Theoretically Money Is not an Issue for Status Rivalry}

Since I do have the professional experience and skills to execute a fund management job in San Francisco that will without any doubt make me richer than Bill Gates, we can safely conclude that for Social Status in American Society, Money is not an issue.  I can be richer than Bill Gates in theory quite quickly if China does agree to Global Individual Debt.

\section{Bill Gates Actual Character}
Bill Gates happens to be a totally criminal cat who is white supremacist and has various Racial Order plans and violates my Natural Rights by damaging my Body Meta using US War meta and then cutting my eyes even though I am an independent entrepreneur and not his employee, and claiming my company Thyself Inc. is his own even though I had registered it, claiming my ideas are his own even when I have paper trail on priority and so on.  So he happens to be a rotten Character without any integrity or Honour who has a glowing saintly PR with many documentaries extolling his goodness and industry and talent.

From his point of view the key factors for high social status in American Society are (a) whiteness, (b) money.

\section{What Factors I think Matter For Social Status in American Society}

I am taking the bet that Bill Gates view is in error and neither (a) whiteness nor (b) money matter for high social status in American Society.

Instead I will take the classical view that what matters are (a) Virtues and (b) Character Strengths.  In particular my Morality is much higher naturally than Bill Gates and Honesty and Integrity is my Character Strength.  I am also vastly better studied in issues of Western Culture and Civilization than him.  This is for me not frill but integrated into my Soul.  I am much weaker in Power than him at the moment and that could decide things against me.

\end{document}