\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf is Far More Successful in Life than Bill Gates}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{My Achievements in Life Far Exceed the Reach of Bill Gates}

First of all, I graduated magna cum laude from Princeton University in Mathematics.  That alone is far greater success than Bill Gates had ever accomplished.  He was unable to graduate from university at all.

Second, I took apart three centuries of macroscopic physics, literally abolished the most established theories of the entire twentieth century--Relativity, Schroedinger Quantum Mechanics, Expansionary Cosmology and Big Bang in a series of papers in a decade's amount of work.  I did this without institutional support living with my aunt in Allen Texas with disability earning.  This is immortal genius work and Bill Gates has nothing comparable in genius. 

The totality of my scientific ouvre include one of the best stochastic volatility option pricing model that is competitive in accuracy to the best in the world, a Medium Frequency Pure Arbitrage Alpha strategy for which I am owed \$120 million from D. E. Shaw \& Co. that Bill Gates blockaded out of racial order plans despite it being work I had done for years alone and succeeded it.  Obviously I will mark \$120 million as my money.

Then the work I have done in Personality Psychology (discovery of thousands of personality types in data); the work in Human Nature, where I have produced a quantitative theory of human morals across the entire human race with 91\% explanatory power.

Then introduction of infinitely divisible distribution fits to actual World Values Survey data which will lead to great success in Social Science.  

My scientific genius is immortal, in the scale of Newton or Maxwell or Schroedinger or Darwin.

Bill Gates, on the other hand, was deceptive about his true nature and is malevolent in people's eyes and has made money by power tricks and harming people and stealing rather than by legitimate business.  

My ex-wife left me at 26; his wife is leaving him at 66.

\section{Conclusion}

There is no question in my mind that I am a thousand times more successful than Bill Gates, despite me living at 48 with my aunt after half-a-year of hobo in New York in 2008.

\end{document}