\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{So You Want to be Superior to Some Bloke Huh?} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Things that Will Fail}

We all want to be superior to that other guy, whoever it might be.  In my case it's Bill Gates.  In yours it might be George Mucha Cara, the insufferable man that I have never met but my condolences to you because I probably wouldn't like George either.

First things first, avoid taking group-superiority approaches.  They usually fail.  I have done this in the past with limited success.  I have said, "Well I am Princetonian, and it's lonely at the top."  Now this works in Princeton campus because those t-shirts and woolen clothesware are cool, but in fact this approach does not work either.  Certainly you will not have much success with tribal superiority.  The days are far gone when your Amorite tribe goes around enslaving all the Hittites and so on.  That's why we consider those sorts of thing Old Testament.  This refers to the Testament being too stale.  And besides, if you are anything like me, your skills with the sword and spear and all sorts of slicing up people from nave to chops and holding all sorts of daggers before you have not led to many actual people dead.  These are old school and they work sometimes but more often than not you will be sitting there explaining to FBI for a long long time that these things are not 'hate group' and explaining how you were talking to some hot German girl on Facebook but were not actually aware that she was involved in some secret ring to declare some dodo Fuhrer and had all sorts of odd salutes and watched too many of those Leni Riefenstahl propaganda films instead of finding something that is more meaningful and serious for the future today.  I won't go into the whole history of how Zulf met Talia and got in more hot soup with FBI than I could even contemplate and how Talia was too rich for Zulf and was screwing around with every husband who could be cuckolded and so on.  Those are private issues.

The important issue is that don't do tribal.  It's a losing strategy.  Just as you get your libido channeled for taking down the other tribe you find out that more than three quarters of your tribe are no good and then you're stuck.  Your tribe is going to weigh you down and you'll be doing service to try to get your tribe back in gear and you'll be outraged at how unburdened with every 80 IQ fuck in your tribe these other guys are just cruising along to new heights.  So do not do ethnic.  Stick to careful drawing of boundaries, ok?

\section{Pay Attention to Your Virtues and Conscience}

The first step to being a superior man is to pay extraordinary attention to your own Conscience and have stock of your Virtues.  Virtues require habituation, so don't skimp doing just things and thinking through how you can contribute to improve the Human Condition and so on.  

\section{Basic Dos and Don'ts}

Don't be stupid and throw in your weight behind backward tribal elements; take a Human Race perspective.  Do pay attention to your Conscience, and focus on things that you have Character strengths.

Do treat people with respect even if they are rich or poor or of all ethnicities.  This is a sign of great inner nobility and you will find that reciprocity is the name of the game and people will respect you if you respect them.  Don't harm people you don't know for all sorts of political programmes.  Those sorts of programmes will derail you from your inner greatness.  
 

\end{document}