\documentclass{amsart}
\usepackage{amsthm}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{United States Senate Rules Need Thorough Examination For Constitutionality Pronto} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\newtheorem{proposition}
\maketitle

\section{Months Have Passed Since US Senate Has not Apprehended and Put Bill Gates to Death}

Bill Gates has been violating my Natural Rights for six months using Racial Tricks of White Supremacists in horrible destructive ways and US Senate has been using "Senate Rules" as an excuse not to seize his property and put the Vile Malevolent White Supremacist little Cunt to Death.

This obviously implies that US Senate is not doing its job, which according to US Declaration, is to {\em secure Natural Rights} of Americans including mine.

What is necessary is a thorough review of Senate Rules for Constitutionality (which includes Consistency with Declaration).  

Obviously Senate Rules are wrong versus Founder's vision and US Supreme Court is obligated to correct problems.

\section{My Letter to US Supreme Court}

OPEN LETTER TO THE US SUPREME COURT
Inbox

zulfikar.ahmed@gmail.com <zulfikar.ahmed@gmail.com>
2:03 PM (21 minutes ago)

US Supreme Court,

I do not find it acceptable as an American that Bill Gates is able to brutally harm my Natural Rights and US Senate claims that their 'rules' prevent them from confiscating the assets of this Evil Malevolent White Supremacist Criminal and secure my Natural Rights.  Could you please intervene into the business of US Senate and throw out all the rules getting between US Declaration and US Senate's SORDID DEPLORABLE performance here and declare every single rule UNCONSTITUTIONAL.  

Thank you,
ZULFIKAR MOINUDDIN AHMED

\section{US Senate is Completely Confused About Its Job}

US Senate constantly gets distracted by issues of US Economy, in which its role is minimal and its expertise even more minimal.  These are distractions from US Senate's primary duty, to secure Natural Rights of Americans.  Senate Rules might all have to be thrown out, since the incompetence of US Senate in securing my Natural Rights is outrageous.

\end{document}
