\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf On Inner Strength To Deal With The Evil Of the World} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

I have been dealing with malevolent Evil for the past year.  Bill Gates is an exceedingly malevolent and Evil force who has been on a mission to destroy and kill me.  And I want to share with the world how I have survived, and how I can dismiss his wealth and power and retain my optimism for the future rather than contemplating suicide, which has been the fate of many of his earlier victims.

First of all, let there be no mistake that I consider myself far superior as a man than Bill Gates, despite my having much less success and wealth compared to him.  I also have legitimately earned \$120 million with my Finance work that I am trying to collect from D. E. Shaw \& Co.  So that should put things in context.  My Finance is world class, and that is why I legitimately earned \$120 million from D. E. Shaw \& Co.  What Bill Gates has been doing is denigrating my work, calling it 'trivia' and forbidding D. E. Shaw \& Co. from paying me my legitimate earnings. 

I would say one of the things that helped me survive is being on the right side and understanding that as an American, I can stand on United States Declaration of Independence to continuously demand that the US Senate must either relentlessly bomb and obliterate Bill Gates or be held guilty of Treason and be executed by a firing squad.




\end{document}