\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Thoughts about Working Mother and Rape Rate relationship}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\epigraph{Hey woman, whose to blame

For the birth of a race

That was born too late?

Last chance to Paradise

Open your eyes

Last chance to Paradise

Open open}{Frances Ashman, "Pandorra"}

\section{Fundamental Truth}
The fundamental truth that I propose all people accept are that (a) Human Race is a Single Race, and (b) Human Nature is not rape.  By this I mean a hard acceptance that we are a single race across the globe, biologically, with shared actual ancestors in East Africa 75,000 years ago for non-Africans.  Second, from the inference that rape rates across the world are uniformly lower than 0.06 percent, which implies that 99.94 percent of men everywhere on Earth do not commit any rapes at all we make the strong inference than rapes are not human nature at all.  In particular there are no such things as genetic predisposition to rape anywhere on Earth.  Our genetic material is evolved not to have rape in it, and that is the reason there is at most 0.06 percent rape rate per year across the globe.  

\section{We Must Expunge Ethnic Theories of Rape}

My result that whites in America overrepresent rapes by 16.33\% is simply a corrective against the false claims made against hispanics and blacks.  My result refutes popular false delusions.  Whites rather than ethnic minorities in America overrepresent rapes.  

In fact the real variables explaining rapes are not ethnic.  I do not want new bogus 'whites are lecherous rapists' propaganda arise as a vengeance against "The Clansman" or "The Birth of a Nation" and its horrible anti-black propaganda.  The right answer is Rapes are not Human Nature.

\section{Driving Variable is Romantic Love and its capacity}

My scientific outlook for a universal factor for Human Race is that Romantic Love is central to our Race, our Species, is more ancient than even our emergence as Homo Sapiens and therefore fundamental and necessary for our propagation.  Rapes arise from failures that produce individuals badly damaged and incapable and incompetent for Romantic Love. 

\section{Secure Attachment and Habituation of Virtues are preparation for Romantic Love}

Working mothers produce insecure attachments by neglect, and combined with lack of habituation of moral Virtues, usually a feature of paternal contribution, society produces a pool of men with low social competence, inadequate Virtues, and all rapists are from these men.  Obviously not all such badly served men are rapists but they are damaged.  

The fault here is not the mother's but in the exceeding importance given to industry and demands for work rather than the view that Motherhood is of fundamental value to society, much more than profit and corporations.  Every mother on Earth is literally far more valuable than Bill Gates.


When mothers need to work neglecting children who have insecure attachment, a large number of natural processes are underdeveloped leading to minor and severe problems for the children throughout their lives.  Various political philosophies both in left and right and the general respect for profits and career over these fundamental aspect in West and East conspire to produce conditions where mothers are pushed to botch the raising of healthy children, and the result are measurable vast rape rate increases across the world.


\end{document}



