\documentclass{amsart} 
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Thoughts about Eugenics}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}

\begin{document}
\maketitle

\section{Issues of IQ}

IQ is not a great measure of intelligence in many ways.  Intelligence is a complex topic, and summary of one number is at best a rough indicator of some cognitive facility.  My IQ is around 135-140.  This is not particularly important to me personally.  I have my own ideas about intelligence.  But let us assume that you think IQ is a worthwhile measure.  My SAT score during high school was 1450, in two trials.  I can probably could have gotten higher but I did not care.  So my SAT score and IQ are compatible.  

IQ is adequately described by Gaussian normal distributions.  The white American IQ distribution in N( mu=100, sigma=15).  I can make the inference that I am in the 99.6th percentile of American white IQ.  This may seem odd to some people but I went to Princeton and many people had IQ that are close to and higher than mine so the population statistics does not represent people who graduated magna cum laude from Ivy League and other top universities.  Now let's look at World IQ means (remember the sd=15 is pretty wide for white IQ so you should not even worry about whites being more or less intelligent on average if it is within (100-15, 100+15).  This is the first inference error people make.  There are literally millions of white Americans with higher IQ than mine, but they are 0.4% of the population.  Let's see some of the IQ means around the world next with the specific elementary statistical intuition that if they are not more than 2*sd of white mean IQ then we cannot actually produce strong conclusion that they differ at all from white IQ significantly.

https://worldpopulationreview.com/country-rankings/average-iq-by-country.  Top 10 IQ countries:

Hong Kong (108)
Singapore (108)
South Korea (106)
China (105)
Japan (105)
Taiwan (104)
Italy (102)
Switzerland (101)
Mongolia (101)
Iceland (101)
None of these means are about 130 IQ, so they are not significantly different from American white mean IQ.  I won't go too much into this issue.  I do not believe that Africans are actually less intelligent than white Americans.  But that is a separate conflict.  You cannot really define the world in terms of IQ any way.


Now there are a number of African countries with IQ mean around 70, which is lower than American white IQ by our criteria.  

Bill Gates IQ is not 160 or whatever is the propaganda.  He is bright in a way, but he is prone to lying a lot.

\section{Thoughts About Eugenics}

Eugenics by IQ is an atrocious idea.  IQ is a very poor measure and is not compelling to me as a full measure of intelligence.  I don't like the idea of eugenics by IQ.

Nietzsche says, "The root of all true culture is the longing of man to be reborn as a genius and a saint; where we find talent devoid of that longing we are repelled and disgusted by it, for we feel that all their great intellect they do not promote an evolving culture and a procreation of genius but hinder it."  Nietzche was not such a will-to-power man at all but rather someone who believed that love is the source of all great insights and genius.

First, looking at IQ is the wrong place to find true genius.  Second, if we are going to do eugenics we ought to follow long tradition of millions of years where murderers have been put to death and simply do eugenics of Character rather than IQ anyway.  I feel there is nothing more dull than taking a dull measure of intelligence and then doing dull eugenic thinking on that dull measure.

\end{document}
