\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Tolerance and Respect by Ethnic Groups Across the Globe}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Aggregate Stats}

Proportion of populations that think teaching children respect and tolerance is important across the world.
% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Fri Apr 30 22:52:17 2021
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 & eth & tolerance \\ 
  \hline
1 & White & 0.63 \\ 
  2 & Black & 0.67 \\ 
  3 & South Asian & 0.69 \\ 
  4 & East Asian & 0.58 \\ 
  5 & Arab & 0.82 \\ 
  6 & Other & 0.58 \\ 
   \hline
\end{tabular}
\end{table}
This is most interesting.  Tolerance levels are all quite high, with whites at $0.63$ which is close to blacks and south asians, but highest tolerance is for Arabs $0.82$, and lowest for East Asians $0.58$.  This is interesting and for me at least, quite enlightening and I did not know at all.

Now mean is $\mu=0.66$ and $\mu-\sigma=0.57$ and all the data fall within this bound.  There is no statistical significance for any deviation at the bottom end; i.e. whites are {\em not more intolerant than anyone else}. 

\section{Total End to White Supremacist Programs}

The observation that whites are not more intolerant than anyone else has the consequence that no White Supremacist World Order can actually be stable.  For a White Supremacist World Order, Whites would need to be much more intolerant than they are.

\section{My letter from February 3 2021}

I was looking at my arguments to snafu White Supremacy in America noting the happiness effects of hate speech, noting the PHASE TRANSITION in unhappiest people when the Positive and Negative Affect changes from P>=N to P<N, and we go from 5.4% and 6.9% to 23.2% of the people landing in the unhappiest category, we can begin to see that a divided nation where everyone is hating everyone else is going to spiral the happiness level of individuals (by biological machinery) down into the lowest happiness levels.  

This is a time for me to sing the praises of Love and Acceptance.  We are all Americans here, regardless of race and political stripe and we must stop harming ourselves with all the NEGATIVE AFFECT.  We are still one of the wealthiest nations in the world.  We cannot now destroy our own health by upping Negative Affect in our lives.  Negative Affect is not automatic.  Stop the hate, for your own sake.  Let us return to TOLERANCE.  The Nation must unite and resolve all our problems together.  Nothing good is going to come from all sorts of Supremacism and strife.  Nothing will come from hatred.  Embrace your fellow Americans and embrace the Human Race.  We are all in this together.  

Fine, the numbers are from NORMAN BRADBURN'S book from 1969 but might as well make great and uplifting speech like Martin Luther King, Jr.  

\section{Conclusion}

In order to lower white intolerance, Bill Gates would need them to embrace hate speech, and that will produce phase transition to a very high level of unhappiness among whites around the world, and that will make short work of his White Supremacist World Order, inevitably.  Then people will burn Bill Gates at the stake and return to normal world order.
\end{document}