\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{On the Expected Tragic Fall of Bill Gates} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Elements of Tragic Flaw}

The Ancient Greek Tragedians, Sophocles, Aeschylus, Euripedes has profound wisdom regarding nature of human affairs, and I am quite sure that Aristotle's Poetics did not have a full picture.  I have discovered elements of many interesting {\em tragic flaws} in Bill Gates persona and character.  He is a virtual {\em symphony of seven deadly sins} from the Christian perspective.  

But unfortunately I have not been successful in seeing clearly the trajectory of his Tragic Fall and dissolution into Nothingness just yet.  My understanding of how things are is simply not good enough yet.  It is true that I have proclaimed that I, Tiresias, who had sat beneath the walls of New York and walked amongst the lowest of the dead had profound insight, that I throbbing between two lives with wrinkled female breasts had foreseen various scenes and foretold various other things.  However, this bluster of the Apollonian prophetic mode was not sufficient to see clearly the particular trajectory of the Tragic Fall of Bill Gates, who is a Hollow Man, all of whose self-promotion propaganda are totally false and the Bill Gates of public mind simply does not exist, so that when he dies, he will simply vanish from history as no one knows how he actually is.  From my perspective, he was a Demon for many centuries before his birth on Earth, with Chaotic Evil governing his psyche and actions.  He is the most deceptive of all people alive. 

\section{Fate Cannot be Predicted Easily}

I cannot predict the particular pathways that Bill Gates' Tragic Fall will reveal itself, but I am quite excited to find out.



\end{document}