\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Who is a Traitor and Trojan Horse Within United States Government?}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Executive Summary}
I will argue in this note that anyone in the United States Government is a {\em traitor} and a {\em trojan horse}, a virus, if they do not fully grasp the purpose of each unit of United States Federal Government.  That fundamental purpose is to secure Natural Rights, unalienable rights endowed by the Creator that every person is born with in America.  

\section{Source of Authority}

I will ask my readers to accept that the United States of America is a Multi-Ethnic Classical Liberal Democratic Republic.  Then I will invoke exact careful wording of the US Declaration of Independence as an authoritative document that enshrines the American view of politics.  In particular I will show you that the Founders did not leave the {\em purpose of government} to chance and had precise and unambiguous answer for this issue.

\section{The Preamble of Declaration}

I take the text from \cite{WikiDec}

"We hold these truths to be self-evident, that all men are created equal, that they are endowed by their Creator with certain unalienable Rights, that among these are Life, Liberty and the pursuit of Happiness.—That to secure these rights, Governments are instituted among Men, deriving their just powers from the consent of the governed,—That whenever any Form of Government becomes destructive of these ends, it is the Right of the People to alter or to abolish it, and to institute new Government, laying its foundation on such principles and organizing its powers in such form, as to them shall seem most likely to effect their Safety and Happiness. Prudence, indeed, will dictate that Governments long established should not be changed for light and transient causes; and accordingly all experience hath shewn, that mankind are more disposed to suffer, while evils are sufferable, than to right themselves by abolishing the forms to which they are accustomed. But when a long train of abuses and usurpations, pursuing invariably the same Object evinces a design to reduce them under absolute Despotism, it is their right, it is their duty, to throw off such Government, and to provide new Guards for their future security."

\section{Focus Attention on Key Purpose Part}

"...they are endowed by their Creator with certain unalienable Rights, that among these are Life, Liberty and the pursuit of Happiness.—That to secure these rights, Governments are instituted among Men, deriving their just powers ..."

\section{No Ambiguity Here}

The above quote leaves absolutely no doubts about the purpose of existence of government in the American view even in principle.  We, Americans, believe that governments are formed "to secure these rights".  I like to be very clear here.  All people in America are included included immigrants with Permanent Residency who are not US Citizens yet.  Why?  Because the process of contract of USCIS immigration papers includes an embedded implicit contract that the United States will secure my Natural Rights as a future citizen. Regardless, it is the purpose of existence of the United States Government to secure Natural Rights of Americans, and not an optional {\em service} that is secondary.  For example, to make this clearer, the purpose of our government could have been to produce an ordered society, and then Natural Rights security would be a convenience that results from good policing.  That is not what is the foundation of American vision of government.  We believe that securing Natural Rights of Americans is the {\em fundamental purpose of government at all}.  In other words, we do not believe that Natural Rights security is a convenience or a secondary priority to, say, commercial success of United States Industry, or indeed of {\em any other issue}.  

American view of purpose of government is that it ought to exist 'to secure these rights' for all Americans, and ought to be abolished are reformed when the government is unable to fulfill {\em this purpose above all}.

\section{Inference: American Government Employees Who Dismiss Natural Rights of Americans Are Traitors}

American Government exists to secure Natural Rights of Americans by sacred foundations.  Thus those Employees of US Federal Government, who are paid by the largesse of the trusting American people and whose income is taxed to pay for livelihood of these Employees who dismiss Americans' Natural Rights -- like snakes who bite the hand that feeds them and corrupts American Government with all manner of other things as more important than securing of Natural Rights -- are traitors to the foundations of this Nation, and do not belong in American Government at all.  


\begin{thebibliography}{CCCC}
\bibitem{WikiDec}{\url{https://en.wikipedia.org/wiki/United_States_Declaration_of_Independence}}
\end{thebibliography}

\end{document}