\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Two Sorts of Aristocratic Nobility}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Looking Down and Tolerating}

The two sorts of elitism of nobility are those who look down because of their exclusiveness and those who accept and have tolerance and benevolence toward people.  The former type may have some exclusivity but they hide away from the world, and their snootiness hides an insecurity that the plebian population has ill-will towards them.  The second type of elitism is expansive and accepting.  The former type is much weaker than the latter and for very good rational reasons.  The latter type led to the rise of civilisations; figures like Rama of Ramayana and Buddha are nobles of the latter type and they were fearless in the crowds and welcomed wherever they went.  They were the first kings and emperors in the rise of Civilisations because they commanded naturally the trust of people as benefactors of people.  And indeed I posit that notions of {\em divinity} co-evolved with social status.  The latter type of nobility had the {\em trust} of the vast peoples and also the {\em respect} of the people.  

The former type is defensive, who are attempting to preserve something from danger.  They are not the most influential.  They are secure in a way, but they are not trusted for their very nature; they do not show their hearts and the latter is liberation, to be free and trusted for a great and noble heart is part of Human Nature's natural machinery.  The former have privileges, often wealth, but they are not considered naturally {\em assets} for others, for people, while the latter are valued and trusted in the end because they are assets and have their influence for more than their wealth or other symbols of status.  

The former congregate is secret to declare their specialness; the whole world declare and accept the specialness of the latter and no reinforcement and private ceremonies are required for them in the end.

\end{document}