\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Dick Cheney does a United States Consider of Myself, Bill Gates and Noia Efrat}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\epigraph{You used to be alright

What happened?

Did the cat get your tongue?

Did your strings come undone?

One by one 
One by one
It comes to us all
It's as soft as your pillow}{Radiohead, "Fifteen Steps"}




\section{Dramatic Introduction}
History is written on the sands and shores of the United States of America, and in the Hearts and souls of its men.  Know, then, that it is April 2 2021.  At this time the Earth was ruled by various factions in the United Nations Security Council.  Zulfikar Moinuddin Ahmed had walked up to the second floor of 915 Meadowgate Drive in Allen Texas to sit down to ponder the enterprises of great pith and moment that he was planning.  As Dick Cheney's United States Consider found great devastation in his meta, and there were explosives hidden by Bill Gates and Noia Efrat, it became clear that as United States considers Bill Gates' eyes he will be found to have quite a bit of difference from the United States.  

\section{Bill Gates plot to sabotage Natural Rights in America's Foundations}

Zulf was hurt and obstructed by Bill Gates' atrocious destruction of his Ancestral Meta and many other important things in his personal life and Bill Gates had plotted to sabotage the security of Natural Rights that lay at the Foundation of United States of America.  This would be quite disastrous for his eyes in the end, for the United States cannot tolerate any grave threats to its Foundations.  This will produce some problems for Bill Gates.  His gigantic hubris, of harming Zulf and using his meta to damage the United States will surely be foiled, and White Supremacy will cough and sputter towards its extinction in America.

Now from some people's perspective in the distant future, they might be tempted to congratulate Dick Cheney as well as Zulf Ahmed for the epic moment when an American tycoon whose public relations with all sorts of documentaries and such were quite good overall, but whose hubris was tragic as he sought to challenge Natural Rights from the Foundations of America.  Rather than consult with the US Government Official, he attempted to harm and victimize Zulf Ahmed, and this was truly a monumental blunder.  For Zulf Ahmed was quite a bit better educated than our tycoon Bill Gates and could therefore see clearly that after the United States consider is done, Bill Gates will be quite responsible for his calumny against the eyes of Zulf Ahmed for Natural Rights violations and ultimately his legacy will wash away like castles in the shores.  This is quite a melancholy moment, a solemn moment, and I will celebrate this with a great song by Radiohead, "Reckoner" \cite{RR}, because we separate like ripples on a blank shore.

\begin{verbatim}
"Reckoner"

Reckoner
You can't take it with yer
Dancing for your pleasure

You are not to blame for
Bittersweet dis-tractor
Dare not speak its name
Dedicated to all human beings

Because we separate
Like ripples on a blank shore
In rainbows
Because we separate
Like ripples on a blank shore

Reckoner, take me with yer

Dedicated to all human beings
\end{verbatim}


\section{Dedicated to All Human Beings}
Yes I am quite upset that my life has been devastated and Ancestral meta was very ancient.  But Fate is quite astounding, and as we lose some parts of ourselves in our struggles we find far deeper parts of ourselves and we become closer to our Eternal Selves in the Eternally Recurrent Universes, and our life and song echoes further out into the cosmos where we are well regarded and known for many billions of years like familiar friends.

\section{Dick Cheney Discovers that Bill Gates had severed my dying mother from my heart in meta}

My mother is sick and dying, is a widow from 2002 and lost her daughter, my sister in 2017, and Bill Gates took my work on Medium Frequency Strategy, is making money from it on \$2 billion in investment with D. E. Shaw & Co and they agreed to pay me \$120 million and he intervened to blockade it before.

Since 1955-2021 Bill Gates never had a more important achievement.  His achievements in Microsoft and all other things are trivial by comparison.  {\em This malevolence} is his greatest accomplishment.  

I will of course hold United States of America accountable for \$1 trillion in damages since not only did America fail to secure my Natural Rights, but after they already knew that Bill Gates was criminally violating my Natural Rights they did not arrest and put him away immediately and let it drag on so he committed more and greater atrocities against me.




\begin{thebibliography}{CCC}
\bibitem{RR}{Radiohead, "Reckoner"}
\end{thebibliography}
\end{document}



