\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{My Unorthodox Beliefs about Myself}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Purpose of this note}

I believe Four-Sphere Theory is roughly absolute truth, and not one theory among others in fundamental macroscopic physics.  There is a vast purely electromagnetic fourth spatial dimension with objective existence in the universe.  Truth is what is the case in the universe.  Empiricism is essential as a tool to determine the truth, but there are other ways of obtaining truth.  These other ways are not acceptable to the scientific community, and this is as it should be.  Strong rules for acceptance has allowed empiricist science to flourish.

This note is not a scientific note.  Perhaps it can be called religious in a way.  I was born in Bengal in 1973, and I moved to United States in 1987; I am American.  I was not religious as a young boy and by six was Atheist.  I developed my own faith that is peculiar to myself.  I believe that I was an Angel in the universe for billions of years, and have been born as a human being a number of times in the past.  One life I remember is roughly between 1188-1300 in England.  And then this one from 1973-present.   I have no problems with this belief and all that it implies contradicting many established scientific views.  Four-Sphere Theory has a great deal of space for existence of purely electromagnetic life, and for me an Angel is not a physical being in the ordinary sense but purely electromagnetic.

An electromagnetic being does not have arbitrary methods of being able to be a human being.  I believe I entered the fertilized egg of my mother as a spirit and then simply grew in her womb as a human child.  To be clear, I am completely human being, and do not have any extraordinary abilities so my faith here is about my past before birth and also that I will be an Angel on death.  As a matter of faith, this is not particularly radical compared to things believed by Jews and Christians and Muslims.  But this is in fact what I do believe about myself.  

I can justify my belief about myself in terms of Four-Sphere Theory.  I won't try to prove it at all, because it does not matter in a way.  The universe of propositions that can be proven by empirical methods will be quite exhaustive and so most people will not care about my subjective faith.  They are not interesting scientifically.  

Although not interesting scientifically, they will illuminate something about what gives me a coherent view of all of existence, and since I will be working on scientific problems on Human Nature, they give perspective about what subjective constraints are important to me, as background material.  I like to be explicit about these because my biases are disclosed.  I will not be impressed by various sorts of ethnic tribalist theories of classification of human beings, for example, because my faith leads to a firm conviction that Human Race is a Single Race, even if divided and scattered across Earth. 

I have strong views about Virtue Ethics; I am pleased to see that the Human Race has improved in Virtues almost uniformly across the globe.  I value Virtues in Human Race for they are more Angel-like.


\section{On discrepancy with Angels in Scriptures}

 My morality is imperfect but contained in a sense.  In my 48 years I shoplifted twice or three times.  I certainly remember shoplifting a chocolate bar in one of the supermarkets on Broadway above 110th street in New York when I was a graduate student of Mathematics at Columbia University sometime in 1996 maybe.  Then in 2008 when I had given up all my material possessions and loft in Williamsburg after arguing in a Brooklyn Court for the abolition of all Nation States and foundation of a Great Republic of Humanity, and proceeding to send 13,000 people emails for the project.  I stole a pack of tarot cards there quite fascinated by the deterministic Fate and considering the meanings in the cards.  

I did go through great pangs of guilt later and vowed never to do those things later.  I am proud of my Character Strengths and Virtues where Honesty ranks third after Love and Creativity.  So I am not exactly a man of moral perfection but on the other hand, I am proud of my moral Character and my lack of malevolence towards people generally.  I am known to be overly naive and trusting by my family.  

In case there is a discrepancy between myself and Angels in Scriptures, I reason that since I am an Angel Soul born as human being, that how I am is the right answer for how an Angel ought to be.
 

\end{document}