\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Small Correct Decision by US Defense}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{US Defense Decides Zulf's Request for Security of Natural Rights supercedes Bill Gates' Request}

I just learned that US Defense has decided my request for security of my Natural Rights supercedes that of Bill Gates to use military power to harm me.

Many people know Bill Gates and so one might think this is a great coup by me or some such thing.  It is not.  It is the correct decision by US Defense.  It is a small but correct decision by US Defense.  

\section{Why is it th Correct Decision?}

United States is founded on securing all Americans' Natural Rights, but internal issues are rarely addressed by US Defense.  Now US Defense is a professional outfit and have to worry about Natural Rights all the time because they deal with lethal force.  In fact I am fortunate that US Defense {\em must} be involved for reasons having to do with Bill Gates rather than me.  

Bill Gates had used US War meta against the Body Meta of myself, an American, and later US Defense found Bill to be in possession of military meta that are not authorised for non-military use.  Then they were doing considers for Bill Gates to surrender his military meta which he used against me in my deep interior underneath my blood meta.  This then forced the involvement of US Defense in an internal American matter.

Bill Gates is a businessman, not a military man and did not even serve in Vietnam War.  It is quite unreasonable for US Defense to let him have control of military meta after he had revealed that he planned to have power to kill any non-white person in America at will.  This threatened US Sovereignty.  

I have argued that in matter of intolerance where American norm is $x=4$ mean in $I=[0,10]$ Bill Gates would have literally a value close to $x=52.4$ not out of a joke but because his level of disrespect and intolerance towards others (non-whites he says now) is so high.  

US Defense is not a political organisation but obviously they are concerned that with 40 percent Americans being non-white his plans and desires pose a credible threat to Sovereignty of the United States because only the state has the monopoly of power to kill in America, and this is regulated by the laws of the Republic.  Bill Gates' attempt to usurp powers reserved for the state is a threat to the nation.

On one hand US Defense decision to secure my Natural Right is surprising if one thinks of the prominence of Bill Gates whom everyone knows, and I am relatively unknown.  But it is correct because of the Principles of the Nation.  So this is a small but correct decision.  It shows that US Defense is not completely corrupted by money and industry or ethnicity-centric concerns.  I like to emphasize that this is not 'political correctness'; it is a matter of survival of the state.  Once there is a lapse in principled decision from US Government, it will weaken America and in the end lies dissolution and ruin of bad decisions.


\end{document}