\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{The Most Craven Treacherous United States Senate in American History Does Nothing While American Man's Natural Rights are Desecrated By Evil White Supremacist Cunt} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Introduction}

Ever since the United States Declaration of Independence of 1776, there has never been a time when the entire United States Senate decided that they will let an Evil White Supremacist with Conviction that 'Natural Rights are claptrap' cuts into an American man's eyes and caused total devastation, destroying his Ancestral meta, rotting his teeth, cutting through his blood meta, destroying his interior, and when the American man keeps emailing to American Enterprise Institute seeking the Death Penalty for this heinous Evil White Supremacist who is desecrating his Natural Rights, the United States Senate is literally {\em confused} about what to do.  In the entire time, the US Declaration of Independence was sitting with instructions for the purpose of United States Government to 'secure these rights'.  United States simply decided to not intervene and kill and annihilate the murderous White Supremacist Criminal, to allow him to starve the American man of all livelihood and use US Military and US Industry meta to continue to commit his abominable crimes against the American man.

And still the United States Senate decided to watch as spectators, to be entertained as the desecration of the Sacred Natural Rights that they were sworn to secure.  

Foreign nations, Sweden and Germany, was wondering why United States Senate does not take care of their own.  But that did not change anything.  United States Senate, instead of murdering the Vile White Supremacist Criminal with Racial Slurs as chants, kept on defying all calls and kept violating the Natural Rights of the American Man.

The United States Senate was an amused spectator to the destruction of Natural Rights of an American, quite oblivious to the irony of the situation, that they, the US Senators had been entrusted their jobs and positions and privileges by the unsuspecting American Peopl, to secure Natural Rights, but they instead would rather hog up important seats of United States Government and watch lurid and horrific Criminal Destruction of an American man's Natural Rights instead.

What is their excuse?  If they were to do their jobs, i.e. if they were to intervene and kill the White Supremacist Vile Criminal who was continuing his great crimes, then in the future something bad might happen, something to the Economy maybe, something else could go wrong, such as some of their investments might not go in the right way.

In the entire history of America, never has the United States Senate been not just corrupt and incompetent but positively macabre in their glee in the destruction of this great nation.   This is akin to the Catholic Church psalms being replaced by chants of 'all praise Satan'.  

\section{Zulf is Not Interested in Excuses For Total Incompetence By the United States Senate}

Why is a man who says he does not kowtow to United States Law able to have any property or business at all in the United States?  Why is he still alive after plotting to snuff out Natural Rights of non-white Americans?

Why was Zulf's Natural Rights even remotely damaged?  Why did the Senate not {\em confiscate his property} and {\em kill him} meaning Bill Gates already in the 1970s.  

Why does Zulf have to take off time from his {\em Pursuit of Happiness} without pay and fix United States Senate?  

How is this even possible that a man plotting to snuff out Natural Rights of Americans and who refuses to be subject to United States Law is allowed to have {\em any property} on American Soil, let alone \$130.5 billion worth, and he is able to routinely commit grave crimes?

You should all be taken and shot for Treason and Incompetence for allowing this situation to occur?    What is it that you do all day?

\end{document}