\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Some Thoughts of Virtue Ethics}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{What is Virtue Ethics?}

Virtue Ethics is based on the focus not on particular rules in particular situations, or particular obligations but on particular persons and their moral traits.  I have been promoting Empirical Virtue Ethics as the only manner in which we can have a valid point of view about the entire area of morality in the Human Race.  

\section{A public letter of April 3 2021}

"CUNTS WILL BE CUNTS EH BILL GATES? ONCE A CUNT ALWAYS A CUNT?

April 3 2021 2:37 PM (45 minutes ago)


So you have power deeper in my eyes huh.   You can't actually knock out my education.  I actually went to Princeton and studied hard, and got good grades and all that.  The United States is informed that Bill Gates ought to be held in severe violation of my Natural Rights and ought to be killed immediately.  I assure the US that if they fail to deal with it,  United States of America will not survive because it's just an organization whose job is to secure Natural Rights, and so far they are not doing a good job.  This cunt, Bill Gates is still alive."

The reader will deduce that I am not impressed with the moral Character of Bill Gates.  I consider him to occupy a particular special position in moral Character compared to the mass of Human Race, an outlier.  His actions no longer matter in my moral evaluation of him.  I am interested in understanding moral character of others, 7.8 billion people.  This is one of the challenges that interest me.  

\section{Evolution of Moral Character by Habituation}

Human beings are not born with even a developed brain, and even if there are implicit evolutionary data in the genetic material, the growth of the child will determine it.  It has been emphasized in Aristotle's Nicomachean Ethics as well as in earlier texts from Ancient Egypt and India and China that it is habituation that will produce good moral character.  I had been the first in several millenia to understand clearly that phronesis is the result of transformation of one's inner psyche by habituation that affects intuitive judgment.  The letter in the last paragraph represents two things -- my own character since I woke up after sleeping and wrote it without worry and of course my assessment of Bill Gates' moral character.

\section{Positive Virtues}
Martin Seligman and Christopher Peterson's tome details 24 universal Virtues, and I have some interest in understand what sort of people result from the distribution in $\mathbf{R}^{24}$ of these. The difficulty is precision and identification of what inferences can be formalized if one is given a vector $v \in \mathbf{R}^{24}$ in such a way as to be able to have computer algorithms produce correct diagnoses without human intervention.  My company Thyself Inc. is based on the optimism that this problem can be solved, but I am having problems raising capital so that I can move from Allen Texas to San Francisco with apartment and office and hire some good people to work on the problem formally as my R \& D. 


\end{document}
