\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf is Firmly Opposed to Bill Gates' Efforts at Planetary Autocrat} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates is not cut from the right material}

Egyptian Pharaohs were highly focused on Virtue and had to have training to get them; Bill Gates is indolent, insufferably ignorant, uncultivate and glib, and he does not have in him to be warden of well-being of 7.8 billion.  Now there are Worlds in the Universe with competent Planetary Autocrats.  I can't even tell you about how to find more information.  What is clear is that Bill Gates has no talent in this arena.  None whatsoever; indeed US Government ought to bomb him to extinction because he wants to overthrow United States and eradicate security of Natural Rights.  He is dangerous enough to kill immediately.

\section{Human Race is Angelic}  

I have verified that the Human Race is Angelic, so my Beloved People will prefer a Republic or an equivalent.  

\section{Warning}

Please Prevent Bill Gates from gaining Global Autocracy at all costs.  He is a White Supremacist Butcher and Malevolent man intent on re-instituting slavery and recolonising the world and so on.  Instead, just kill him.  He has violated enough of the laws to deserve Death Penalty.  He ought to be put to death.  We do not need him.

\end{document}
