\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{epigraph}
\title{Zulf is Willing To Concede That Whites Are Superior in Accepting Terrorist Violence in the Fringes}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Bill Gates has been repeating Whites are Superior}

Bill Gates has been occupying my meta with illegitimate use of power and repeatedly saying "Whites are Superior".  I do not believe this sort of position makes any sense without concrete detailed metrics.  There are a few sorts of metrics where there is some significant difference between whites and other broad ethnicities.

\section{Whites are  "Superior" in Accepting of Terrorist Violence at the Fringe}

It occurred to me that Bill Gates might be referring to my discovery that Whites are quite a bit more likely at the fringe of agreeing with Political or Terrorist violence being {\em always justified}.  Now around 95\% whites do not agree that Political or Terrorist violence is justified, and that is about the percentage for all other ethnicities as well.  What is special is that the percentage who think Terrorist Violence is {\em always justified} is around $1.45\sigma$ higher for Whites than Arabs.  

So I can easily concede that if "Superiority" means the easier acceptance of political violence as "always justified" then Whites are Superior to non-whites. That's no problem at all.  Bill Gates can easily win this; I will gladly hand over this sort of Superiority to Whites without any protest.  You want it bud?  It's yours.  It's yours.  Please feel free.  I don't want that sort of Superiority thank you very much.

\end{document}