\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Why I Consider it Appropriate to Describe Bill Gates as Mother Fucking Cunt In Ordinary Communication} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

Language is for precise communication.  I was mathematically trained at Princeton, and take pride in precise accurate communication.  I don't consider it appropriate to simply exclaim at random people 'mother fucking cunt'.  That's inappropriate.  But in the case of Bill Gates, since he has cut into my eyes and totalled my interior and cause untold damage to my meta, he is literally just 'mother fucking cunt' and other things.  I feel completely comfortable referring to him in this way in public communication.  That's just what he is.  He is an evil mother fucking cunt.  This is not any exaggeration, and I know more than most people on the planet that that is exactly what he is and so I think it is only proper to refer to him by what he is rather than whatever sorts of deception he uses in public.  He is not a gentleman who was successful by hard work etc.  He's an evil mother fucking cunt.  He's a White Supremacist Malevolent Butcher.  He is those things and he has proven to me that he is those things and so I do not consider it inappropriate to describe him by how I know him.  I don't really give a damn if people get offended by it or not. I am 48 and I am comfortable with my assessments and judgments.  My moral compass and virtuous character is quite strong.  On any disagreement with anyone on what Bill Gates is, I will claim superior knowledge.  I am just right.

\section{Anyone Who Says Bill Gates is a Good Man Is A Lying Sack of Shit}

I will attack the credibility of anyone who says Bill Gates is a good man quite successfully.  Those who do not want their credibility attacked randomly ought to stay away from saying good things about this Evil Malevolent Criminal Cunt at all.  You want your reputation to be dragged through the mud and put on bright bonfire?  Then please, consider propagating lies about how Bill Gates is a good man.  Otherwise keep out of our way.

\end{document}