\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}\title{Why I Am An Immortal Scientific Genius}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

Four-Sphere Theory is perfect and will not be displaced for millions of years in the future.  And I showed with data the Moral Nature of Man is roughly ethnicity-independent and thereby overthrew all racial theories of moral superiority.  And I just resolved partially the issue of Universal Noise in Nature by showing that the Barndorff-Nielsen densities arise as the push-forward of the normalized invariant measure under particular smooth maps.  This tells us that Bardorff-Nielsen densities arise as just the push-forward of the uniform volume element of $S^2$.  This is extremely important because in hundreds of different data, Barndorff-Nielsen can fit noise almost flawlessly.  This is a spectacular thing indeed. 

You have to take a brief look at history from De Moivre considering binomial distribution in 1700 to 1810 or so when Gaussians were already established as Nature's Noise and the confusion of twentieth century from failure in Finance to discovery of Barndorff-Nielsen in 1976.  Benoit Mandelbrot proposed stable densities but they are not the right answer.  The right answer is Barndorff-Nielsen.

For the tremendous cost to humanity with Gaussian models, I have transformed the world already because we will eventually have deeper understanding of Universal Noise.  Obviously O. Barndorff Nielsen discovered the true Noise Model.  But by showing they are push-forwards from $S^2$ I get one step to understanding how the actual geometry of the universe affects it.  Scientific Inference will sharpen as these works gain renown.  In the history of Statistics and Probability from 1700 to 2021, no one had actually been able to provide any fundamental explanation of any Error models to the structure of the universe at all.  Indeed the idea of law of large numbers had developed instead as the primary motivator for Normal model.  But the fundamental reason we have this, is because the universe is a four-sphere of fixed radius, and not because of large number of independent but small shocks etc.  Those things are secondary issues. I was reading Stigler's history book.  I had also read Peter Bernstein's erudite tome "Against the Gods".  No one had any idea that localisation of Noise could be a feature of compactness of the universe.  This is the right answer; the answer is not that there are only large numbers of iid just randomly concentrating.  Take a look at the central limit theorem.  In distributional sense the sum of iid will have normality.  Obviously the nice theorem never actually applied to noise in Nature because 93\% of the time series out their have non-Gaussian fits.

\section{I have a need to write these things}

I am straightforward and humility is not a strength of mine. I am an immortal scientific genius, and Bill Gates is every day cutting into my body and putting all sorts of pain meta and acting as malevolent criminal ways all day all night because United States Government does not actually care enough to kill murderers and White Supremacist Malevolent Criminals but rather protect their interests rather than simply wipe him out.


\end{document}
