\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{I am objectively superior to Bill Gates}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle
\epigraph{Come on, come on
Holy Roman Empire
Come on if you think
Come on if you think
You can take us on
You can take us on

You and whose army?
You and your cronies

You forget so easy
We ride tonight
We ride tonight
Ghost horses
Ghost horses}{Radiohead, "You and Whose Army"}

\section{General Concerns}
Generally I do not get involved in superior and inferior because I am fine with uniqueness.  But in the case of Bill Gates and maybe in my entire life there will be a handful of people where I am actually interested in ensuring that there are no ambiguities about my position.  This note will go over the various criteria that I will use to assert publicly that I am superior to Bill Gates.

\section{Criteria for Superiority}
Criteria for comparing the inferiority or superiority of men, for I do not know the rules for women, are classical.  They have been established in Ancient Greece and Indus Valley and Mesopotamia and Egypt and have propagated across the world since.  

Superiority and inferiority are determined in a number of metrics, the most important of which are moral Character and Conscience.

I will first go through some of my Personality Trait and Virtue measure features.  Then we will address comparison of achievements.  

\section{My Personality Profile}

\csvautotabular{zulf_big_five.csv}

\section{Some highlights of my Personality}

The percentile measures are with respect to the human race population.  Note those values above 80th percentile.

\subsection{A4: Morality}
My Morality is 86th percentile.  Now I am not religious in the ordinary way and spent most of my life 1979-2008 as pure empiricist and Atheist in the West.  I was never Muslim which is not inherited but one must accept the tenets of the faith.  Therefore my high morality is intrinsic and not imposed.  This includes my strong affinity towards Natural Rights of Man, my kind treatment of people, my labour while I was homeless of periodically searching the garbage bags thrown out with out-dated sandwiches to collect them for other homeless in 2008 and various other sorts of things that a person who cares about moral issues does. I am extremely proud of my fine tuned sense of right and wrong and evolved Conscience.  

\subsection{Sympathy and Trust}
For Sympathy I have 87th percentile and for Trust 80th percentile.  These are I think fairly good indication that I am a good person and do not cause harm to others without justification, and do not distrust people in a suspicious manner.

\subsection{Artistic Interests}
For Artistic Interests I have 90th percentile and I have a highly well developed artistic taste that I have cultivated since I was a young boy in film, poetry, novels, and have studied Literature formally at Princeton University including upper level courses on Mikhail Bakhtin's theories of Dostoevsky's Poetics.  I am interpreting Rilke's {\it Duino Elegies} recently with some good results.  I am extremely interested in Romantic Modernists.  I have a very good education in Western Literature.

\section{Intellect}
For Intellect I am 85th Percentile and this is evident from my early prizes at Westinghouse Science talent search (3rd place), my 1450 SAT score which corroborates 135-40 IQ, and my excellent academic performance at Princeton 1991-1995.  I am not particularly interested in misguided ideas about IQ as a true measure of intellectual talent.

\section{Achievements}

My Four-Sphere Theory is a great Scientific Revolution for macroscopic physics that succeeded after a decade of effort without any income; I also have excellent work in Finance such as my Medium Frequency strategy on which D. E. Shaw \& Co. have put in \$6 billion.  I have new work in Psychology and Social Science such linear fits to rapes, murder, and robbery rates across the world using LogGDP (per capita), Single Mother rate, and personality trait means of different countries.  They are all pioneering discoveries.

\section{Superiority to Bill Gates}

Bill Gates major achievements in creation of Microsoft cannot compete with my success in Four-Sphere Theory because my achievement is a Scientific Revolution with successful challenge to Einstein, Schroedinger, Lemaitre, Gravity, expansion, Big Bang. This is work of immortal genius.  All of Bill Gates achievements between 1955-2021 cannot compete since his achievements are not his own but from exploitation of other people's work, and they are not immortal genius and he has stolen many pioneering ideas from others.  

\section{Bill Gates is a Pathological Liar and Deceiver}

All of Bill Gates public self-promotion material are lies; his saintly philanthropic mask hides his outrageous greed, malevolence, murderousness.  He is also white supremacist which is a rather sordid ideology that intelligent American whites do not touch.

\section{Bill Gates Intuition is Bad}
Bill Gates holds glib convictions about the world that are often easy to refute with statistical data.  I will give you two examples of this here.

\subsection{White and Black Happiness}

First is his conviction that white happiness is inverse to black happiness.  I found after some hours of work that the correlation of yearly changes of happiness levels of blacks and whites in England is 0.26, a substantial positive correlation.  

The UK happiness by race is quite interesting and here is the table I determined.

\csvautotabular{whitehapp.csv}

\subsection{Philanthropy and Productivity}

Bill Gates had a glib conviction that Philanthropy is inverse to Productivity.  An hour later I was able to find a study that shows that Employee philanthropy is positively correlated to Productivity.

\subsection{Conclusion: Why?}
Bill Gates is glib with his general prejudices about feature of the world quite often.  Partly he is wrong because he's not a good student and does not study before holding convictions.  Partly it is because he's a White Supremacist who are not actually knowledgeable about how the world actually is -- since the Human Race is a single race in actuality -- but based on fantastic faith in all manner of mythologies that I, as a non-white, have no time for.  

Since I am much more careful about being right about the world than him, I ought to be given higher Social Status in American Society.


\section{Summary}
My moral Character and Conscience is far superior to his.  My achievements are far more immortal in their genius.  My taste in art is better than his.  He has more money but I am superior.


\end{document}