\documentclass{amsart} 
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Zulf's Quick Plans to Survive the Wrath of the World with Trillions in the bank}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}

\begin{document}
\maketitle

\section{Learning from Bill Gates' Fatal Errors}

Bill Gates has voiced eugenics as a method for population control.  This is such a fatal error for him, that Zulf is wise and is planning to avoid this pitfall altogether by doubling down on Natural Right of Life to every single human being on Earth.  I shiver thinking about the various parties who might corner me with death traps the moment my bank account exceeds a trillion. Zulf believes in Natural Rights of Life, Liberty, and Pursuit of Happiness, and does not want death for innocent people just for accounting purposes.  Zulf is quite wise and does not want to end up in anyone's death list.  People do have stupid schemes for eugenics.  I am rather happy with my Life and Liberty and Pursuit of Happiness and would recommend that people who create population control plans with other people's name on the list watch their own interests.  

\section{My population control scheme}

Just improve prosperity and earning.  This naturally reduces the population rate as more people are more concerned about becoming successful rather than focusing on having large families.

\end{document}