\documentclass{amsart} 
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{Several Facts about Myself Proves I am Far More American than Bill Gates}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}

\begin{document}
\maketitle

\section{Americanness is not about Paperwork}

America is defined by universal principles and not by ethnicity and other characteristics.  It is a multi-ethnic Classical Liberal Democratic Republic.  For me Universal Natural Rights are sacred, and this is a defining feature of the genuine Americans.  Americans differ from people of other countries in our adherence to Classical Liberal values.

Bill Gates considers Natural Rights to be inconsequential and calls it "PR" and ergo is not even a candidate to challenge my American-ness.

\section{Six Months of Homelessness in New York City in 2008}
I do have a Permanent Residency from 1997 that is valid, and I have lived in America from 1987, so thirty three years.  But in addition to all this I was actually homeless in New York City for six months in 2008.  I have given literal truth to sleeping on American soil, without benefits from any foreign agencies, alone.  And this gives higher weight to my Americanness-by-Life than anything Bill Gates can point to that gives his American-ness any more weight.  His English-Scottish ancestry is cute, but it is not as serious as my hobo experience for American-ness.  I have sold Socialist newspapers in San Francisco in 2002-2005 on weekends.  Combined with my hobo experience, I would give fictional Americans of F. Scott Fitzgerald in {\em This Side of Paradise} a run for their money in American-ness.  Bill Gates is a fake American by comparison, having hidden himself in Seattle provincial elites, not even real cosmopolitan America, New York and San Francisco.

\section{I am Princetonian}
I am Princetonian with strong feelings for Natural Rights, and have copies of John Rawls' {\em A Theory of Justice} on my desk, have followed the wisdom of Ralph Waldo Emerson.  I am Princetonian like James Madison.  Bill Gates literally thinks that his tawdry wealth from sales of second rate software products will give him higher American-ness than myself.  These things are not possible in this world.  Perhaps in an alternative universe he could have this, not in this one.

\end{document}