\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Relations with Jewish People, Israel, and All That} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{American Jewish People are not Israeli}

I have never had any problem with Jewish people in America at all.  I have had so many Jewish friends and teachers from high school.  My teacher for calculus in high school was Mr. Lieberman; he was Jewish.  He was a very good teacher.  I went to Ohio State University Ross Program and I befriended David Pollack, Keith and Brian Conrad, Josh Fischman, and they were Jewish.  I went to Princeton and was friends with David Ben-Zvi and Eric Gawaiser and Steven Gubser and they were Jewish.  I used to love eating at Hillel at Princeton sometimes and enjoyed kosher food.  Later on after I graduated, I was in New York.  I worked with Bob at Technology Solutions Company, and he was Jewish.  I worked for Robert Reich and he was Jewish.  I am quite familiar with and friendly with many Jewish Americans.  

American Jewish people I have known are mostly liberal and agree with me about Classical Liberal Universal ideals including sacredness of Natural Rights and the fundamental purpose of government for securing them.  That is my Jewish experience.  I have been friends with so many Jewish people that you might even confuse me for a Jewish man yourself if you only considered my opinions about matters not about the political topic.  

Israel, for me, has not much to do with American Jewish People.  I was truly surprised when I first found out that Israel pretends that American Jewish people are even remotely represented by them.  American Jewish people are perfectly normal sane good people.  Israeli people, on the other hand, are right wing freaks on the whole.  I don't understand how Israel even pretends to represent American Jewish people at all.  Israel is a European colonial enterprise that may have been helpful for the distraught Jewish population of Europe after they witnessed horrors of ethnic cleansing and mass incarceration and mistreatment during the war.  But American Jewish people by and large are Classical Liberal people who believe in the sanctity of Natural Rights for all Human Beings.  Like me.  They are my brothers and sisters.  They are not demented people who believe that some people have Natural Rights that ought to be preserved and others do not.


\section{Zulf's 100\% Conviction About 9/11}

United States had some classified war plans for seven or so Muslim countries that began developing after the fall of Soviet Union.  Israel knew about it and faked plane hijackings and remote controlled planes into Twin Towers and demolished them.  Muslims had no involvement in 9/11 whatsoever.  That is my conviction, and I consider anyone who has any other views to be totally and irredeemably deluded.  People who have other opinions will simply be ridiculed by me, just to be clear.  So Israel's Mossad did 9/11 is not exactly 'anti-semitic' but just true.  Anti-semitic is something else, having to do with holding hateful negative views about Jewish people.  One day when Mossad stops being a Doctor Strangelove organisation and becomes a Jewish Organisation, I'll reconsider whether my 9/11 view is anti-semitic; not today.

\section{Zulf's Position on Jewish Morals}

Zulf has a position on Human Nature Morals, that they are independent of ethnicity modulo 6.5-9.5\% and good and bad distribute about the same way within each ethnicity.  So my view about Jewish Morals is that they won't differ much from Human Nature Universal Morals.

This is my attitude about Hindu, Muslim, Christian and other morals. These are measured by World Values Survey.  Anyone who holds views that are off from measured values are idiots and illiterates.


\end{document}