\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Why The World Is Fortunate that White Supremacist World Order Plotter Bill Gates Targeted Me} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{My Marriage to Natalia Brizuela}

I got married to Natalia Brizuela in 1996.  She is half Argentine (Spanish ethnic father) and half American (Irish ethnic mother).  She lived with me at my invitation.  I was a virgin when I got together with her, and I was naturally much more conservative than her.  She was a Western liberal woman, with all sorts of problems with the 'institution of marriage'.  I was so steeped in marriage as an institution that I did not even understand what her concerns were.  For me, people get married for good, till death do us apart.  Well things did not work out.  I was devastated for a while, but met Sine Jensen at MIT around 1999.  Natalia and I got our divorce settled amicably in 2005 maybe.  She was bisexual and had a complicated love life afterward and I never got in her way.  

Sine Jensen and I were good together from 1999 to around 2002 maybe. I did not know what happened but I could not get good jobs in New York after 9/11, and eventually she left me and went back to Denmark.  Some years later I invited her to San Francisco to propose but it was too late.

These are some of my relationships.  I am American, although not white myself, I have been intimate with various white women and find this quite normal.  

You see, I grew up in multi-ethnic environments all my life, and am not racial at all.  I don't see white people as particularly different from me in race.  This has problems in podunk but in San Francisco, in New York, in Boston, in London, there are no problems.  I am a Princetonian so I am elite, and women I end up dating or getting into relationships are elite and highly educated. 

\section{What Does This Have To Do With Bill Gates?}

Well, I am far more evolved today about issues of race than I was even at Princeton during 1991-1995.  Then, I was nice to everyone, diplomatic, but did think about my life in terms of being an immigrant.  But it's 33 years later now.  I don't see white or anyone else as distant from me.  If you're a good person, you're good.  If you're a cunt, you're a cunt.  I don't consider ethnicity a major factor.  That's because I am evolved.  All these people who see ethnicity as making them who they are just seem too unevolved, too primitive, and they come from all ethnicities.  Great people are not restricted by ethnicity; shitty people are not either.

So Bill Gates seems like a pathetic little boy who has had a sheltered existence and was a psychopath from early age, and his 'lifelong dreams' of a white supremacist world order is not a nightmare for me but impossible.  I just {\em know} a lot more about what race and non-race matters really are. 

Do you think that my results on 6.5\% variation in moral values by ethnicity is just pure fortune?  Of course not.  I knew this all my life.  I've had friends, lovers, etc. who are white, and they were elite, so I fit in with the elite of London and New York and San Francisco.  That's right. I'm elite, and I am also sophisticated enough not to make people feel uncomfortable about their ethnicity.  That is just ghetto, ok?

How is a White Supremacist cunt without any class, with tacky gaudy mansions and no education going to compete with me?  I am far beyond his league in posh.  I am an evolved American man.  He thinks all this talk that he does about people getting along is "PR" and reality is that white people are evil malevolent cunts and that people's actual attitudes in the modern world is from the Old Testament tribal domination and enslavement.  That's a fucked up cunt over there.  

\section{Zulf Stands as a Warden of Sacred Natural Rights of United States of America}

Bill Gates is quite entitled and considers himself worthy of ruling the United States while repeating "Whites are Superior" and "Natural Rights are Claptrap".  This is one of the greatest threats to the Multi-Ethnic Classical Liberal Democratic Republic that is America.  The United States Senate is too incompetent to handle these threats from people with money.  So it falls upon Zulf's shoulders to secure the United States of America from the Glib Psychopathic Charlatan from Corrupting the Nation.  The US Legislature is far too incompetent to even understand their job, i.e. securing the Natural Rights of all Americans, and would, if I were not here, have allowed Bill Gates to collapse the Republic altogether.  It then falls on me to secure the Nation from a real threat, not a fake threat like Bin Laden and Al Qaeda, who had nothing to do with 9/11.

\end{document}
