\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Towards a Manifesto of Zulf's World Order} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Key Points of Zulf's World Order}

John Locke and Thomas Jefferson were great men, and had great successes, but they were not Zulf, so they made many serious errors as well.  My Zulf's World Order Plan will fix these errors.

First of all we hold these truths to be self-evident that every man, woman and child on earth are born with certain inalienable rights that include right to have maximal Life Satisfaction in their lives on Earth.  Locke and Jefferson mention, Life, Liberty, and Pursuit of Happiness, but they did not know the finer points of either Happiness or Life Satisfaction.  I want my World Order to include provisions for maximal Life Satisfaction for all people born on Earth.

\section{Rationale}

Every human being born on Earth is unique and special and furthermore deserves to have sufficient support to have a fulfilling Life Satisfaction.  I am unimpressed with the political structure of the Human Race currently which is too crude to produce even rudimentary understanding of Life Satisfaction and Well-Being for 7.8 billion.  This will change in my World Order.

\section{The Virtue of Intellect is to Produce More Solid Foundations For The World}

Nature is inscrutible, and we, the human race, are complex products of nature.  That we should not know ourselves is but an almost certainty for we have difficulties understanding far less complex features of nature and expend centuries on these.  The time period between light speed being infinite (Rene Descartes) to the first measurements of finite speed of light was Ole Romer in 1676 and eventually sharp measurements were found by 1900.  Human beings are infinitely more complex and inscrutible compared to the speed of light.  The US Declaration and Constitution stand as examples of great success of the intellect, for the founders produced some small set of principles and rules that allowed a multi-ethnic population to produce an enormously successful nation.  We must strive therefore to produce finer understanding of human nature and to find deeper and more correct principles that will produce a flourishing world Civilisation with less strife and targeting of Life Satisfaction {\em as a Natural Right} is the right way forward.  

The purpose of Natural Rights is to ensure that governments' purpose is to secure natural rights, in sharp contrast to a more primitive age of Princes and the resulting problems of tyranny and Despotism.  

\section{Revision Is Desperately Necessary}

Failures of Classical Liberal Foundations of America are visible with disintegration and failures of marriages and single-mother households across the planet.  I describe these elsewhere.  

\end{document}