\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf Returns to the Old Question of Soul and Body} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Plato's Theory}

Plato propagated a theory of soul and body as separate.  Aristotle, after him, had a slightly different theory.  Centuries later Rene Descartes would write {\em On the Passions of the Soul}.  I think the issue is still wide open, and I have new advances to propose some new understanding for these.  The foundation for my speculations and theories is my {\em Four-Sphere Theory} which posits a very large purely electromagnetic fourth macroscopic spatial dimension.  This is not a simple matter.  All of Western Science could not see this clearly for three centuries and even the great Hermann Weyl went astray.  I am positing an objectively real fourth macroscopic spatial dimension, not a mathematical artifice.

\section{Bill Gates is Truly Irritating Because he Cut into my Eyes}

Cutting into one's eyes produces enormous problems including having to hear the ugly horrible voice of Bill Gates day and night.  This man is the most illiterate ignorant uncultivated uncouth, inferior-intellect man in the entire history of the Human Race.  He does not even know the importance of Thomas Aquinas' reformulation of Plato and Aristotle's Theories of the Soul which is the foundation of Western Civilisation after the collapse of the Roman Empire.  Empiricism that became stronger much later than Rene Descartes, around 1650, never had great sway in either Europe or America which is still a deeply religious Chrisitan country, and this man, Bill Gates is totally ignorant of the reality.  

Here I am, after many projects taking up the issues of the Soul which remain completely mysterious to the Human Race, and this man is irritating me cutting up my eyes and harming me every day with no respite, no execution from US Senate for damaging my Natural Rights.  I am quite irritated about this situation.  I am a great genius and I do not appreciate how my country the United States of America is treating me at all.  I will surely hold the US Senate accountable for this grave insolence.  I want the world to know that I consider Bill Gates to be of {\em lesser breed} than myself and inferior intellectually as well as in moral character.  


\section{Four-Sphere Theory Implies a Different Four-Dimensional Chemistry Than Established}

My electromagnetic law, not Maxwell's, governs the actual universe.  It is a wave equation on sections of a Clifford bundle on a metric four-sphere of radius $R=3075.69$ Mpc. This law governs all of 'macroscopic existence'.  I will clarify my use of the word 'existence'.  From the Four-Sphere Theory view, all things that have objective existence in the external world is contained in a Four-Sphere whose radius will be constant $R=3075.69$ Mpc is an estimate but further improvements of this figure will not radically change it.  This is an {\em Eternal constant}.  Indeed, it is related simply to the measured {\em Planck constant} $h$.  All of the external world as we know, {\em and much much more} is included in existence, geometrically $S^4(R)$.  Time is linear and extends back to minus infinity and forward to plus infinity.  There is no relationship between time and space of the type Albert Einstein posited.  There is no Lorentz invariance of space.  This theory of Albert Einstein, of 1905, the Special Theory of Relativity, is wrong.  In actual truth, space and time are separate and do not mingle in the way Einstein thought.

\section{Eternity of Past and Eternity of Future}

The actual universe is structured in such a way that things that exist are not unbounded and infinite but have precise bounds, and S4 Electromagnetic law ensures that the universe has existed for infinite time in the past and will continue for infinite time in the future.

\section{Brief Comments on Why Einstein Was Wrong}

Einstein died in 1955 and was not in possession of crucial facts of Nature that were discovered later, both of which are central to development of my Four-Sphere Theory. First is the discovery in 1959 by Bohm and Aharanov of physical reality of the electromagnetic potential.  Their publications use quantum mechanical language but the reality of electromagnetic potential is not any special 'quantum' feature of Nature; it is just a feature of electromagnetism in Nature.  Four-Sphere Theory is a {\em classical} field theory and I rely on this feature as crucial to justifying my theory.  Second feature is the exact value of the {\em cosmological constant} $\Lambda=1.11 \times 10^{-52} m^{-2}$.  The exact value was not determined for a long time after Einstein had died.  Here again, it is crucial to physics the exact value, for unless $\Lambda=0$ the Special Theory of Relativity does not actually apply to the actual universe at all, as a simple consider of a matterless universe would show.

\section{Putting Aside Science: My Private Faith}

My private faith, my subjective beliefs about myself and the universe include the following.  I believe that I have been an Archangel Soul for many millions of years in the universe, and that I have had two lives on Earth that I can extract.  One of these lives took place between 1180-1300 in England, and I believe I was an English Knight.  And this life began in November 19 1973 in Bengal.  In other words, I believe that "I" have an extension that extends beyond physical life.  As you can surmise, these subjective matters of {\em faith} are not yet matters of Empirical Science.  In particular, today we do not have any reasonable scientific theory that could explain why I think that some Englishman's life between 1180-1300 could have anything to do with me, Zulfikar Moinuddin Ahmed.  Now my faith is unperturbed despite quite reasonable empirical skepticism that indeed I did have such a life on Earth, as another human being.

There are other beliefs that I hold that are also not quite consistent with the extant empiricist views of the current age that are respectable to scientific audience.  

I will attempt to remedy this and make some efforts to bringing my own faith with my scientific views.

\section{Issues of Faith}

I hold it a matter of religious faith that I have had a life as an Englishman in 1180-1300 period and this one.  I have other articles of religious faith.  These are protected by United States Constitution First Amendment.  They cannot be challenged by anyone else.  These are matters of religious conviction for me.  I have no interest in coercing agreement by anyone else regarding these either.  I believe that I am the Chosen One as well.  It matters very little to me who agrees with these and who does not.  These are mostly private matters, and my faith in them is quite strong.

\section{Aristotle's Theory of Soul is Wrong}

Aristotle, unlike Plato, theorised that the Soul is tied to the body.  Given my revelation about my own faith about my past, I do not agree.  I believe that I have existed without a body for millions of years, and I am having a life with a body on Earth right now.  

But this is a matter of conviction.  There needs to be a consistency with Four-Sphere Theory still regarding how it is possible to have existence without a body at all, and that is what is interesting to attempt to understand.

I want to delve deeper into this topic further in the future, but at the moment, a clear articulation of how to produce consistency with a mathematical physics is all that is important.

I ask the question: are there coherent theories that are {\em reasonable} rather than {\em certain truth} that will ensure that my religious faith can co-exist in a contradiction-free manner with Four-Sphere Theory.  We will leave aside experimental evidence and other more stringent requirements for when we have a class of consistent theories.

\section{Why Would Someone With an English Life be born in Bengal}

I do not have distinct memories of my reasoning for being born to my particular parents.  My father's bloodline is very old in royalty going back to Vedic times although he was Muslim, and my mother is superbly talented in her ways and filled with life.  Most likely it had to do with geopolitics, where I considered the genetic quality of my father's line, the relative quiet far away from Washington D. C. and a good vantage point for an Archangel Soul.  Besides I come here on Earth and have human lives for vacation, and I might have thought Bengal was peaceful with a long Civilisational tradition and it would be more interesting.  I cannot recall the details because Archangels would turn off all memory at conception, i.e. when I entered the pregnant cell that ended being my physical body.

My relationship with England and Bengal both evolved in a complex manner to be sure, so I am not surprised that I had picked an English ex-colony.  Early in my childhood I gained interest in the poetry of the English Romantics at my paternal grandparents' house, and even today I have poetry of Percy Bysshe Shelley and some biographies on my shelves.  I have a very strong resonance with Percy Bysshe Shelley, for although I did not have any genius in poetry I have felt quite inspired by his political radicalism and adherence to Classical Liberal thought.  

\section{Human Extension in Four Dimensions}

We are four-dimensional beings with an extension past the physical world.  At a given instant of time, $t\in \mathbf{R}$, roughly the physical universe is a smooth hypersurface $M(t) \subset S^4(R)$.  It consists of electrically charged particles that hold together.  One can put absolute coordinate on $S^4(R)$ but the physical hypersurface $M(t)$ is constantly changing.  This is because the charged particles in the physical universe are in interacting dynamics with all other charged particles not just in $M(t)$ but in the entire $S^4(R)$.

I consider my physical body; I consider my full electromagnetic extent to $B(t) \subset S^4(t)$ and my physical body to be $B_0(t) = B(t) \cap M(t)$.  I leave open the possibility of unknown complexity in my own full electromagnetic body.  

We consider $U(t) = S^4(R) - M(t)$ to be the unseen part of the universe.  This is vast and objectively real.  I do not offer any structure for this in terms of distribution of magnetic monopoles, charges etc.




\end{document}