\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Understanding of My Relationship With the Government of United States of America} 
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Reminisces of the Past}

Late summer of 1987 I was in the Los Angeles airport with my brother.  My mother was creative and had prepared for the trip from Bengal by making some special clothes for us.  She made the matching jackets I and my brother Feroze (now he goes by Tobias Firooz Ahmed but he was born Feroze Alamgir Ahmed) wore corduroy jackets with lamb's wool in the inner side and at the time I did not appreciate that my mom's creative talents and skills as well as courage were outstanding.  I love my father and he has many other great qualities too but he had no interest in immigration to America.  I was some months past my thirteenth birthday.  Years later, I was married in New York to my then lover Natalia Brizuela in 1996, and I obtained Permanent Residency in 1997.  Now Permanent Residency is actually immigration status of those who are planning to be Naturalised as US Citizens.  But you see, I was American already in 1988.  The paperwork was, for me, just formality, for all my friends and life was already in America.  

\section{The Implicit Contract}

When I sign immigration papers with the United States, on one hand, I am pledging that I will be subject to the laws and be in good standing in America; but the flip side is that United States Government is promising that while I am in America, and permanently, they will secure my Natural Rights.  They told me in US Declaration that that is the purpose of their existence, to secure American Natural Rights.  And I did not doubt any of this ever.  I was never suspicious that United States Government is not going to secure my Natural Rights against Criminals. 

But this is precisely what has been happening.  This Evil Vile White Supremacist Criminal, who goes by the name of Bill Gates, has brutally and criminally cut into my eyes and violated all possible norms of Civilisation in the most barbaric, brutal, heinous, evil, abominable ways for almost a year now and United States Government has not done what any reasonable government ought to do, which is obliterate him physically and destroy him and fling the remains into oblivion.  This specific sequence is just from history of civilisation of what ought to be done with these types of criminals, but that is what I was {\em expecting} from the United States Government.  I am not pleased to see that United States of America, founded as a Multi-Ethnic Classical Liberal Democratic Republic, is now suddenly confused about what to do the moment when {\em Zulf's} interests are concerned.  You have spend three centuries giving blowjobs to everyone else's interests but you suddenly have not enough enthusiasm when {\em Zulf's} interests are concerned.  I am obviously outraged.  



\end{document}