\documentclass{amsart} 
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[fontsize=14pt]{scrextend}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{epigraph}
\title{I am the Success of this Age and Bill Gates its Great Failure}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Why I Ought to be Recognized as the Great Success of this Age}

In all of Human History, I alone have given Man the final true laws of Nature, with Four-Sphere Theory.  I had struggled hard to reach higher levels of insight about truth of Nature to reach this, leaving behind Isaac Newton, Albert Einstein, Erwin Schroedinger, and all others.  This is not a matter of denigrating their accomplishments for they are giants on whose shoulders I stood to see beyond, to the bounds of existence itself and recover the fundamental laws of Nature. It was I who returned Fate to its rightful place and salvaged Eternity from Oblivion.  

It was I who had seen through the gaps and failures of Adam Smith and John Locke, great geniuses, to trace their errors to the conception of primordial man as a solitary creature, and established with quantitative numbers that Social/Respect needs are more fundamental than Money for Self-Interest, and link the weaknesses of Classical Liberalism to failures of marriages across the globe, of epidemic of loneliness, of fatherlessness across the world.

It was I who promoted targeting of Global Unhappiness levels along with Global Inflation and Unemployment to return Central Banking from a weak effort to an enterprise to oversee the well-being of my people the Human Race.

It was I who had proposed the reduction of Global Individual Credit Spread, absurdly high, a burden on my people the Human Race, with a simple \$5 trillion loan taken out by China from the debt markets.

And I have done this with a decade of absence from the various \$150-200k positions without any income far from Civilization (well from San Francisco and New York) in Allen Texas.  I have done these on my own by my own efforts.

\section{Bill Gates is a Deceptive Charlatan}

Bill Gates is a primitive malevolent criminal thief and murderer who had simply projected a completely false image of his competence and benevolence with documentary movies and interviews while in his heart are primitive petty ethinic tribalist ambitions that would be quite embarrassing to the Ostrogoths who overran Roman Empire.  He sold shoddy software using criminal predatory principles and is driven by some of the most disgusting unlawful methods such as cutting up people's eyes and harming their Life, Body, Ancestral, Family meta when they do him a favour that allows him to profit from D. E. Shaw \& Co.


\section{I am the Great Success and Bill the Great Failure}

There is no question that Bill Gates has had no accomplishment in his life that stands a shadow of a chance to compare with mine.

\end{document}




\end{document}