\documentclass{amsart}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage{hyperref}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{epigraph}
\title{Zulf's Notes on Things That I Know A Bit But Will Not Prove}
\author{Zulfikar Moinuddin Ahmed}
\date{\today}
\begin{document}
\maketitle

\section{Believe These At Your Own Discretion}

This is not science but my faith.  I will not be liable if you believe any of this and this harms your life.  So beware.  Believe any of it at your own discretion.

\section{Network of Paths connecting Galaxies}

There are networks of paths connecting galaxies for souls. Living souls without bodies.  Souls can traverse intergalactic spaces by these paths.  If you are dead, you will know intuitively how this works.  The paths are to centers of galaxies.  They are natural parts of the universe.  So you exit the solar system through the center of the Sun, then exit the Galaxy through its center.  Then you will find the network of paths.

You can travel to a number of galaxies.  These are fast.  Galaxies that are hundreds of light years away you can reach in a few days by these paths.  

Generally you want to stick to Angelic Worlds.  There are humanoid Civilisations across the universe, but not near Milky Way.  You can be born as one of their young.  You'll end up erasing your memory almost completely as physical consciousness and mind has to grow from baby.  Here on Earth we have knowledge of DNA and evolutionary adaptations that form all functions of the brain and thoughts.  You can't retain a lot of memory and also it will produce problems for your time as fetus and newborn to try to retain all sorts of memories that will lead to health problems.  So I just do a wipe before birth in any Angelic World.  

Do not ask me to prove any of this.  I won't bother.  I will repel any lawsuits if you claim that I had deceived you as well, because I am simply sharing my private faith and am not benefitting commercially.

\end{document}